---
title: "JSDM models test"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(arm)
library(jagsUI)
library(ggplot2)
library(gridExtra)
library(parallel)
library(Rcpp)
library(magrittr)
library(purrr)
library(readr)
library(corrplot)
library(gjam)
library(Hmsc)


#setwd("~/Desktop/VirtualCommunity/simcoms-master/ExampleFiles")
 setwd("~/Documents/GitHub/Ecology-models/simcoms-master/ExampleFiles")
# lapply(list.files(path = "."),load,.GlobalEnv)

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master")
load("params.rds")
load("sim_names.rds")
load("comp_inter.rds")
load("fac_inter.rds")
#sim_data<-readRDS("sim_data.rds")


load_object <- function(file) {
  tmp <- new.env()
  load(file = file, envir = tmp)
  tmp[[ls(tmp)[1]]]
}
```



## Data description

Data was simulated using VirtualCommunity code.\
Simulated data contains 20 data sets. \



NB - if chain/sample parameters is modified - should be changed in the whole section(dataset) 

## Environment filtering 5 species

### JSDM


```{r draw, echo=FALSE, include=FALSE}
setwd("~/Desktop/VirtualCommunity/simcoms-master/")
sim_data<-readRDS("sim_data.rds")

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")

#' Extract correlation parameter means
#+ mean-correlations


prob_cooccur_es <- function(Y) {
  K <- ncol(Y)
  ans <- matrix(0, K, K)
  
  for (k in 1:K) {
    for (kk in 1:K) {
      N1 <- sum(Y[, k])
      N2 <- sum(Y[, kk])
      N <- nrow(Y)
      j <- max(0, N1 + N2 - N):min(N1, N2)
      p <- vector("numeric", length(j))
      for (i in seq_along(j)) {
        p[i] <- (
          choose(N, j[i]) * choose(N - j[i], N2 - j[i]) *
            choose(N - N2, N1 - j[i])
        ) / (
          choose(N, N2) * choose(N, N1)
        )
      }  
      ans[k, kk] <- (sum(Y[, k] + Y[, kk] == 2) - sum(p * j)) / N
    }
  }
  ans
}

#load("model-2019-04-09-19-02-16.rda")
me5 <- load_object("model-2019-04-09-19-02-16.rda")
summary(me5)
jsdm_conv<-function(mod) {
  cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mod$R$B),4)))
  cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mod$R$Rho),4)))
  cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mod$R$EnvRho),4)))
  hist(mod$n.eff$B, lwd=2,col=gray(.6), main="ess(beta)", xlab = "Beta")
  hist(mod$n.eff$Rho, lwd=2,col=gray(.6), main="ess(rho)",  xlab = "Rho")
  hist(mod$n.eff$EnvRho, lwd=2,col=gray(.6), main="ess(envrho)",  xlab = "EnvRho")
}

jsdm_conv(me5)
me5$mcmc.info[1:7]




#load("fac_inter.rds")
#load("comp_inter.rds")

mean_cor<-function(mod){
  mean_correlations <- do.call(
  rbind,
  lapply(
    seq_along(mod),
    function(i) {
      x <- models[[i]]
      nm <- strsplit(
        names(models)[[i]], "(?<=[a-z])(?=[A-Z])", perl = TRUE
      )[[1]]
      nsp <- ncol(x$mean$Rho)
      ut <- upper.tri(x$mean$Rho)
      sp <- arrayInd(which(ut), c(nsp, nsp))
      ans <- data.frame(
        model = i,
        sp1 = sp[, 1],
        sp2 = sp[, 2],
        rho = c(prob_cooccur_es(x$model$cluster1$data()$Y)[ut], x$mean$Rho[ut]),
        rho_type = rep(c("Effect-Size", "Residual"), each = sum(ut)),
        sgn = sign(x$mean$Rho)[ut],
        significant = x$overlap$Rho[ut],
        #cint = simulation_parameters$comp_inter[[i]][ut],
        #fint = simulation_parameters$fac_inter[[i]][ut],
        cint = comp_inter[[i]][ut],
        fint = fac_inter[[i]][ut],
        density = tail(nm, 2)[1],
        type = paste0(head(nm, -2), collapse = ""),
        nsp = nsp,
        stringsAsFactors = FALSE
      )
      ans$cint[is.na(ans$cint)] <- 0
      ans$fint[is.na(ans$fint)] <- 0
      ans$density[ans$density == "Even"] <- "None"
      ans$density <- factor(ans$density, c("None", "Sparse", "Dense"))
      ans$type[ans$type == "Env"] <- "Environmental\nFiltering Only"
      ans$type[ans$type == "Fac"] <- "Facilitation"
      ans$type[ans$type == "Comp"] <- "Competition"
      ans$type[ans$type == "FacComp"] <- "Facililation +\nCompetition"
      ans$type <- factor(
        ans$type, 
        c(
          "Environmental\nFiltering Only", "Facilitation", "Competition",
          "Facililation +\nCompetition"
        )
      )
      ans$interaction <- "None"
      ans$interaction <- ifelse(ans$cint, "Competition", ans$interaction)
      ans$interaction <- ifelse(ans$fint, "Facilitation", ans$interaction)
      ans$status <- ifelse(
        ans$significant,
        ifelse(ans$sgn * -ans$cint == 1 | ans$sgn * ans$fint == 1, "TP", "FP"),
        ifelse(ans$cint == 0 & ans$fint == 0, "TN", "FN")
      )
      ans$interaction <- factor(
        ans$interaction, c("None", "Facilitation", "Competition")
      )
      ans
    }
  )
)
 return(mean_correlations)  
}





metrics_jsdm<-function(model,fac=NULL,comp=NULL,only_env=T){
  
  Rho<-(!model$overlap0$Rho)*model$mean$Rho
  #{
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
       
      }
#    }
#    }
    }
    }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
 }
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
   list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
}



```


```{r heat, include=TRUE}
data<-sim_data$EnvEvenSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

Y_cor<-cor(data$Y)

to_prec<-function(m){
  n<-dim(m)[1]
  Tau_n<-matrix(nrow=n, ncol=n)
  for (j in 1:n) {
   for (k in 1:n){
    Tau_n[j, k] <-  -m[j, k]/sqrt((m[j,j]*m[k,k]))
   }
  }
  return(Tau_n)
}

#Tau_n<-matrix(nrow=dim(model$mean$Tau)[1], ncol=dim(model$mean$Tau)[1])
Tau_n<-to_prec(me5$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

par(mfrow=c(2,4),oma = c(3, 1, 2, 1))
cols = colorRampPalette(c("dark blue","white","red"))
col2 <- colorRampPalette(c("#4393C3", "#2166AC", "#053061",
                           "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE",
                           "#67001F", "#B2182B", "#D6604D", "#F4A582"))


corrplot(Y_cor, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Correlation cor(Y)")
corrplot(me5$mean$EnvRho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("EnvRho")
corrplot(me5$mean$EnvRho*(!me5$overlap0$EnvRho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("EnvRho signif")
corrplot(me5$mean$Rho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Rho")
corrplot(me5$mean$Rho*(!me5$overlap0$Rho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Rho signif")
corrplot(Tau_n, diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Tau")
corrplot(Tau_n*(!me5$overlap0$Tau), diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Tau signif")

j_metric_e5<-metrics_jsdm(me5)
#cat("Success rate ")
#j_metric_e5$success_env
 cat(sprintf("Success rate: %s\n", metrics_jsdm(me5)$success_env))
 
```


### GJAM 

```{r gjam functions, include=FALSE}
############################################################Functions
makeSymm <- function(m) {
  m[upper.tri(m)] <- t(m)[upper.tri(m)]
  return(m)
}

convert_to_m<-function(ar){
  d <-floor((sqrt(length(ar)*8+1)-1)/2)
  C <- matrix(0,d,d)
  i.lwr <- which(lower.tri(C, diag = TRUE), arr.ind=TRUE)
  C[i.lwr] <- ar
  C<-makeSymm(C)
  return(t(C))
}


metrics_gjam<-function(Rho, comp=NULL,fac=NULL,only_env=T){
  
  
  #{
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
       
      }
    }
#    }
#    }
    }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
  }
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
  list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
  }





fit_gjam<-function(data, it=2500,burn=500 , name="./gjam_models/temp.rda",interact=diag(ncol(data$Y))){
  #setup parameters
  data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )
  xdata<-as.data.frame(data$X[,-1])
  colnames(xdata)<- c("env","env2")
  ydata<-as.data.frame(data$Y)
  ###formula
  formula<-as.formula( ~env+ env2)
  ml   <- list(ng = it, burnin = burn, typeNames = 'PA')
  ####fit
  
  
  mod_gjam1  <- gjam(formula, xdata = xdata, ydata = ydata, modelList = ml)
  save(mod_gjam1, file = name)
  #summary(mod_gjam1)
  hist(effectiveSize(mod_gjam1$chains$sgibbs), main="ess(beta)",lwd=2,col=gray(.6))
  hist(effectiveSize(mod_gjam1$chains$bgibbs), main="ess(beta)",lwd=2,col=gray(.6))
 
  Tau <- solve(mod_gjam1$parameters$sigMu)
  Tau_n = to_prec(Tau)
  
  postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
  postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)
  
  
  pH<-convert_to_m(postH)
  pL<-convert_to_m(postL)
  
  R_sign<-cov2cor(mod_gjam1$parameters$sigMu)*(!(pH>0 & pL<0))
  
  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(ydata), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",   type = "lower")
  title("Correlation cor(Y)")
  corrplot(mod_gjam1$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R")
  corrplot(mod_gjam1$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("E matrix")
  corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Tau")
  corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("True interactions")
  R_sign
}

load_gjam<-function(data,name="./gjam_models/temp.rda",interact=diag(ncol(data$Y))){
  #setup parameters
  data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )

  
  gj_mod<-load_object(name)
  #summary(gj_mod)
  hist(effectiveSize(gj_mod$chains$sgibbs), main="ess(beta)",lwd=2,col=gray(.6))
  hist(effectiveSize(gj_mod$chains$bgibbs), main="ess(beta)",lwd=2,col=gray(.6))
 
  
  Tau <- solve(gj_mod$parameters$sigMu)
  Tau_n = to_prec(Tau)
  postH<-apply(gj_mod$chains$sgibbs, 2, quantile,0.95)
  postL<-apply(gj_mod$chains$sgibbs, 2, quantile,0.05)
  pH<-convert_to_m(postH)
  pL<-convert_to_m(postL)
  R_sign<-cov2cor(gj_mod$parameters$sigMu)*(!(pH>0 & pL<0))

  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(data$Y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Correlation cor(Y)")
  corrplot(gj_mod$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R")
  corrplot(gj_mod$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("E matrix")
  corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Tau")
  corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
  
  R_sign
}

######################################################################
```




```{r gjam env5, include=TRUE}

##to setup chains parameters
data<-sim_data$EnvEvenSp5
#Rho_sign<-fit_gjam(data,2000,1000,"./gjam_models/gjam5env.rda")
Rho_sign<-load_gjam(data,name="./gjam_models/gjam5env.rda")

g_metric_e5<-metrics_gjam(Rho_sign)
#cat("Success rate ")
#g_metric_e5$success_env
cat(" ")
cat(sprintf("Success rate: %s\n", metrics_gjam(Rho_sign)$success_env))

```

### HMSC

```{r hmsc, include=TRUE, results=FALSE}

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
fit_hmsc<-function(data,label="Fit",nsamples = 1000,nchains=2,name="./HMmodels/hmtemp.rda" ){
  if (label=="Fit"){
    Y_data = subset(data, select = -env)
    ns<- ncol(Y_data)
    np <- nrow(Y_data)
    X<-scale(poly(data$env[1:np], 2))
    colnames(X)<-c("env","env2")
    studyDesign = data.frame(sample = as.factor(1:np))
    rL = HmscRandomLevel(units = studyDesign$sample)
    m = Hmsc(Y=as.matrix(Y_data), XData=as.data.frame(X), XFormula=~env+env2, distr="probit",
             studyDesign = studyDesign, ranLevels = list(sample = rL))
    m = sampleMcmc(m, nsamples, thin=10, adaptNf=c(200,200), transient=500,nChains=nchains ,verbose=F)
    save(m, file = name)
    return(m)
  }
  if (label=="Load"){
    return(load_object(name))
  }
}




data<-sim_data$EnvEvenSp5
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm5env.rda" )
#hm_mod<-load_object("./HMmodels/hm5env.rda")

```



Convergence:

```{r hmsc convergence, include=TRUE}

hm_conv<-function(mod){
  codaList = convertToCodaObject(mod)

  #convergence histograms
  hist(effectiveSize(codaList$Beta), main="ess(beta)",lwd=2,col=gray(.6))
  hist(gelman.diag(codaList$Beta,multivariate=FALSE)$psrf,lwd=2,col=gray(.6), main="psrf(beta)")
  
  hist(effectiveSize(codaList$Omega[[1]]), main="ess(omega)",lwd=2,col=gray(.6))
  hist(gelman.diag(codaList$Omega[[1]], multivariate=FALSE)$psrf,lwd=2,col=gray(.6),      main="psrf(omega)")
}

hm_conv(hm_mod)
```



Study of interactions

```{r hmsc study of interactions, include=TRUE}
metrics_hmsc<-function(Rho, comp=NULL,fac=NULL,only_env=T){
  #{
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
      }
    }
  #  }
  #  }
  }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
  }  
  
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
  list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
}



hm_inter<-function(mod, nchains=2,nsamples = 1000, interact=diag(ns)){
  getOmega = function(a,r=1)
  return(crossprod(a$Lambda[[r]]))
  ns<-mod$ns
  postOmega1 = array(unlist(lapply(mod$postList[[1]],getOmega)),c(ns,ns,mod$samples))
  postOmega2 = array(unlist(lapply(mod$postList[[2]],getOmega)),c(ns,ns,mod$samples))
  
  postOmega<-abind(postOmega1,postOmega2,along=3)
  postOmegaMean = apply(postOmega,c(1,2),mean)
  postOmegaUp=apply(postOmega,c(1,2),quantile,0.95)
  postOmegaLo=apply(postOmega,c(1,2),quantile,0.05)
  
  postR<-array(dim=c(ns,ns,nchains*nsamples))
  for(i in 1:dim(postOmega)[3])
  postR[,,i]<-stats::cov2cor(postOmega[,,i])
  
  
  postRMean = apply(postR,c(1,2),mean)
  postRUp=apply(postR,c(1,2),quantile,0.95)
  postRLo=apply(postR,c(1,2),quantile,0.05)
  
  Tau = solve(postOmegaMean)
  Tau_n = -cov2cor(Tau)
  
  
  Toplot_R<-postRMean*(!(postRUp>0 & postRLo<0))
  
  # Omegacor<- computeAssociations(m)
  # supportLevel<- 0.95
  # toPlot<- ((Omegacor[[1]]$support>supportLevel)+ (Omegacor[[1]]$support<(1-supportLevel))>0)*Omegacor[[1]]$mean
  # corrplot(toPlot, method="color", col=colorRampPalette(c("blue", "white", "red"))(200))
  
  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(hm_mod$Y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Correlation cor(Y)")
  corrplot(postRMean, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R")
  corrplot(Toplot_R, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Plot only non zero value")
  corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Partial correlation matrix")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
  
  Toplot_R
}

Rho_sign<-hm_inter(hm_mod)

h_metric_e5<-metrics_hmsc(Rho_sign)
# cat("Success rate ")
# h_metric_e5$success_env
cat(" ")
cat(sprintf("Success rate: %s\n", metrics_hmsc(Rho_sign)$success_env))

```


## Environmental filtering 10 species

### JSDM

```{r load_m en10}
me10 <- load_object("model-2019-04-10-08-26-20.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me10)
jsdm_conv(me10)
me10$mcmc.info[1:7]

j_metric_e10<-metrics_jsdm(me10)
cat("Success rate ")
j_metric_e10$success_env

data<-sim_data$EnvEvenSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

plot_cor_jsdm<-function(mod,y,interact=diag(ncol(y))){
  par(mfrow=c(2,4),oma = c(3, 1, 2, 1))
  corrplot(cor(y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Correlation cor(Y)")
  corrplot(mod$mean$EnvRho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("EnvRho")
  corrplot(mod$mean$EnvRho*(!mod$overlap0$EnvRho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("EnvRho signif")
  corrplot(mod$mean$Rho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Rho")
  corrplot(mod$mean$Rho*(!mod$overlap0$Rho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Rho signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
}

plot_cor_jsdm(me10,data$Y)



```

### Gjam

```{r gjam en10}

data<-sim_data$EnvEvenSp10

#Rho_sign<-fit_gjam(data,5000,500,"./gjam_models/gjam10env.rda")
Rho_sign<-load_gjam(data,name="./gjam_models/gjam10env.rda")
#gje10<-load_object("./gjam_models/gjam10env.rda")

g_metric_e10<-metrics_gjam(Rho_sign)
cat("Success rate ")
g_metric_e10$success_env


#to check posterior density of s in Sigma 
#gje10<-load_object("./gjam_models/gjam10env.rda")
#plot(density(gje10$chains$sgibbs[,4]))


```

### HMSC
```{r hmsc en10}

data<-sim_data$EnvEvenSp10
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm10env.rda" )

hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod)

h_metric_e10<-metrics_hmsc(Rho_sign)
# cat("Success rate ")
# h_metric_e10$success_env
# h_metric_e10$success_fac

cat(" ")
cat(sprintf("Success rate: %s\n", h_metric_e10$success_env))
cat(sprintf("Success rate: %s\n", h_metric_e10$success_fac))

```




## Environmental filtering 20 species

### JSDM

```{r load_m en20}
me20 <- load_object("model-2019-04-11-19-06-02.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me20)

me20$mcmc.info[1:7]

jsdm_conv(me20)

j_metric_e20<-metrics_jsdm(me20)
cat("Success rate ")
j_metric_e20$success_env

data<-sim_data$EnvEvenSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################

plot_cor_jsdm(me20,data$Y)

```


### Gjam

```{r gjam en20}

data<-sim_data$EnvEvenSp20

#Rho_sign<-fit_gjam(data,5000,500,"./gjam_models/gjam20env.rda")

Rho_sign<-load_gjam(data,name="./gjam_models/gjam20env.rda")
#gje20<-load_object("./gjam_models/gjam20env.rda")

g_metric_e20<-metrics_gjam(Rho_sign)
cat("Success rate ")
#g_metric_e20$success_env

cat(" ")
cat(sprintf("Success rate env: %s\n", round(metrics_gjam(Rho_sign)$success_env,3)))

#to check posterior density of s in Sigma 
#gje20<-load_object("./gjam_models/gjam20env.rda")
#plot(density(gje20$chains$sgibbs[,4]))


```

### Gjam dimension reduction

```{r gjam en20 dim red}

data<-sim_data$EnvEvenSp20

#fit_gjam(data,5000,500,"./gjam_models/gjam20env.rda")

#load_gjam(data,name="./gjam_models/gjam20env.rda")
#gje20<-load_object("./gjam_models/gjam20env.rda")


#to check posterior density of s in Sigma 
#gje20<-load_object("./gjam_models/gjam20env.rda")
#plot(density(gje20$chains$sgibbs[,4]))
 data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )
xdata<-as.data.frame(data$X[,-1])
colnames(xdata)<- c("env","env2")
ydata<-as.data.frame(data$Y)
###formula
rl   <- list(r = 8, N = 20)
formula<-as.formula( ~env+ env2)
ml  <- list(ng = 2500, burnin = 500, typeNames = 'PA', reductList = rl)
####fit


mod_gjam1 <- gjam(formula, xdata = xdata, ydata = ydata, modelList = ml)
save(mod_gjam1, file = "./gjam_models/gjam20env_dr.rda")
summary(mod_gjam1)

Tau <- solve(mod_gjam1$parameters$sigMu)
Tau_n = to_prec(Tau)

#postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
#postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)


#pH<-convert_to_m(postH)
#pL<-convert_to_m(postL)

#R_sign<-cov2cor(mod_gjam1$parameters$sigMu)*(!(pH>0 & pL<0))

g_metric_e20_dim_red<-metrics_gjam(Rho_sign)
cat("Success rate ")
g_metric_e20_dim_red$success_env

par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
corrplot(cor(ydata), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Correlation cor(Y)")
corrplot(mod_gjam1$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("R")
corrplot(mod_gjam1$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("E matrix")
# corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("Tau")
# corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("R signif")
corrplot(diag(20), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("True interactions")



```

```{r hmsc en20}

data<-sim_data$EnvEvenSp20
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm20env.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod)

h_metric_e20<-metrics_hmsc(Rho_sign)
cat("Success score ")
h_metric_e20$success_env
cat(" ")
cat(sprintf("Success rate non-interacting: %s\n", round(metrics_hmsc(Rho_sign)$success_env,3)))

```

## Environmental filtering + Facilitation dense 5 species

### JSDM

```{r load_m facd5}
mfd5 <- load_object("model-2019-04-11-19-35-11.rda")
summary(mfd5)
#mfd5$Rhat
jsdm_conv(mfd5)
mfd5$mcmc.info[1:7]

j_metric_facDense5<-metrics_jsdm(mfd5,fac = fac_inter[[4]],only_env = F)
cat("Success rate ")
j_metric_facDense5$success_env
j_metric_facDense5$success_fac

data<-sim_data$FacDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

plot_cor_jsdm(mfd5,data$Y,fac_inter[[4]])

```

### Gjam

```{r gjam fd5}
data<-sim_data$FacDenseSp5
#Rho_sign<-fit_gjam(data,10000,2000,"./gjam_models/gjam5f.rda",interact=fac_inter[[4]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjam5f.rda", interact=fac_inter[[4]])
#gjfd5<-load_object("./gjam_models/gjam5f.rda")

g_metric_facDense5<-metrics_gjam(Rho_sign,fac=fac_inter[[4]], only_env = F)
#cat("Success rate ")
#g_metric_facDense5$success_env
#g_metric_facDense5$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5f.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facDense5$success_fac,3)))

```



### HMSC
```{r hmsc fd5}
data<-sim_data$FacDenseSp5
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm5fd.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod, interact = fac_inter[[4]])
Rho_sign<-hm_inter(hm_mod)

h_metric_facDense5<-metrics_hmsc(Rho_sign,fac=fac_inter[[4]],only_env = F)
#cat("Success rate ")
# h_metric_facDense5$success_env
# h_metric_facDense5$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facDense5$success_fac,3)))


```

## Environmental filtering + Facilitation dense 10 species

### JSDM

```{r model jsdm fd10, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfd10 <- load_object("model-2019-04-12-06-59-42.rda")

summary(mfd10)
jsdm_conv(mfd10)
mfd10$mcmc.info[1:7]

j_metric_facDense10<-metrics_jsdm(mfd10,fac = fac_inter[[5]],only_env = F)
cat("Success rate ")
j_metric_facDense10$success_env
j_metric_facDense10$success_fac

######################################################Prepare data
data<-sim_data$FacDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

######################################################Plot 

plot_cor_jsdm(mfd10,data$Y,fac_inter[[5]])

```


```{r gjam fd10}

data<-sim_data$FacDenseSp10

#Rho_sign<-fit_gjam(data,5000,500,"./gjam_models/gjam10fd.rda",interact=fac_inter[[5]])
load_gjam(data,name="./gjam_models/gjam10fd.rda", interact=fac_inter[[5]])
#gjfd5<-load_object("./gjam_models/gjam10fd.rda")

g_metric_facDense10<-metrics_gjam(Rho_sign,fac=fac_inter[[5]], only_env = F)
# cat("Success rate ")
# g_metric_facDense10$success_env
# g_metric_facDense10$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam10fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facDense10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facDense10$success_fac,3)))


```


### HMSC

```{r model2 hmsc, echo=FALSE}
data<-sim_data$FacDenseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples = 2000,nchains=2,name="./HMmodels/hm10fd.rda" )
hm_conv(hm_mod)
Rho_sigh<-hm_inter(hm_mod, nsamples = 2000,nchains=2,interact = fac_inter[[5]])

h_metric_facDense10<-metrics_hmsc(Rho_sign,fac=fac_inter[[5]],only_env = F)
# cat("Success rate ")
# h_metric_facDense10$success_env
# h_metric_facDense10$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facDense10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facDense10$success_fac,3)))


```




## Environmental filtering + Facilitation dense 20 species

### JSDM

```{r model jsdm fd20, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfd20 <- load_object("model-2019-04-13-17-22-12.rda")

summary(mfd20)
#mfd20$Rhat
jsdm_conv(mfd20)
mfd20$mcmc.info[1:7]

j_metric_facDense20<-metrics_jsdm(mfd20,fac = fac_inter[[6]],only_env = F)
cat("Success rate ")
j_metric_facDense20$success_env
j_metric_facDense20$success_fac

######################################################Prepare data
data<-sim_data$FacDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

#Tau_n<-to_prec(mfd20$mean$Tau)
plot_cor_jsdm(mfd20,data$Y,fac_inter[[6]])

```


### Gjam


```{r gjam fd20}

data<-sim_data$FacDenseSp20

#Rho_sign<-fit_gjam(data,10000,1500,"./gjam_models/gjam20fd.rda",interact=fac_inter[[6]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjam20fd.rda", interact=fac_inter[[6]])
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")

g_metric_facDense20<-metrics_gjam(Rho_sign,fac=fac_inter[[6]], only_env = F)
# cat("Success rate ")
# g_metric_facDense20$success_env
# g_metric_facDense20$success_fac
# 
#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facDense20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facDense20$success_fac,3)))



```


### HMSC
```{r hmsc fd20}
data<-sim_data$FacDenseSp20
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm20fd.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, interact = fac_inter[[6]])

h_metric_facDense20<-metrics_hmsc(Rho_sign,fac=fac_inter[[6]],only_env = F)
# cat("Success rate ")
# h_metric_facDense20$success_env
# h_metric_facDense20$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facDense20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facDense20$success_fac,3)))

```



## Environmental filtering + Facilitation sparse 5 species

### JSDM


```{r model jsdm fs5, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs5 <- load_object("model-2019-04-13-17-51-16.rda")

summary(mfs5)
#mfs5$Rhat
jsdm_conv(mfs5)

mfs5$mcmc.info[1:7]

j_metric_facSparse5<-metrics_jsdm(mfs5,fac = fac_inter[[7]],only_env = F)
# cat("Success rate ")
# j_metric_facSparse5$success_env
# j_metric_facSparse5$success_fac
# cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_facSparse5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_facSparse5$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfs5,data$Y,fac_inter[[7]])
```


### Gjam

```{r gjam fs5}

data<-sim_data$FacSparseSp5

#Rho_sign<-fit_gjam(data,2500,500,"./gjam_models/gjam5fs.rda",interact=fac_inter[[7]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjam5fs.rda", interact=fac_inter[[7]])
#gjfd5<-load_object("./gjam_models/gjam5fs.rda")

g_metric_facSparse5<-metrics_gjam(Rho_sign,fac=fac_inter[[7]], only_env = F)
# cat("Success rate ")
# g_metric_facSparse5$success_env
# g_metric_facSparse5$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facSparse5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facSparse5$success_fac,3)))

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```

### HMSC
```{r hmsc fs5}
data<-sim_data$FacSparseSp5

hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm5fs.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, interact = fac_inter[[7]])
h_metric_facSparse5<-metrics_hmsc(Rho_sign,fac=fac_inter[[8]],only_env = F)
# cat("Success rate ")
# h_metric_facSparse5$success_env
# h_metric_facSparse5$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse5$success_fac,3)))

```







## Environmental filtering + Facilitation sparse 10 species

### JSDM

```{r model jsdm fs10, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs10 <- load_object("model-2019-04-14-05-17-58.rda")

summary(mfs10)
#mfs10$Rhat
jsdm_conv(mfs10)
mfs10$mcmc.info[1:7]

j_metric_facSparse10<-metrics_jsdm(mfd10,fac = fac_inter[[8]],only_env = F)
# cat("Success rate ")
# j_metric_facSparse10$success_env
# j_metric_facSparse10$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_facSparse10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_facSparse10$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfs10,data$Y,fac_inter[[8]])
```

```{r gjam fs10}

data<-sim_data$FacSparseSp10

#Rho_sign<-fit_gjam(data,2500,500,"./gjam_models/gjam10fs.rda",interact=fac_inter[[8]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjam10fs.rda", interact=fac_inter[[8]])
#gjfd5<-load_object("./gjam_models/gjam10fs.rda")

g_metric_facSparse10<-metrics_gjam(Rho_sign,fac=fac_inter[[8]], only_env = F)
# cat("Success rate ")
# g_metric_facSparse10$success_env
# g_metric_facSparse10$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam10fs.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facSparse10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facSparse10$success_fac,3)))


```

### HMSC
```{r hmsc fs10}
data<-sim_data$FacSparseSp10

hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm10fs.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, interact = fac_inter[[8]])
h_metric_facSparse10<-metrics_hmsc(Rho_sign,fac=fac_inter[[8]],only_env = F)
# cat("Success rate ")
# h_metric_facSparse10$success_env
# h_metric_facSparse10$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse10$success_fac,3)))

```



## Environmental filtering + Facilitation sparse 20 species

### JSDM


```{r model jsdm fs20, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs20 <- load_object("model-2019-04-15-15-34-20.rda")

summary(mfs20)
#mfs20$Rhat
jsdm_conv(mfs20)
mfs20$mcmc.info[1:7]

j_metric_facSparse20<-metrics_jsdm(mfs20,fac = fac_inter[[9]],only_env = F)
# cat("Success rate ")
# j_metric_facSparse20$success_env
# j_metric_facSparse20$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_facSparse20$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfs20,data$Y,fac_inter[[9]])
```


### Gjam

```{r gjam fs20}

data<-sim_data$FacSparseSp20

#fit_gjam(data,10000,1500,"./gjam_models/gjam20fs.rda",interact=fac_inter[[9]])
load_gjam(data,name="./gjam_models/gjam20fs.rda", interact=fac_inter[[9]])
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")

g_metric_facSparse20<-metrics_gjam(Rho_sign,fac=fac_inter[[9]], only_env = F)
# cat("Success rate ")
# g_metric_facSparse20$success_env
# g_metric_facSparse20$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facSparse20$success_fac,3)))


```


### HMSC

### HMSC
```{r hmsc fs20}
data<-sim_data$FacSparseSp20
hm_mod<-fit_hmsc(data,nsamples=3000, nchains=2,"Load",name="./HMmodels/hm20fs.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod, nsamples=3000, nchains=2,interact = fac_inter[[9]])
h_metric_facSparse20<-metrics_hmsc(Rho_sign,fac=fac_inter[[9]],only_env = F)
# cat("Success rate ")
# h_metric_facSparse20$success_env
# h_metric_facSparse20$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse20$success_fac,3)))

```


## Environmental filtering + Competition dense 5 species

### JSDM


```{r model jsdm cmpd5, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd5 <- load_object("model-2019-04-15-16-03-39.rda")

summary(mcmpd5)
#mcmpd5$Rhat
jsdm_conv(mcmpd5)

mcmpd5$mcmc.info[1:7]

j_metric_compDense5<-metrics_jsdm(mcmpd5,comp = comp_inter[[10]],only_env = F)
cat("Success rate ")
j_metric_compDense5$success_env
j_metric_compDense5$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse20$success_fac,3)))

######################################################Prepare data
data<-sim_data$CompDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mcmpd5,data$Y,comp_inter[[10]])
```



### Gjam

```{r gjam cmpd5}
data<-sim_data$CompDenseSp5

#Rho_sign<-fit_gjam(data,10000,1000,"./gjam_models/gjam5cmpd.rda",interact=comp_inter[[10]])

Rho_sign<-load_gjam(data,name="./gjam_models/gjam5cmpd.rda", interact=(-1)*comp_inter[[10]])
#gjfd5<-load_object("./gjam_models/gjam5cmpd.rda")

g_metric_compDense5<-metrics_gjam(Rho_sign,comp=comp_inter[[10]], only_env = F)
# cat("Success rate ")
# g_metric_compDense5$success_env
# g_metric_compDense5$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_compDense5$success_comp,3)))

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5cmpd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```


```{r hmsc cmpd5}
data<-sim_data$CompDenseSp5

hm_mod<-fit_hmsc(data,"Load",nsamples=3000, nchains=2,name="./HMmodels/hm5cmpd.rda" )
#hm_mod<-fit_hmsc(data,"Fit",nsamples=3000, nchains=2 )

hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=3000, nchains=2,interact = (-1)*comp_inter[[10]])

h_metric_compDense5<-metrics_hmsc(Rho_sign,comp=comp_inter[[10]],only_env = F)
# cat("Success rate ")
# h_metric_compDense5$success_env
# h_metric_compDense5$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_compDense5$success_comp,3)))

```


## Environmental filtering + Competition dense 10 species

```{r model jsdm cmpd10, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd10 <- load_object("model-2019-04-16-03-39-17.rda")

summary(mcmpd10)
#mcmpd10$Rhat

jsdm_conv(mcmpd10)
mcmpd10$mcmc.info[1:7]

j_metric_compDense10<-metrics_jsdm(mcmpd10,comp = comp_inter[[11]],only_env = F)
# cat("Success rate ")
# j_metric_compDense10$success_env
# j_metric_compDense10$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compDense10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_compDense10$success_comp,3)))

######################################################Prepare data
data<-sim_data$CompDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mcmpd10,data$Y,(-1)*comp_inter[[11]])
```



### Gjam

```{r gjam cmpd10}
data<-sim_data$CompDenseSp10

#Rho_sign<-fit_gjam(data,5000,500,"./gjam_models/gjam10cmpd.rda",interact=comp_inter[[11]])

Rho_sign<-load_gjam(data,name="./gjam_models/gjam10cmpd.rda", interact= (-1)*comp_inter[[11]])
#gjfd5<-load_object("./gjam_models/gjam10cmpd.rda")

g_metric_compDense10<-metrics_gjam(Rho_sign,comp=comp_inter[[11]], only_env = F)
# cat("Success rate ")
# g_metric_compDense10$success_env
# g_metric_compDense10$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compDense10$success_comp,3)))


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```


### HMSC

```{r hmsc cmpd10}
data<-sim_data$CompDenseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples=5000, nchains=2,name="./HMmodels/hm10cmpd.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod,nsamples=5000, nchains=2, interact =  (-1)*comp_inter[[11]])

h_metric_compDense10<-metrics_hmsc(Rho_sign,comp=comp_inter[[11]],only_env = F)
# cat("Success rate ")
# h_metric_compDense10$success_env
# h_metric_compDense10$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compDense10$success_comp,3)))


```



## Environmental filtering + Competition dense 20 species

```{r model jsdm cmpd20, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd20 <- load_object("model-2019-04-17-14-00-45.rda")

summary(mcmpd20)
#mcmpd10$Rhat

jsdm_conv(mcmpd20)
mcmpd20$mcmc.info[1:7]

j_metric_compDense20<-metrics_jsdm(mcmpd20,comp = comp_inter[[12]],only_env = F)
# cat("Success rate ")
# j_metric_compDense20$success_env
# j_metric_compDense20$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compDense20$success_comp,3)))

######################################################Prepare data
data<-sim_data$CompDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mcmpd20,data$Y, (-1)*comp_inter[[12]])
```



### Gjam

```{r gjam cmpd20}
data<-sim_data$CompDenseSp20

#Rho_sign<-fit_gjam(data,10000,1000,"./gjam_models/gjam20cmpd.rda",interact= (-1)*comp_inter[[12]])

Rho_sign<-load_gjam(data,name="./gjam_models/gjam20cmpd.rda", interact= (-1)*comp_inter[[12]])
#gjfd5<-load_object("./gjam_models/gjam20cmpd.rda")

g_metric_compDense20<-metrics_gjam(Rho_sign,comp=comp_inter[[12]], only_env = F)
# cat("Success rate ")
# g_metric_compDense20$success_env
# g_metric_compDense20$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compDense20$success_comp,3)))


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```


### HMSC

```{r hmsc cmpd20}
data<-sim_data$CompDenseSp20

hm_mod<-fit_hmsc(data,"Load",nsamples=5000, nchains=2,name="./HMmodels/hm20cmpd.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=5000, nchains=2,interact =  (-1)*comp_inter[[12]])

h_metric_compDense20<-metrics_hmsc(Rho_sign,comp=comp_inter[[12]],only_env = F)
# cat("Success rate ")
# h_metric_compDense20$success_env
# h_metric_compDense20$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compDense20$success_comp,3)))


```



## Environmental filtering + Competition sparse 5 species

```{r model jsdm cmps5, echo=FALSE}
#load("model-2019-04-17-14-30-01.rda")
cmps5 <- load_object("model-2019-04-17-14-30-01.rda")

summary(cmps5)
jsdm_conv(cmps5)
cmps5$mcmc.info[1:7]

j_metric_compSparse5<-metrics_jsdm(cmps5,comp = comp_inter[[13]],only_env = F)
# cat("Success rate ")
# j_metric_compSparse5$success_env
# j_metric_compSparse5$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compSparse5$success_comp,3)))



######################################################Prepare data
data<-sim_data$CompSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmps5,data$Y,(-1)*comp_inter[[13]])
```




### Gjam

```{r gjam cmps5}
data<-sim_data$CompSparseSp5


#Rho_sign<-fit_gjam(data,5000,2000,"./gjam_models/gjam5cmps.rda",interact= (-1)*comp_inter[[13]])

Rho_sign<-load_gjam(data,name="./gjam_models/gjam5cmps.rda", interact= (-1)*comp_inter[[13]])
#gjfd5<-load_object("./gjam_models/gjam5cmps.rda")

g_metric_compSparse5<-metrics_gjam(Rho_sign,comp=comp_inter[[13]], only_env = F)
cat("Success rate ")
g_metric_compSparse5$success_env
g_metric_compSparse5$success_comp


cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compSparse5$success_comp,3)))


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5cmps.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```


### HMSC

```{r hmsc cmps5}
data<-sim_data$CompSparseSp5

hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hm5cmps.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[13]])

h_metric_compSparse5<-metrics_hmsc(Rho_sign,comp=comp_inter[[13]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compSparse5$success_comp,3)))


```



## Environmental filtering + Competition sparse 10 species


### JSDM

```{r model jsdm cmps10, echo=FALSE}
#load("model-2019-04-17-14-30-01.rda")
cmps10 <- load_object("model-2019-04-18-01-55-45.rda")

summary(cmps10)
jsdm_conv(cmps10)
cmps10$mcmc.info[1:7]

j_metric_compSparse10<-metrics_jsdm(cmps10,comp = comp_inter[[14]],only_env = F)
cat("Success rate ")
j_metric_compSparse10$success_env
j_metric_compSparse10$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compSparse10$success_comp,3)))


######################################################Prepare data
data<-sim_data$CompSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmps10,data$Y,(-1)*comp_inter[[14]])

```


### Gjam

```{r gjam cmps10}
data<-sim_data$CompSparseSp10
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjam10cmps.rda",interact= (-1)*comp_inter[[14]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjam10cmps.rda", interact= (-1)*comp_inter[[14]])

g_metric_compSparse10<-metrics_gjam(Rho_sign,comp=comp_inter[[14]], only_env = F)
# cat("Success rate ")
# g_metric_compSparse10$success_env
# g_metric_compSparse10$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compSparse10$success_comp,3)))


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam10cmps.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
```


```{r hmsc cmps10}
data<-sim_data$CompSparseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hm10cmps.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[14]])

h_metric_compSparse10<-metrics_hmsc(Rho_sign,comp=comp_inter[[14]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compSparse10$success_comp,3)))


```

## Environmental filtering + Competition sparse 20 species

### JSDM 

```{r model jsdm cmps20, echo=FALSE}
#load("model-2019-04-17-14-30-01.rda")
cmps20 <- load_object("model-2019-04-19-12-40-30.rda")

summary(cmps20)
jsdm_conv(cmps20)
cmps20$mcmc.info[1:7]

j_metric_compSparse20<-metrics_jsdm(cmps20,comp = comp_inter[[15]],only_env = F)
# cat("Success rate ")
# j_metric_compSparse10$success_env
# j_metric_compSparse10$success_comp
# 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compSparse20$success_comp,3)))


######################################################Prepare data
data<-sim_data$CompSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmps20,data$Y,(-1)*comp_inter[[15]])

```

### Gjam

```{r gjam cmps20}
data<-sim_data$CompSparseSp20
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjam20cmps.rda",interact= (-1)*comp_inter[[15]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjam20cmps.rda", interact= (-1)*comp_inter[[15]])

g_metric_compSparse20<-metrics_gjam(Rho_sign,comp=comp_inter[[15]], only_env = F)
# cat("Success rate ")
# g_metric_compSparse20$success_env
# g_metric_compSparse20$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compSparse20$success_comp,3)))


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20cmps.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
```


### HMSC

```{r hmsc cmps20}
data<-sim_data$CompSparseSp20

hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hm20cmps.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[15]])

h_metric_compSparse20<-metrics_hmsc(Rho_sign,comp=comp_inter[[15]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compSparse20$success_comp,3)))

```






## Environmental filtering + Competition +Facilitation 5 dense species

### JSDM 

```{r model jsdm cmp_facd5, echo=FALSE}
cmp_fd5 <- load_object("model-2019-04-19-13-08-47.rda")
summary(cmp_fd5)
jsdm_conv(cmp_fd5)
cmp_fd5$mcmc.info[1:7]
j_metric_FacCompDense5<-metrics_jsdm(cmp_fd5,comp = comp_inter[[16]],fac = fac_inter[[16]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompDense5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompDense5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompDense5$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacCompDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmp_fd5,data$Y,(-1)*comp_inter[[16]]+fac_inter[[16]])

```


### Gjam

```{r gjam cmp_facd5}
data<-sim_data$FacCompDenseSp5
#Rho_sign<-fit_gjam(data,30000,15000,"./gjam_models/gjam5cmp_facd.rda",interact= (-1)*comp_inter[[16]]+fac_inter[[16]])
Rho_sign2<-load_gjam(data,"./gjam_models/gjam5cmp_facd2.rda",interact= (-1)*comp_inter[[16]]+fac_inter[[16]])
#Rho_sign3<-fit_gjam(data,5000,1000,"./gjam_models/gjam5cmp_facd2.rda",interact= (-1)*comp_inter[[16]]+fac_inter[[16]])
#Rho_sign4<-fit_gjam(data,5000,2500,"./gjam_models/gjam5cmp_facd.rda",interact= (-1)*comp_inter[[16]]+fac_inter[[16]])
#Rho_sign5<-fit_gjam(data,20000,5000,"./gjam_models/gjam5cmp_facd2.rda",interact= (-1)*comp_inter[[16]]+fac_inter[[16]])
#Rho_sign<-load_gjam(data,name="./gjam_models/gjam5cmp_facd.rda", (-1)*comp_inter[[16]]+fac_inter[[16]])

g_metric_FacCompDense5<-metrics_gjam(Rho_sign2,comp=comp_inter[[16]], fac=fac_inter[[16]], only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompDense5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompDense5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompDense5$success_fac,3)))




# par(mfrow=c(2,3))
#corrplot((Rho_sign+Rho_sign2)/2, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
# corrplot(Rho_sign2, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
# corrplot(Rho_sign3, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
# corrplot(Rho_sign4, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
# corrplot(Rho_sign5, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20cmps.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
```



### HMSC

```{r hmsc cmp_facd5}
data<-sim_data$FacCompDenseSp5
hm_mod<-fit_hmsc(data,"Load",nsamples=3000, nchains=2,name="./HMmodels/hmcmp_facd5.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=3000, nchains=2,interact =  (-1)*comp_inter[[16]]+ fac_inter[[16]])

h_metric_FacCompDense5<-metrics_hmsc(Rho_sign,comp=comp_inter[[16]],fac= fac_inter[[16]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompDense5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompDense5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompDense5$success_fac,3)))

```




## Environmental filtering + Competition +Facilitation 10 dense species

### JSDM 

```{r model jsdm cmp_facd10, echo=FALSE}
cmp_fd10 <- load_object("model-2019-04-20-00-37-25.rda")
# 
summary(cmp_fd10)
jsdm_conv(cmp_fd10)
cmp_fd10$mcmc.info[1:7]
# 
j_metric_FacCompDense10<-metrics_jsdm(cmp_fd10,comp = comp_inter[[17]],fac=fac_inter[[17]],only_env = F)
# # cat("Success rate ")
# # j_metric_compSparse10$success_env
# # j_metric_compSparse10$success_comp
# # 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompDense10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompDense10$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmp_fd10,data$Y,(-1)*comp_inter[[17]] +fac_inter[[17]] )

```

### Gjam

```{r gjam cmp_facd10}
data<-sim_data$FacCompDenseSp10
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facd10.rda",interact=  (-1)*comp_inter[[17]]+fac_inter[[17]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjamcmp_facd10.rda", interact= (-1)*comp_inter[[17]]+fac_inter[[17]])

g_metric_FacCompDense10<-metrics_gjam(Rho_sign,comp=comp_inter[[17]], fac=fac_inter[[17]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompDense10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompDense10$success_fac,3)))

```


### HMSC

```{r hmsc cmp_facd10}
  
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facd10.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[17]] + fac_inter[[17]])

h_metric_FacCompDense10<-metrics_hmsc(Rho_sign,comp=comp_inter[[17]],fac=fac_inter[[17]], only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompDense10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompDense10$success_fac,3)))

```


## Environmental filtering + Competition +Facilitation 20 dense species

### JSDM 

```{r model jsdm cmp_facd20, echo=FALSE}

cmp_fd20 <- load_object("model-2019-04-21-11-10-34.rda")

summary(cmp_fd20)
jsdm_conv(cmp_fd20)
cmp_fd20$mcmc.info[1:7]
# 
j_metric_FacCompDense20<-metrics_jsdm(cmp_fd20,comp = comp_inter[[18]],fac=fac_inter[[18]],only_env = F)
# # cat("Success rate ")
# # j_metric_compSparse10$success_env
# # j_metric_compSparse10$success_comp
# # 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompDense20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompDense20$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmp_fd20,data$Y,(-1)*comp_inter[[18]] +fac_inter[[18]] )

```


### Gjam

```{r gjam cmp_facd20}
data<-sim_data$FacCompDenseSp20
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facd20.rda",interact=  (-1)*comp_inter[[18]]+fac_inter[[18]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjamcmp_facd20.rda", interact= (-1)*comp_inter[[18]]+fac_inter[[18]])

g_metric_FacCompDense20<-metrics_gjam(Rho_sign,comp=comp_inter[[18]], fac=fac_inter[[18]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompDense20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompDense20$success_fac,3)))

```


### HMSC

```{r hmsc cmp_facd20}
data<-sim_data$FacCompDenseSp20
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facd20.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[18]] + fac_inter[[18]])
h_metric_FacCompDense20<-metrics_hmsc(Rho_sign,comp=comp_inter[[18]],fac=fac_inter[[18]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompDense20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompDense20$success_fac,3)))

```



## Environmental filtering + Competition +Facilitation 5 sparse species

### JSDM 

```{r model jsdm cmp_facs5, echo=FALSE}
cmp_fds5 <- load_object("model-2019-04-21-11-39-52.rda")
# 
summary(cmp_fds5)
jsdm_conv(cmp_fds5)
cmp_fds5$mcmc.info[1:7]
# 
j_metric_FacCompSparse5<-metrics_jsdm(cmp_fds5,comp = comp_inter[[19]],fac=fac_inter[[19]],only_env = F)
# # cat("Success rate ")
# # j_metric_compSparse10$success_env
# # j_metric_compSparse10$success_comp
# # 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompSparse5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompSparse5$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmp_fds5,data$Y,(-1)*comp_inter[[19]] +fac_inter[[19]] )
```

### Gjam

```{r gjam cmp_facs5}
data<-sim_data$FacCompSparseSp5
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facs5.rda",interact= (-1)*comp_inter[[19]]+ fac_inter[[19]] )
Rho_sign<-load_gjam(data,name="./gjam_models/gjamcmp_facs5.rda", interact=  (-1)*comp_inter[[19]]+ fac_inter[[19]])
g_metric_FacCompSparse5<-metrics_gjam(Rho_sign,comp=comp_inter[[15]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse5$success_comp,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse5$success_comp,3)))

```


### HMSC

```{r hmsc cmp_facs5}
data<-sim_data$FacCompSparseSp5
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facs5.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[19]]+ fac_inter[[19]])
 
h_metric_FacCompSparse5<-metrics_hmsc(Rho_sign,comp=comp_inter[[19]],fac= fac_inter[[19]] ,only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompSparse5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompSparse5$success_fac,3)))

```



## Environmental filtering + Competition +Facilitation 10 sparse species

### JSDM 

```{r model jsdm cmp_facs10, echo=FALSE}
cmp_fds10 <- load_object("model-2019-04-21-22-58-58.rda")
# 
summary(cmp_fds10)
jsdm_conv(cmp_fds10)
cmp_fds10$mcmc.info[1:7]
# 
j_metric_FacCompSparse10<-metrics_jsdm(cmp_fds10,comp = comp_inter[[20]],fac=fac_inter[[20]],only_env = F)
# # cat("Success rate ")
# # j_metric_compSparse10$success_env
# # j_metric_compSparse10$success_comp
# # 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompSparse10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompSparse10$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmp_fds10,data$Y,(-1)*comp_inter[[20]] +fac_inter[[20]] )
```


### Gjam

```{r gjam cmp_facs10}
data<-sim_data$FacCompSparseSp10
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facs10.rda",interact= (-1)*comp_inter[[20]] +fac_inter[[20]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjamcmp_facs10.rda", interact=  (-1)*comp_inter[[20]] +fac_inter[[20]])

g_metric_FacCompSparse10<-metrics_gjam(Rho_sign,comp=comp_inter[[20]],fac=fac_inter[[20]], only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompSparse10$success_fac,3)))

```


### HMSC

```{r hmsc cmp_facs10}
data<-sim_data$FacCompSparseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facs10.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[20]] +fac_inter[[20]])

h_metric_FacCompSparse10<-metrics_hmsc(Rho_sign,comp=comp_inter[[20]],fac=fac_inter[[20]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompSparse10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompSparse10$success_fac,3)))

```



## Environmental filtering + Competition +Facilitation 20 sparse species

### JSDM 

```{r model jsdm cmp_facs20, echo=FALSE}
cmp_fds20 <- load_object("model-2019-04-23-09-42-18.rda")

summary(cmp_fds20)
jsdm_conv(cmp_fds20)
cmp_fds20$mcmc.info[1:7]
# 
j_metric_FacCompSparse20<-metrics_jsdm(cmp_fds20,comp = comp_inter[[21]],fac=fac_inter[[21]],only_env = F)
# # cat("Success rate ")
# # j_metric_compSparse10$success_env
# # j_metric_compSparse10$success_comp
# # 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompSparse20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompSparse20$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

plot_cor_jsdm(cmp_fds20,data$Y,(-1)*comp_inter[[21]] +fac_inter[[21]] )
```

### Gjam

```{r gjam cmp_facs20}
data<-sim_data$FacCompSparseSp20
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facs20.rda",interact= (-1)*comp_inter[[21]]+fac_inter[[21]])
Rho_sign<-load_gjam(data,name="./gjam_models/gjamcmp_facs20.rda", interact= (-1)*comp_inter[[21]]+fac_inter[[21]])
g_metric_FacCompSparse20<-metrics_gjam(Rho_sign,comp=comp_inter[[21]], fac=fac_inter[[21]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompSparse20$success_fac,3)))

```

### HMSC

```{r hmsc cmp_facs20}
data<-sim_data$FacCompSparseSp20
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facs20.rda" )
hm_conv(hm_mod)
Rho_sign<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[21]] +fac_inter[[21]])
h_metric_FacCompSparse20<-metrics_hmsc(Rho_sign,comp=comp_inter[[21]],fac=fac_inter[[21]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompSparse20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompSparse20$success_fac,3)))

```




## Graph from paper

```{r combined models, echo=FALSE, warning=FALSE}

models<-list(EnvEvenSp5=me5,EnvEvenSp10=me10, EnvEvenSp20=me20,FacDenseSp5 =mfd5, FacDenseSp10=mfd10, FacDenseSp20=mfd20,
             FacSparseSp5 =mfs5, FacSparseSp10=mfs10, FacSparseSp20=mfs20, CompDenseSp5=mcmpd5,CompDenseSp10=mcmpd10,CompDenseSp20=mcmpd20)

mean_correlations <- mean_cor(models)
x <- subset(mean_correlations, type != "Environmental\nFiltering Only")
acc <- by(x, x$model, function(x) sum(x$status == "TP" | x$status == "TN") / nrow(x))

#' Plot correlation parameter means
#+ plot-correlations
ggplot(mean_correlations) +
  aes(factor(nsp), rho, fill = interaction) +
  geom_hline(yintercept = 0) +
  geom_boxplot(
    outlier.size = .2, size = .1, position = position_dodge(preserve = "single")
  ) +
  scale_fill_manual(values = c("grey", "blue", "red")) +
  facet_grid(type ~ rho_type + density, switch = "y") +
  xlab("Number of species") +
  ylab("Correlation") +
  theme_bw() +
  theme(legend.position = "top")






# first part just for me to create fake variables

# h_metric_e5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# g_metric_e5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# j_metric_e5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# h_metric_e10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# g_metric_e10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# j_metric_e10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# h_metric_e20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# g_metric_e20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# j_metric_e20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=NULL)
# 
# h_metric_facDense5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# g_metric_facDense5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# j_metric_facDense5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# h_metric_facDense10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# g_metric_facDense10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# j_metric_facDense10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# h_metric_facDense20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# g_metric_facDense20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# j_metric_facDense20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# 
# h_metric_compSparse5<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# g_metric_compSparse5<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# j_metric_compSparse5<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# h_metric_compSparse10<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# g_metric_compSparse10<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# j_metric_compSparse10<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# h_metric_compSparse20<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# g_metric_compSparse20<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# j_metric_compSparse20<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# 
# 
# h_metric_compDense5<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# g_metric_compDense5<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# j_metric_compDense5<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# h_metric_compDense10<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# g_metric_compDense10<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# j_metric_compDense10<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# h_metric_compDense20<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# g_metric_compDense20<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# j_metric_compDense20<- list("success_env"=runif(1,0,1),"success_fac"=NULL,"success_comp"=runif(1,0,1))
# 
# h_metric_facSparse5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# g_metric_facSparse5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# j_metric_facSparse5<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# h_metric_facSparse10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# g_metric_facSparse10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# j_metric_facSparse10<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# h_metric_facSparse20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# g_metric_facSparse20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# j_metric_facSparse20<- list("success_env"=runif(1,0,1),"success_comp"=NULL,"success_fac"=runif(1,0,1))
# 
# g_metric_FacCompSparseSp5<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# h_metric_FacCompSparseSp5<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# j_metric_FacCompSparseSp5<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# g_metric_FacCompSparseSp10<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# h_metric_FacCompSparseSp10<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# j_metric_FacCompSparseSp10<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# g_metric_FacCompSparseSp20<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# h_metric_FacCompSparseSp20<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# j_metric_FacCompSparseSp20<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# 
# g_metric_FacCompDenseSp5<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# h_metric_FacCompDenseSp5<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# j_metric_FacCompDenseSp5<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# g_metric_FacCompDenseSp10<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# h_metric_FacCompDenseSp10<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# j_metric_FacCompDenseSp10<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# g_metric_FacCompDenseSp20<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# h_metric_FacCompDenseSp20<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))
# j_metric_FacCompDenseSp20<- list("success_env"=runif(1,0,1),"success_comp"=runif(1,0,1),"success_fac"=runif(1,0,1))

all<-list("j_metric_e5"=j_metric_e5,"g_metric_e5"=g_metric_e5,"h_metric_e5"=h_metric_e5,
          "j_metric_e10"=j_metric_e10,"g_metric_e10"=g_metric_e10,"h_metric_e10"=h_metric_e10,
          "j_metric_e20"=j_metric_e20,"g_metric_e20"=g_metric_e20,"h_metric_e20"=h_metric_e20,
          "h_metric_facDense5"=h_metric_facDense5,"g_metric_facDense5"=g_metric_facDense5,"j_metric_facDense5"=j_metric_facDense5,
          "h_metric_facDense10"=h_metric_facDense10,"g_metric_facDense10"=g_metric_facDense10,"j_metric_facDense10"=j_metric_facDense10,
          "h_metric_facDense20"=h_metric_facDense20,"g_metric_facDense20"=g_metric_facDense20,"j_metric_facDense20"=j_metric_facDense20,
          "h_metric_facSparse5"=h_metric_facSparse5,"g_metric_facSparse5"=g_metric_facSparse5,"j_metric_facSparse5"=j_metric_facSparse5,
          "h_metric_facSparse10"=h_metric_facSparse10,"g_metric_facSparse10"=g_metric_facSparse10,"j_metric_facSparse10"=j_metric_facSparse10,
          "h_metric_facSparse20"=h_metric_facSparse20,"g_metric_facSparse20"=g_metric_facSparse20,"j_metric_facSparse10"=j_metric_facSparse20,
          "h_metric_compDense5"=h_metric_compDense5,"g_metric_compDense5"=g_metric_compDense5,"j_metric_compDense5"=j_metric_compDense5,
          "h_metric_compDense10"=h_metric_compDense10,"g_metric_compDense10"=g_metric_compDense10,"j_metric_compDense10"=j_metric_compDense10,
          "h_metric_compDense20"=h_metric_compDense20,"g_metric_compDense20"=g_metric_compDense20,"j_metric_compDense20"=j_metric_compDense20,
          "h_metric_compSparse5"=h_metric_compSparse5,"g_metric_compSparse5"=g_metric_compSparse5,"j_metric_compSparse5"=j_metric_compSparse5,
          "h_metric_compSparse10"=h_metric_compSparse10,"g_metric_compSparse10"=g_metric_compSparse10,"j_metric_compSparse10"=j_metric_compSparse10,
          "h_metric_compSparse20"=h_metric_compSparse20,"g_metric_compSparse20"=g_metric_compSparse20,"j_metric_compSparse20"=j_metric_compSparse20,
          "g_metric_faccompSparseSp5"= g_metric_FacCompSparse5,"h_metric_faccompSparseSp5"=h_metric_FacCompSparse5, "j_metric_faccompSparseSp5"=j_metric_FacCompSparse5,
          "g_metric_faccompSparseSp10"= g_metric_FacCompSparse10,"h_metric_faccompSparseSp10"=h_metric_FacCompSparse10, "j_metric_faccompSparseSp10"=j_metric_FacCompSparse10,
          "g_metric_faccompSparseSp20"= g_metric_FacCompSparse20,"h_metric_faccompSparseSp20"=h_metric_FacCompSparse20, "j_metric_faccompSparseSp20"=j_metric_FacCompSparse20,
          "g_metric_faccompDenseSp5"= g_metric_FacCompDense5,"h_metric_faccompDenseSp5"=h_metric_FacCompDense5, "j_metric_faccompDenseSp5"=j_metric_FacCompDense5,
          "g_metric_faccompDenseSp10"= g_metric_FacCompDense10,"h_metric_faccompDenseSp10"=h_metric_FacCompDense10, "j_metric_faccompDenseSp10"=j_metric_FacCompDense10,
          "g_metric_faccompDenseSp20"= g_metric_FacCompDense20,"h_metric_faccompDenseSp20"=h_metric_FacCompDense20, "j_metric_faccompDenseSp20"=j_metric_FacCompDense20
        )
          
table<-as.data.frame(matrix(NA,nrow=63, ncol=8,dimnames=list(NULL,c("success_env","success_comp","success_fac","n_sp","Facilitation","Competition","sparsity","model"))))
                                                  
for(i in 1:length(names(all))){
  if(!is.null(all[[i]]$success_env)) table[i,"success_env"]<-all[[i]]$success_env
  if(!is.null(all[[i]]$success_comp)) table[i,"success_comp"]<-all[[i]]$success_comp
  if(!is.null(all[[i]]$success_fac)) table[i,"success_fac"]<-all[[i]]$success_fac
  
  if(length(grep("5",names(all)[i]))>0) table[i,"n_sp"]<-5
  if(length(grep("10",names(all)[i]))>0) table[i,"n_sp"]<-10
  if(length(grep("20",names(all)[i]))>0) table[i,"n_sp"]<-20
  
  if(length(grep("fac",names(all)[i]))>0){ table[i,"Facilitation"]<-"facilitation"}#else{table[i,"facilition"]<-NULL}
  if(length(grep("comp",names(all)[i]))>0){ table[i,"Competition"]<-"competition"}#else{table[i,"competition"]<-NULL}
  #if(!(length(grep("comp",names(all)[i]))>0) | length(grep("fac",names(all)[i]))>0) {table[i,"Comp_fac"]<-"comp_fac"}else{table[i,"Comp_fac"]<-NULL}
  
  
  if(length(grep("Dense",names(all)[i]))>0){ table[i,"sparsity"]<-"dense"}else{table[i,"sparsity"]<-"sparse"}
  
  if(length(grep("j_",names(all)[i]))>0) table[i,"model"]<-"Jsdm"
  if(length(grep("g_",names(all)[i]))>0) table[i,"model"]<-"Gjam"
  if(length(grep("h_",names(all)[i]))>0) table[i,"model"]<-"Hmsc"
  
}

table_comp<-table[which(!is.na(table$success_comp)),]
table_fac<-table[which(!is.na(table$success_fac)),]

tc<-cbind(table_comp$success_comp,table_comp$model,rep("All",nrow(table_comp)),rep("Int",nrow(table_comp)))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==5),"success_comp"],table_comp[which(table_comp$n_sp==5),"model"],rep("5",sum(table_comp$n_sp==5)),rep("Int",sum(table_comp$n_sp==5))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==10),"success_comp"],table_comp[which(table_comp$n_sp==10),"model"],rep("10",sum(table_comp$n_sp==10)),rep("Int",sum(table_comp$n_sp==10))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==20),"success_comp"],table_comp[which(table_comp$n_sp==20),"model"],rep("20",sum(table_comp$n_sp==20)),rep("Int",sum(table_comp$n_sp==20))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$sparsity=="dense"),"success_comp"],table_comp[which(table_comp$sparsity=="dense"),"model"],rep("dense",sum(table_comp$sparsity=="dense")),rep("Int",sum(table_comp$sparsity=="dense"))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$sparsity=="sparse"),"success_comp"],table_comp[which(table_comp$sparsity=="sparse"),"model"],rep("sparse",sum(table_comp$sparsity=="sparse")),rep("Int",sum(table_comp$sparsity=="sparse"))))
tc<-rbind(tc,cbind(table_comp$success_env,table_comp$model,rep("All_env",nrow(table_comp)),rep("Env",nrow(table_comp))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==5),"success_env"],table_comp[which(table_comp$n_sp==5),"model"],rep("5_env",sum(table_comp$n_sp==5)),rep("Env",sum(table_comp$n_sp==5))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==10),"success_env"],table_comp[which(table_comp$n_sp==10),"model"],rep("10_env",sum(table_comp$n_sp==10)),rep("Env",sum(table_comp$n_sp==10))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==20),"success_env"],table_comp[which(table_comp$n_sp==20),"model"],rep("20_env",sum(table_comp$n_sp==20)),rep("Env",sum(table_comp$n_sp==20))))

tc<-data.frame("success"=as.numeric(tc[,1]),"model"=tc[,2],"fac"=tc[,3],"int"=rep("Competition",nrow(tc)),"col"=tc[,4])



tf<-cbind(table_fac$success_fac,table_fac$model,rep("All",nrow(table_fac)),rep("Int",nrow(table_fac)))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==5),"success_fac"],table_fac[which(table_fac$n_sp==5),"model"],rep("5",sum(table_fac$n_sp==5)),rep("Int",sum(table_fac$n_sp==5))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==10),"success_fac"],table_fac[which(table_fac$n_sp==10),"model"],rep("10",sum(table_fac$n_sp==10)),rep("Int",sum(table_fac$n_sp==10))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==20),"success_fac"],table_fac[which(table_fac$n_sp==20),"model"],rep("20",sum(table_fac$n_sp==20)),rep("Int",sum(table_fac$n_sp==20))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$sparsity=="dense"),"success_fac"],table_fac[which(table_fac$sparsity=="dense"),"model"],rep("dense",sum(table_fac$sparsity=="dense")),rep("Int",sum(table_fac$sparsity=="dense"))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$sparsity=="sparse"),"success_fac"],table_fac[which(table_fac$sparsity=="sparse"),"model"],rep("sparse",sum(table_fac$sparsity=="sparse")),rep("Int",sum(table_fac$sparsity=="sparse"))))
tf<-rbind(tf,cbind(table_fac$success_env,table_fac$model,rep("All_env",nrow(table_fac)),rep("Env",nrow(table_fac))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==5),"success_env"],table_fac[which(table_fac$n_sp==5),"model"],rep("5_env",sum(table_fac$n_sp==5)),rep("Env",sum(table_fac$n_sp==5))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==10),"success_env"],table_fac[which(table_fac$n_sp==10),"model"],rep("10_env",sum(table_fac$n_sp==10)),rep("Env",sum(table_fac$n_sp==10))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==20),"success_env"],table_fac[which(table_fac$n_sp==20),"model"],rep("20_env",sum(table_fac$n_sp==20)),rep("Env",sum(table_fac$n_sp==20))))

tf<-data.frame("success"=as.numeric(tf[,1]),"model"=tf[,2],"fac"=tf[,3],"int"=rep("Facilitation",nrow(tf)),"col"=tf[,4])





table<-rbind(tf,tc)

p<-ggplot(data=table)+geom_boxplot(aes(y=as.numeric(success),x=as.factor(fac),fill=as.factor(col)))+
  scale_x_discrete(name="Parameters", breaks=c("All","5","10","20","dense","sparse","All_env","5_env","10_env","20_env"),
                   labels=c("All","5","10","20","dense","sparse","All","5","10","20"),limits=c("All","5","10","20","dense","sparse","All_env","5_env","10_env","20_env"))+
  scale_y_continuous(name="% success")+
  scale_fill_discrete(name = "Success in retrieving_", labels = c("Sensibility (non int.)","Sensitivity (int."))+
  facet_wrap( ~ int+model, scales="free")
p





```



## Visualization for true interactions

### Facilitation

```{r inter_patter_fac, echo=FALSE}
par(mfrow=c(1,3))
corrplot(fac_inter[[4]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200),type = "lower")
title("FacDenseSp5")
corrplot(fac_inter[[5]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("FacDenseSp10")
corrplot(fac_inter[[6]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp20")
mtext("Facilitation Dense", outer = TRUE, cex = 1.5,side=1,line=-1)

par(mfrow=c(1,3))
corrplot(fac_inter[[7]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp5")
corrplot(fac_inter[[8]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp10")
corrplot(fac_inter[[9]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp20")
mtext("Facilitation Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)
```

### Competition Dense

```{r inter_pattern_comp dense, echo=FALSE}
par(mfrow=c(1,3))
corrplot((-1)*comp_inter[[10]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp5")
corrplot((-1)*comp_inter[[11]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("CompDenseSp10")
corrplot((-1)*comp_inter[[12]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp20")
#mtext("Competition Dense", outer = TRUE, cex = 1.5,side=1,line=-1)

```

### Competition Dense

```{r inter_pattern_comp sparse, echo=FALSE}

par(mfrow=c(1,3))
corrplot((-1)*comp_inter[[13]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompSparseSp5")
corrplot((-1)*comp_inter[[14]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompSparseSp10")
corrplot((-1)*comp_inter[[15]], diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("CompSparseSp20")
#mtext("Competition Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)


```


### Competition + Facilitation Dense

```{r inter_pattern_both dense, echo=FALSE}
par(mfrow=c(2,3))
corrplot(fac_inter[[16]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp5")
corrplot(fac_inter[[17]], diag = FALSE,order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp10")
corrplot(fac_inter[[18]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp20")
#mtext("Both types Dense - Facilitation + Competition", outer = TRUE, cex = 1.5,side=1,line=-1)
corrplot((-1)*comp_inter[[16]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp5")
corrplot((-1)*comp_inter[[17]], diag = FALSE,order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp10")
corrplot((-1)*comp_inter[[18]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp20")
#mtext("Both types Dense", outer = TRUE, cex = 1.5,side=3,line=-1)

```

### Competition + Facilitation Sparse

```{r inter_pattern_both sparse, echo=FALSE}
par(mfrow=c(2,3))
corrplot(fac_inter[[19]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("FacSparseSp5")
corrplot(fac_inter[[20]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp10")
corrplot(fac_inter[[21]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color" ,col=cols(200), type = "lower")
title("FacSparseSp20")
#mtext("Both types Sparse", outer = TRUE, cex = 1.5,side=1,line=-0.5)
corrplot((-1)*comp_inter[[19]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("CompSparseSp5")
corrplot((-1)*comp_inter[[20]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompSparseSp10")
corrplot((-1)*comp_inter[[21]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color" ,col=cols(200), type = "lower")
title("CompSparseSp20")
```











