---
title: "JSDM models test"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(arm)
library(jagsUI)
library(ggplot2)
library(gridExtra)
library(parallel)
library(Rcpp)
library(magrittr)
library(purrr)
library(readr)
library(corrplot)
library(gjam)
library(Hmsc)
library(rlist)
library(ggmcmc)
library(devtools)
#install_github("sbfnk/fitR")
library(fitR) ###load through github
library(reshape)
library(AUC)
library(ggthemes)
library(mcclust.ext)
Rcpp::sourceCpp('/Users/dariabystrova/Documents/GitHub/gjamed/src/cppFns.cpp')
source("/Users/dariabystrova/Documents/GitHub/gjamed/R/gjamHfunctions_mod.R")


#setwd("C:/Users/giaru/Desktop/Documents/GitHub/Ecology-models/simcoms-master")

setwd("/Users/dariabystrova/Documents/GitHub/Ecology-models/simcoms-master/ExampleFiles")

#setwd("~/Tesi/Code/Ecology-models-master_1/simcoms-master")

# lapply(list.files(path = "."),load,.GlobalEnv)

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master")
load("params.rds")
load("sim_names.rds")
load("comp_inter.rds")
load("fac_inter.rds")
#sim_data<-readRDS("sim_data.rds")

load_object <- function(file) {
  tmp <- new.env()
  load(file = file, envir = tmp)
  tmp[[ls(tmp)[1]]]
}
```



## Data description

Data was simulated using VirtualCommunity code.\
Simulated data contains 20 data sets. \

In this file we have compared the 3 models HMSC,GJAM, JSDM on 21 simulated Dataset.\\
We have compared the ability to recover the true interactions used for modelling this datasets, by comparing estimated correlation matrix and matrix representing true interactions.\
There is a  separate file, with the functions needed to fit each model and study the convergence and more parameters are presented.\



## Environment filtering 5 species





### JSDM


```{r draw, echo=FALSE, include=FALSE}
setwd("~/Documents/GitHub/Ecology-models/simcoms-master")
sim_data<-readRDS("sim_data.rds")

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
prob_cooccur_es <- function(Y) {
  K <- ncol(Y)
  ans <- matrix(0, K, K)
  
  for (k in 1:K) {
    for (kk in 1:K) {
      N1 <- sum(Y[, k])
      N2 <- sum(Y[, kk])
      N <- nrow(Y)
      j <- max(0, N1 + N2 - N):min(N1, N2)
      p <- vector("numeric", length(j))
      for (i in seq_along(j)) {
        p[i] <- (
          choose(N, j[i]) * choose(N - j[i], N2 - j[i]) *
            choose(N - N2, N1 - j[i])
        ) / (
          choose(N, N2) * choose(N, N1)
        )
      }  
      ans[k, kk] <- (sum(Y[, k] + Y[, kk] == 2) - sum(p * j)) / N
    }
  }
  ans
}

#load("model-2019-04-09-19-02-16.rda")
me5 <- load_object("model-2019-04-09-19-02-16.rda")
#me5 <- load_object("model-jsdm-2019-05-06-17-42-56.rda")
summary(me5)
jsdm_conv<-function(mod) {
  cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mod$R$B),4)))
  cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mod$R$Rho),4)))
  cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mod$R$EnvRho),4)))
  hist(mod$n.eff$B, lwd=2,col=gray(.6), main="ess(beta)", xlab = "Beta")
  hist(mod$n.eff$Rho, lwd=2,col=gray(.6), main="ess(rho)",  xlab = "Rho")
  hist(mod$n.eff$EnvRho, lwd=2,col=gray(.6), main="ess(envrho)",  xlab = "EnvRho")
}

jsdm_conv(me5)
me5$mcmc.info[1:7]



metrics_jsdm<-function(model,fac=NULL,comp=NULL,only_env=T){
  
  Rho<-(!model$overlap0$Rho)*model$mean$Rho
  #{
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
       
      }
#    }
#    }
    }
    }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
 }
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
   list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
}


predict_y_jsdm <- function(x, ns = 1000) {
  data   <- if(x$parallel) x$model[[1]]$data() else x$model$data()
  n      <- data$n
  nsp    <- data$J
  n.samples  <- x$mcmc.info$n.samples
  B <- x$sims.list$B
  X <- data$X
  Y <- data$Y
  inprod_mat <- cppFunction(
    "NumericMatrix inprod_mat(NumericMatrix X, NumericMatrix B) {
    
    int nX = X.nrow();
    int nB = B.nrow();
    int nK = X.ncol();
    
    NumericMatrix theta(nX, nB);
    
    for (int i = 0; i < nX; i++) {
    for (int j = 0; j < nB; j++) {
    theta(i, j) = 0;
    for (int k = 0; k < nK; k++) {
    theta(i, j) += X(i, k) * B(j, k);
    }
    }
    }
    
    return(theta);
    
}"
  )
  vapply(
    floor(seq(1, n.samples, length.out = ns)),
    function(x){ inprod_mat(data$X, B[x, ,])},
    matrix(NA_real_, n, nsp)
  )
}


```
