---
title: "JSDM models test"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(arm)
library(jagsUI)
library(ggplot2)
library(gridExtra)
library(parallel)
library(Rcpp)
library(magrittr)
library(purrr)
library(readr)
library(corrplot)
library(gjam)
library(Hmsc)


#setwd("~/Desktop/VirtualCommunity/simcoms-master/ExampleFiles")
setwd("~/Documents/GitHub/Ecology-models/simcoms-master/ExampleFiles")
#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
lapply(list.files(path = "."),load,.GlobalEnv)


load_object <- function(file) {
  tmp <- new.env()
  load(file = file, envir = tmp)
  tmp[[ls(tmp)[1]]]
}


```



## Data description

Data was simulated using VirtualCommunity code.\
Simulated data contains 20 data sets. \


```{r load_m}
me5 <- load_object("model-2019-04-09-19-02-16.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me5)
#me5$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(me5$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(me5$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(me5$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(me5$R$Tau),4)))

me5$n.eff
me5$mcmc.info[1:7]
```

## Environment filtering 5 species

### JSDM

Model for $\textbf{EnvEvenSp5}$


```{r draw, echo=FALSE, include=FALSE}
#setwd("~/Desktop/VirtualCommunity/simcoms-master/")
#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
setwd("~/Documents/GitHub/Ecology-models/simcoms-master")
sim_data<-readRDS("sim_data.rds")

#' Extract correlation parameter means
#+ mean-correlations

prob_cooccur_es <- function(Y) {
  K <- ncol(Y)
  ans <- matrix(0, K, K)
  
  for (k in 1:K) {
    for (kk in 1:K) {
      N1 <- sum(Y[, k])
      N2 <- sum(Y[, kk])
      N <- nrow(Y)
      j <- max(0, N1 + N2 - N):min(N1, N2)
      p <- vector("numeric", length(j))
      for (i in seq_along(j)) {
        p[i] <- (
          choose(N, j[i]) * choose(N - j[i], N2 - j[i]) *
            choose(N - N2, N1 - j[i])
        ) / (
          choose(N, N2) * choose(N, N1)
        )
      }  
      ans[k, kk] <- (sum(Y[, k] + Y[, kk] == 2) - sum(p * j)) / N
    }
  }
  ans
}

models<-list(EnvEvenSp5=me5)
load("fac_inter.rds")
load("comp_inter.rds")


mean_cor<-function(mod){
  mean_correlations <- do.call(
  rbind,
  lapply(
    seq_along(mod),
    function(i) {
      x <- models[[i]]
      nm <- strsplit(
        names(models)[[i]], "(?<=[a-z])(?=[A-Z])", perl = TRUE
      )[[1]]
      nsp <- ncol(x$mean$Rho)
      ut <- upper.tri(x$mean$Rho)
      sp <- arrayInd(which(ut), c(nsp, nsp))
      ans <- data.frame(
        model = i,
        sp1 = sp[, 1],
        sp2 = sp[, 2],
        rho = c(prob_cooccur_es(x$model$cluster1$data()$Y)[ut], x$mean$Rho[ut]),
        rho_type = rep(c("Effect-Size", "Residual"), each = sum(ut)),
        sgn = sign(x$mean$Rho)[ut],
        significant = x$overlap$Rho[ut],
        #cint = simulation_parameters$comp_inter[[i]][ut],
        #fint = simulation_parameters$fac_inter[[i]][ut],
        cint = comp_inter[[i]][ut],
        fint = fac_inter[[i]][ut],
        density = tail(nm, 2)[1],
        type = paste0(head(nm, -2), collapse = ""),
        nsp = nsp,
        stringsAsFactors = FALSE
      )
      ans$cint[is.na(ans$cint)] <- 0
      ans$fint[is.na(ans$fint)] <- 0
      ans$density[ans$density == "Even"] <- "None"
      ans$density <- factor(ans$density, c("None", "Sparse", "Dense"))
      ans$type[ans$type == "Env"] <- "Environmental\nFiltering Only"
      ans$type[ans$type == "Fac"] <- "Facilitation"
      ans$type[ans$type == "Comp"] <- "Competition"
      ans$type[ans$type == "FacComp"] <- "Facililation +\nCompetition"
      ans$type <- factor(
        ans$type, 
        c(
          "Environmental\nFiltering Only", "Facilitation", "Competition",
          "Facililation +\nCompetition"
        )
      )
      ans$interaction <- "None"
      ans$interaction <- ifelse(ans$cint, "Competition", ans$interaction)
      ans$interaction <- ifelse(ans$fint, "Facilitation", ans$interaction)
      ans$status <- ifelse(
        ans$significant,
        ifelse(ans$sgn * -ans$cint == 1 | ans$sgn * ans$fint == 1, "TP", "FP"),
        ifelse(ans$cint == 0 & ans$fint == 0, "TN", "FN")
      )
      ans$interaction <- factor(
        ans$interaction, c("None", "Facilitation", "Competition")
      )
      ans
    }
  )
)
 return(mean_correlations)  
}

```



```{r heat, include=TRUE}
data<-sim_data$EnvEvenSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

Y_cor<-cor(data$Y)

to_prec<-function(m){
  n<-dim(m)[1]
  Tau_n<-matrix(nrow=n, ncol=n)
  for (j in 1:n) {
   for (k in 1:n){
    Tau_n[j, k] <-  -m[j, k]/sqrt((m[j,j]*m[k,k]))
   }
  }
  return(Tau_n)
}

#Tau_n<-matrix(nrow=dim(model$mean$Tau)[1], ncol=dim(model$mean$Tau)[1])
Tau_n<-to_prec(me5$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

par(mfrow=c(2,4),oma = c(3, 1, 2, 1))
corrplot(Y_cor, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("Correlation cor(Y)")
corrplot(me5$mean$EnvRho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("EnvRho")
corrplot(me5$mean$EnvRho*(!me5$overlap0$EnvRho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("EnvRho signif")
corrplot(me5$mean$Rho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("Rho")
corrplot(me5$mean$Rho*(!me5$overlap0$Rho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("Rho signif")
corrplot(Tau_n, diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("Tau")
corrplot(Tau_n*(!me5$overlap0$Tau), diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("Tau signif")
```


### GJAM 

```{r gjam functions, include=FALSE}
############################################################Functions
makeSymm <- function(m) {
  m[upper.tri(m)] <- t(m)[upper.tri(m)]
  return(m)
}

convert_to_m<-function(ar){
  d <-floor((sqrt(length(ar)*8+1)-1)/2)
  C <- matrix(0,d,d)
  i.lwr <- which(lower.tri(C, diag = TRUE), arr.ind=TRUE)
  C[i.lwr] <- ar
  C<-makeSymm(C)
  return(t(C))
}

fit_gjam<-function(data, it=2500,burn=500 , name="./gjam_models/temp.rda",interact=diag(ncol(data$Y))){
  #setup parameters
  data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )
  xdata<-as.data.frame(data$X[,-1])
  colnames(xdata)<- c("env","env2")
  ydata<-as.data.frame(data$Y)
  ###formula
  formula<-as.formula( ~env+ env2)
  ml   <- list(ng = it, burnin = burn, typeNames = 'PA')
  ####fit
  
  
  mod_gjam1  <- gjam(formula, xdata = xdata, ydata = ydata, modelList = ml)
  save(mod_gjam1, file = name)
  summary(mod_gjam1)
  
  Tau <- solve(mod_gjam1$parameters$sigMu)
  Tau_n = to_prec(Tau)
  
  postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
  postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)
  
  
  pH<-convert_to_m(postH)
  pL<-convert_to_m(postL)
  
  R_sign<-cov2cor(mod_gjam1$parameters$sigMu)*(!(pH>0 & pL<0))
  
  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(ydata), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Correlation cor(Y)")
  corrplot(mod_gjam1$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R")
  corrplot(mod_gjam1$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("E matrix")
  corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Tau")
  corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("True interactions")
}

load_gjam<-function(data,name="./gjam_models/temp.rda",interact=diag(ncol(data$Y))){
  #setup parameters
  data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )

  
  gj_mod<-load_object(name)
  summary(gj_mod)
  
  Tau <- solve(gj_mod$parameters$sigMu)
  Tau_n = to_prec(Tau)
  postH<-apply(gj_mod$chains$sgibbs, 2, quantile,0.95)
  postL<-apply(gj_mod$chains$sgibbs, 2, quantile,0.05)
  pH<-convert_to_m(postH)
  pL<-convert_to_m(postL)
  R_sign<-cov2cor(gj_mod$parameters$sigMu)*(!(pH>0 & pL<0))

  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(data$Y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Correlation cor(Y)")
  corrplot(gj_mod$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R")
  corrplot(gj_mod$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("E matrix")
  corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Tau")
  corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("True interactions")
}

######################################################################


```

```{r gjam env5, include=TRUE}

##to setup chains parameters

data<-sim_data$EnvEvenSp5
#fit_gjam(data,2000,1000,"./gjam_models/gjam5env.rda")
load_gjam(data,name="./gjam_models/gjam5env.rda")


```

### HMSC

```{r hmsc, include=TRUE, results=FALSE}

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
fit_hmsc<-function(data,label="F_t",nsamples = 1000,nchains=2,name="./HMmodels/hmtemp.rda" ){
  if (label=="F_t"){
    Y_data = subset(data, select = -env)
    ns<- ncol(Y_data)
    np <- nrow(Y_data)
    X<-scale(poly(data$env[1:np], 2))
    colnames(X)<-c("env","env2")
    studyDesign = data.frame(sample = as.factor(1:np))
    rL = HmscRandomLevel(units = studyDesign$sample)
    m = Hmsc(Y=as.matrix(Y_data), XData=as.data.frame(X), XFormula=~env+env2, distr="probit",
             studyDesign = studyDesign, ranLevels = list(sample = rL))
    m = sampleMcmc(m, nsamples, thin=10, adaptNf=c(200,200), transient=500,nChains=nchains ,verbose=F)
    save(m, file = name)
    return(m)
  }
  if (label=="L_d"){
    return(load_object(name))
  }
}

data<-sim_data$EnvEvenSp5
hm_mod<-fit_hmsc(data,"L_d",name="./HMmodels/hm5env.rda" )
#hm_mod<-load_object("./HMmodels/hm5env.rda")

```

Convergence:

```{r hmsc convergence, include=TRUE}
hm_conv<-function(mod){
  codaList = convertToCodaObject(mod)

  #convergence histograms
  hist(effectiveSize(codaList$Beta), main="ess(beta)")
  hist(gelman.diag(codaList$Beta,multivariate=FALSE)$psrf, main="psrf(beta)")
  
  hist(effectiveSize(codaList$Omega[[1]]), main="ess(omega)")
  hist(gelman.diag(codaList$Omega[[1]], multivariate=FALSE)$psrf, main="psrf(omega)")
}

hm_conv(hm_mod)
```

Study of interactions

```{r hmsc study of interactions, include=TRUE}

hm_inter<-function(mod, nchains=2,nsamples = 1000, interact=diag(ns)){
  getOmega = function(a,r=1)
  return(crossprod(a$Lambda[[r]]))
  ns<-mod$ns
  postOmega1 = array(unlist(lapply(mod$postList[[1]],getOmega)),c(ns,ns,mod$samples))
  postOmega2 = array(unlist(lapply(mod$postList[[2]],getOmega)),c(ns,ns,mod$samples))
  
  postOmega<-abind(postOmega1,postOmega2,along=3)
  postOmegaMean = apply(postOmega,c(1,2),mean)
  postOmegaUp=apply(postOmega,c(1,2),quantile,0.95)
  postOmegaLo=apply(postOmega,c(1,2),quantile,0.05)
  
  postR<-array(dim=c(ns,ns,nchains*nsamples))
  for(i in 1:dim(postOmega)[3])
  postR[,,i]<-stats::cov2cor(postOmega[,,i])
  
  
  postRMean = apply(postR,c(1,2),mean)
  postRUp=apply(postR,c(1,2),quantile,0.95)
  postRLo=apply(postR,c(1,2),quantile,0.05)
  
  Tau = solve(postOmegaMean)
  Tau_n = cov2cor(Tau)
  
  
  Toplot_R<-postRMean*(!(postRUp>0 & postRLo<0))
  
  # Omegacor<- computeAssociations(m)
  # supportLevel<- 0.95
  # toPlot<- ((Omegacor[[1]]$support>supportLevel)+ (Omegacor[[1]]$support<(1-supportLevel))>0)*Omegacor[[1]]$mean
  # corrplot(toPlot, method="color", col=colorRampPalette(c("blue", "white", "red"))(200))
  
  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(hm_mod$Y), diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Correlation cor(Y)")
  corrplot(postRMean, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R")
  corrplot(Toplot_R, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Plot only non zero value")
  corrplot(Tau_n, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Partial correlation matrix")
  corrplot(interact, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("True interactions")
}


hm_inter(hm_mod)
```


## Environmental filtering 10 species

### JSDM

```{r load_m en10}
me10 <- load_object("model-2019-04-10-08-26-20.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me10)
#me10$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(me10$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(me10$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(me10$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(me10$R$Tau),4)))

me10$n.eff
me10$mcmc.info[1:7]



data<-sim_data$EnvEvenSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

plot_cor_jsdm<-function(mod,y,interact=diag(ncol(y))){
  par(mfrow=c(2,4),oma = c(3, 1, 2, 1))
  corrplot(cor(y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Correlation cor(Y)")
  corrplot(mod$mean$EnvRho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("EnvRho")
  corrplot(mod$mean$EnvRho*(!mod$overlap0$EnvRho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("EnvRho signif")
  corrplot(mod$mean$Rho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Rho")
  corrplot(mod$mean$Rho*(!mod$overlap0$Rho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Rho signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("True interactions")
  #corrplot(Tau_n, diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  #title("Tau")
  #corrplot(Tau_n*(!me10$overlap0$Tau), diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  #title("Tau")
}

plot_cor_jsdm(me10,data$Y)

```

### Gjam

```{r gjam en10}

data<-sim_data$EnvEvenSp10

#fit_gjam(data,5000,500,"./gjam_models/gjam10env.rda")
load_gjam(data,name="./gjam_models/gjam10env.rda")
#gje10<-load_object("./gjam_models/gjam10env.rda")

#to check posterior density of s in Sigma 
#gje10<-load_object("./gjam_models/gjam10env.rda")
#plot(density(gje10$chains$sgibbs[,4]))


```

### HMSC
```{r hmsc en10}

data<-sim_data$EnvEvenSp10
#hm_mod<-fit_hmsc(data,"F_t",name="./HMmodels/hm10env.rda" )
hm_mod<-fit_hmsc(data,"L_d",name="./HMmodels/hm10env.rda" )

hm_conv(hm_mod)
hm_inter(hm_mod)

```




## Environmental filtering 20 species

### JSDM

```{r load_m en20}
me20 <- load_object("model-2019-04-11-19-06-02.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me20)
#me20$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(me20$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(me20$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(me20$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(me20$R$Tau),4)))


me20$n.eff
me20$mcmc.info[1:7]


data<-sim_data$EnvEvenSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))


plot_cor_jsdm(me20,data$Y)

```


### Gjam

```{r gjam en20}

data<-sim_data$EnvEvenSp20

#fit_gjam(data,5000,500,"./gjam_models/gjam20env.rda")

load_gjam(data,name="./gjam_models/gjam20env.rda")
#gje20<-load_object("./gjam_models/gjam20env.rda")

#to check posterior density of s in Sigma 
#gje20<-load_object("./gjam_models/gjam20env.rda")
#plot(density(gje20$chains$sgibbs[,4]))


```

### Gjam dimension reduction

```{r gjam en20 dim red}

data<-sim_data$EnvEvenSp20



#fit_gjam(data,5000,500,"./gjam_models/gjam20env.rda")

#load_gjam(data,name="./gjam_models/gjam20env.rda")
#gje20<-load_object("./gjam_models/gjam20env.rda")

#to check posterior density of s in Sigma 
#gje20<-load_object("./gjam_models/gjam20env.rda")
#plot(density(gje20$chains$sgibbs[,4]))
 data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )
  xdata<-as.data.frame(data$X[,-1])
  colnames(xdata)<- c("env","env2")
  ydata<-as.data.frame(data$Y)
  ###formula
  rl   <- list(r = 8, N = 20)
  formula<-as.formula( ~env+ env2)
  ml  <- list(ng = 2500, burnin = 500, typeNames = 'PA', reductList = rl)
  ####fit
  
  
  mod_gjam1  <- gjam(formula, xdata = xdata, ydata = ydata, modelList = ml)
  save(mod_gjam1, file = "./gjam_models/gjam20env_dr.rda")
  summary(mod_gjam1)
  
  Tau <- solve(mod_gjam1$parameters$sigMu)
  Tau_n = to_prec(Tau)
  
  #postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
  #postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)
  
  
  #pH<-convert_to_m(postH)
  #pL<-convert_to_m(postL)
  
  #R_sign<-cov2cor(mod_gjam1$parameters$sigMu)*(!(pH>0 & pL<0))
  
  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(ydata), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("Correlation cor(Y)")
  corrplot(mod_gjam1$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("R")
  corrplot(mod_gjam1$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("E matrix")
  # corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  # title("Tau")
  # corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  # title("R signif")
  corrplot(diag(20), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
  title("True interactions")



```

```{r hmsc en20}

data<-sim_data$EnvEvenSp20
hm_mod<-fit_hmsc(data,"L_d",name="./HMmodels/hm20env.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod)



```

## Environmental filtering + Facilitation dense 5 species

### JSDM

```{r load_m facd5}
mf5 <- load_object("model-2019-04-11-19-35-11.rda")
summary(mf5)
#mf5$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mf5$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mf5$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mf5$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mf5$R$Tau),4)))

mf5$n.eff
mf5$mcmc.info[1:7]




data<-sim_data$FacDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

plot_cor_jsdm(mf5,data$Y,fac_inter[[4]])

```

### Gjam

```{r gjam fd5}

data<-sim_data$FacDenseSp5

#fit_gjam(data,5000,500,"./gjam_models/gjam5f.rda",interact=fac_inter[[4]])
load_gjam(data,name="./gjam_models/gjam5f.rda", interact=fac_inter[[4]])
#gjfd5<-load_object("./gjam_models/gjam5f.rda")

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5f.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```



### HMSC
```{r hmsc fd5}
data<-sim_data$FacDenseSp5
hm_mod<-fit_hmsc(data,"L_d",name="./HMmodels/hm5fd.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod, interact = fac_inter[[4]])



```

## Environmental filtering + Facilitation dense 10 species

### JSDM

```{r model jsdm fd10, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfd10 <- load_object("model-2019-04-12-06-59-42.rda")

summary(mfd10)
#mfd10$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mfd10$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mfd10$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mfd10$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mfd10$R$Tau),4)))

mfd10$n.eff
mfd10$mcmc.info[1:7]



######################################################Prepare data
data<-sim_data$FacDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

#Tau_n<-to_prec(mfd10$mean$Tau)


plot_cor_jsdm(mfd10,data$Y,fac_inter[[5]])

```


```{r gjam fd10}

data<-sim_data$FacDenseSp10

#fit_gjam(data,5000,500,"./gjam_models/gjam10fd.rda",interact=fac_inter[[5]])
load_gjam(data,name="./gjam_models/gjam10fd.rda", interact=fac_inter[[5]])
#gjfd5<-load_object("./gjam_models/gjam10fd.rda")

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam10fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```


### HMSC

```{r model2 hmsc, echo=FALSE}
#####HMSC

#data<-sim_data$FacDenseSp10

# Y_data = subset(data, select = -env)
# X<-scale(poly(data$env[1:np], 2))
# colnames(X)<-c("env","env2")

#if sim_data is not a sitexspecies matrix but is a dataframe where one column are the presences
# then do this
 # Y_data<-matrix(NA,nrow=np,ncol=ns)
 # for(i in 1:ns){
 #   Y_data[,i]<-as.numeric(sim_data$FacDenseSp10$present[(np*(i-1)+1):(np*i)])
 # }
 #
 # X<-scale(poly(data$env[1:np], 2))

# studyDesign = data.frame(sample = as.factor(1:np))
# rL = HmscRandomLevel(units = studyDesign$sample)
# 
# m = Hmsc(Y=as.matrix(Y_data), XData=as.data.frame(X), XFormula=~env+env2, distr="probit",
#          studyDesign = studyDesign, ranLevels = list(sample = rL))
# 
# nsamples=10000
# nchains=2
# m = sampleMcmc(m, nsamples, thin=10, adaptNf=c(200,200), transient=500,nChains=nchains ,verbose=F)
# 
# codaList = convertToCodaObject(m)
# 
# #convergence histograms
# hist(effectiveSize(codaList$Beta), main="ess(beta)")
# hist(gelman.diag(codaList$Beta,multivariate=FALSE)$psrf, main="psrf(beta)")
# hist(effectiveSize(codaList$Omega[[1]]), main="ess(omega)")
# hist(gelman.diag(codaList$Omega[[1]], multivariate=FALSE)$psrf, main="psrf(omega)")
# ns<-10
# 
# getOmega = function(a,r=1)
#   return(crossprod(a$Lambda[[r]]))
# 
# postOmega1 = array(unlist(lapply(m$postList[[1]],getOmega)),c(ns,ns,m$samples))
# postOmega2 = array(unlist(lapply(m$postList[[2]],getOmega)),c(ns,ns,m$samples))
# 
# postOmega<-abind(postOmega1,postOmega2,along=3)
# postOmegaMean = apply(postOmega,c(1,2),mean)
# postOmegaUp=apply(postOmega,c(1,2),quantile,0.95)
# postOmegaLo=apply(postOmega,c(1,2),quantile,0.05)
# 
# postR<-array(dim=c(ns,ns,nchains*nsamples))
# for(i in 1:dim(postOmega)[3])
#  postR[,,i]<-cov2cor(postOmega[,,i])
# 
# postRMean = apply(postR,c(1,2),mean)
# postRUp=apply(postR,c(1,2),quantile,0.95)
# postRLo=apply(postR,c(1,2),quantile,0.05)
# 
# 
# 
# 
# Tau = solve(postOmegaMean)
# Tau_n = cov2cor(Tau)
# 
# #Only values that do not overlap zero
# Toplot_R<-postRMean*(!(postRUp>0 & postRLo<0))
# 
# 
# # Omegacor<- computeAssociations(m)
# # supportLevel<- 0.95
# # toPlot<- ((Omegacor[[1]]$support>supportLevel)+ (Omegacor[[1]]$support<(1-supportLevel))>0)*Omegacor[[1]]$mean
# # corrplot(toPlot, method="color", col=colorRampPalette(c("blue", "white", "red"))(200))
# # Omegacor<- computeAssociations(m)
# # supportLevel<- 0.95
# # toPlot<- ((Omegacor[[1]]$support>supportLevel)+ (Omegacor[[1]]$support<(1-supportLevel))>0)*Omegacor[[1]]$mean
# # corrplot(toPlot, method="color", col=colorRampPalette(c("blue", "white", "red"))(200))
# 
# 
# 
# par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
# corrplot(cor(Y_data), diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("Correlation cor(Y)")
# corrplot(postRMean, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("R")
# corrplot(Toplot_R, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("Plot only non zero value")
# corrplot(Tau_n, diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("Partial correlation matrix")
# corrplot(fac_inter[[5]], diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# title("True interactions")



data<-sim_data$FacDenseSp10
hm_mod<-fit_hmsc(data,"L_d",name="./HMmodels/hm10fd.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod, interact = fac_inter[[5]])





```




## Environmental filtering + Facilitation dense 20 species

### JSDM

```{r model jsdm fd20, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfd20 <- load_object("model-2019-04-13-17-22-12.rda")

summary(mfd20)
#mfd20$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mfd20$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mfd20$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mfd20$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mfd20$R$Tau),4)))

mfd20$n.eff
mfd20$mcmc.info[1:7]


######################################################Prepare data
data<-sim_data$FacDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfd20,data$Y,fac_inter[[6]])

```


### Gjam


```{r gjam fd20}

data<-sim_data$FacDenseSp20

fit_gjam(data,5000,500,"./gjam_models/gjam20fd.rda",interact=fac_inter[[6]])
#load_gjam(data,name="./gjam_models/gjam20fd.rda", interact=fac_inter[[6]])
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))


```


### HMSC
```{r hmsc fd20}
data<-sim_data$FacDenseSp20
hm_mod<-fit_hmsc(data,"L_d",name="./HMmodels/hm20fd.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod, interact = fac_inter[[6]])



```



## Environmental filtering + Facilitation sparse 5 species

### JSDM


```{r model jsdm fs5, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs5 <- load_object("model-2019-04-13-17-51-16.rda")

summary(mfs5)
#mfs5$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mfs5$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mfs5$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mfs5$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mfs5$R$Tau),4)))

mfs5$n.eff
mfs5$mcmc.info[1:7]



######################################################Prepare data
data<-sim_data$FacSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfs5,data$Y,fac_inter[[7]])
```



## Environmental filtering + Facilitation sparse 10 species

### JSDM

```{r model jsdm fs10, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs10 <- load_object("model-2019-04-14-05-17-58.rda")

summary(mfs10)
#mfs10$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mfs10$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mfs10$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mfs10$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mfs10$R$Tau),4)))

mfs10$n.eff
mfs10$mcmc.info[1:7]


######################################################Prepare data
data<-sim_data$FacSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfs10,data$Y,fac_inter[[8]])
```





## Environmental filtering + Facilitation sparse 20 species

### JSDM


```{r model jsdm fs20, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs20 <- load_object("model-2019-04-15-15-34-20.rda")

summary(mfs20)
#mfs20$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mfs20$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mfs20$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mfs20$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mfs20$R$Tau),4)))

mfs20$n.eff
mfs20$mcmc.info[1:7]

######################################################Prepare data
data<-sim_data$FacSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mfs20,data$Y,fac_inter[[9]])
```


## Environmental filtering + Competition dense 5 species

### JSDM


```{r model jsdm cmpd5, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd5 <- load_object("model-2019-04-15-16-03-39.rda")

summary(mcmpd5)
#mcmpd5$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mcmpd5$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mcmpd5$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mcmpd5$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mcmpd5$R$Tau),4)))

mcmpd5$n.eff
mcmpd5$mcmc.info[1:7]



######################################################Prepare data
data<-sim_data$CompDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mcmpd5,data$Y,comp_inter[[10]])
```



## Environmental filtering + Competition dense 10 species


```{r model jsdm cmpd10, echo=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd10 <- load_object("model-2019-04-16-03-39-17.rda")

summary(mcmpd10)
#mcmpd10$Rhat
cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mcmpd10$R$B),4)))
cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mcmpd10$R$Rho),4)))
cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mcmpd10$R$EnvRho),4)))
cat(sprintf("Maximum Rhat value for Tau: %s\n", round(max(mcmpd10$R$Tau),4)))

mcmpd10$n.eff
mcmpd10$mcmc.info[1:7]

######################################################Prepare data
data<-sim_data$CompDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
plot_cor_jsdm(mcmpd10,data$Y,comp_inter[[11]])
```




## Environmental filtering + Competition dense 20 species
## Environmental filtering + Competition sparse 5 species
## Environmental filtering + Competition dense 10 species
## Environmental filtering + Competition dense 5 species

## Graph 



```{r combined models, echo=FALSE, warning=FALSE}

models<-list(EnvEvenSp5=me5,EnvEvenSp10=me10, EnvEvenSp20=me20,FacDenseSp5 =mf5, FacDenseSp10=mfd10, FacDenseSp20=mfd20,
             FacSparseSp5 =mfs5, FacSparseSp10=mfs10, FacSparseSp20=mfs20, CompDenseSp5=mcmpd5,CompDenseSp10=mcmpd10)

mean_correlations <- mean_cor(models)
x <- subset(mean_correlations, type != "Environmental\nFiltering Only")
acc <- by(x, x$model, function(x) sum(x$status == "TP" | x$status == "TN") / nrow(x))

#' Plot correlation parameter means
#+ plot-correlations
ggplot(mean_correlations) +
  aes(factor(nsp), rho, fill = interaction) +
  geom_hline(yintercept = 0) +
  geom_boxplot(
    outlier.size = .2, size = .1, position = position_dodge(preserve = "single")
  ) +
  scale_fill_manual(values = c("grey", "blue", "red")) +
  facet_grid(type ~ rho_type + density, switch = "y") +
  xlab("Number of species") +
  ylab("Correlation") +
  theme_bw() +
  theme(legend.position = "top")

```



## Visualization for true interactions

```{r inter_patter_fac, echo=FALSE}
par(mfrow=c(1,3))
corrplot(fac_inter[[4]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacDenseSp5")
corrplot(fac_inter[[5]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacDenseSp10")
corrplot(fac_inter[[6]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacDenseSp20")
mtext("Facilitation Dense", outer = TRUE, cex = 1.5,side=1,line=-1)

par(mfrow=c(1,3))
corrplot(fac_inter[[7]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacSparseSp5")
corrplot(fac_inter[[8]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacSparseSp10")
corrplot(fac_inter[[9]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacSparseSp20")
mtext("Facilitation Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)
```

```{r inter_pattern_comp, echo=FALSE}
par(mfrow=c(1,3))
corrplot(comp_inter[[10]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("CompDenseSp5")
corrplot(comp_inter[[11]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("CompDenseSp10")
corrplot(comp_inter[[12]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("CompDenseSp20")
mtext("Competition Dense", outer = TRUE, cex = 1.5,side=1,line=-1)

par(mfrow=c(1,3))
corrplot(comp_inter[[13]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("CompSparseSp5")
corrplot(comp_inter[[14]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("CompSparseSp10")
corrplot(comp_inter[[15]], diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("CompSparseSp20")
mtext("Competition Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)


```

```{r inter_pattern_both, echo=FALSE}
par(mfrow=c(1,3))
corrplot(comp_inter[[16]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacCompDenseSp5")
corrplot(comp_inter[[17]], diag = FALSE,order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacCompDenseSp10")
corrplot(comp_inter[[18]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacCompDenseSp20")
mtext("Both types Dense", outer = TRUE, cex = 1.5,side=1,line=-1)


par(mfrow=c(1,3))
corrplot(comp_inter[[19]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacCompSparseSp5")
corrplot(comp_inter[[20]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacCompSparseSp10")
corrplot(comp_inter[[21]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
title("FacCompSparseSp20")
mtext("Both types Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)

```




