---
title: "JSDM models test"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(arm)
library(jagsUI)
library(ggplot2)
library(gridExtra)
library(parallel)
library(Rcpp)
library(magrittr)
library(purrr)
library(readr)
library(corrplot)
library(gjam)
library(Hmsc)
library(rlist)
library(ggmcmc)
library(devtools)
#install_github("sbfnk/fitR")
library(fitR) ###load through github
library(reshape)

setwd("~/Documents/GitHub/Ecology-models/simcoms-master")

#setwd("~/GitHub/Ecology-models/simcoms-master")

#setwd("~/Tesi/Code/Ecology-models-master_1/simcoms-master")

# lapply(list.files(path = "."),load,.GlobalEnv)

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master")
load("params.rds")
load("sim_names.rds")
load("comp_inter.rds")
load("fac_inter.rds")
#sim_data<-readRDS("sim_data.rds")

load_object <- function(file) {
  tmp <- new.env()
  load(file = file, envir = tmp)
  tmp[[ls(tmp)[1]]]
}
```



## Data description

Data was simulated using VirtualCommunity code.\
Simulated data contains 20 data sets. \

In this file we have compared the 3 models HMSC,GJAM, JSDM on 21 simulated Dataset.\\
We have compared the ability to recover the true interactions used for modelling this datasets, by comparing estimated correlation matrix and matrix representing true interactions.\
There is a  separate file, with the functions needed to fit each model and study the convergence and more parameters are presented.\

## Environment filtering 5 species

### JSDM


```{r draw, echo=FALSE, include=FALSE}
#setwd("~/Documents/GitHub/Ecology-models/simcoms-master")
sim_data<-readRDS("sim_data.rds")

#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
prob_cooccur_es <- function(Y) {
  K <- ncol(Y)
  ans <- matrix(0, K, K)
  
  for (k in 1:K) {
    for (kk in 1:K) {
      N1 <- sum(Y[, k])
      N2 <- sum(Y[, kk])
      N <- nrow(Y)
      j <- max(0, N1 + N2 - N):min(N1, N2)
      p <- vector("numeric", length(j))
      for (i in seq_along(j)) {
        p[i] <- (
          choose(N, j[i]) * choose(N - j[i], N2 - j[i]) *
            choose(N - N2, N1 - j[i])
        ) / (
          choose(N, N2) * choose(N, N1)
        )
      }  
      ans[k, kk] <- (sum(Y[, k] + Y[, kk] == 2) - sum(p * j)) / N
    }
  }
  ans
}

#load("model-2019-04-09-19-02-16.rda")
me5 <- load_object("model-2019-04-09-19-02-16.rda")
#me5 <- load_object("model-jsdm-2019-05-06-17-42-56.rda")
summary(me5)
jsdm_conv<-function(mod) {
  cat(sprintf("Maximum Rhat value for Beta: %s\n", round(max(mod$R$B),4)))
  cat(sprintf("Maximum Rhat value for Rho: %s\n", round(max(mod$R$Rho),4)))
  cat(sprintf("Maximum Rhat value for EnvRho: %s\n", round(max(mod$R$EnvRho),4)))
  hist(mod$n.eff$B, lwd=2,col=gray(.6), main="ess(beta)", xlab = "Beta")
  hist(mod$n.eff$Rho, lwd=2,col=gray(.6), main="ess(rho)",  xlab = "Rho")
  hist(mod$n.eff$EnvRho, lwd=2,col=gray(.6), main="ess(envrho)",  xlab = "EnvRho")
}

jsdm_conv(me5)
me5$mcmc.info[1:7]



metrics_jsdm<-function(model,fac=NULL,comp=NULL,only_env=T){
  
  Rho<-(!model$overlap0$Rho)*model$mean$Rho
  #{
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
       
      }
#    }
#    }
    }
    }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
 }
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
   list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
}


predict_y_jsdm <- function(x, ns = 1000) {
  data   <- if(x$parallel) x$model[[1]]$data() else x$model$data()
  n      <- data$n
  nsp    <- data$J
  n.samples  <- x$mcmc.info$n.samples
  B <- x$sims.list$B
  X <- data$X
  Y <- data$Y
  inprod_mat <- cppFunction(
    "NumericMatrix inprod_mat(NumericMatrix X, NumericMatrix B) {
    
    int nX = X.nrow();
    int nB = B.nrow();
    int nK = X.ncol();
    
    NumericMatrix theta(nX, nB);
    
    for (int i = 0; i < nX; i++) {
    for (int j = 0; j < nB; j++) {
    theta(i, j) = 0;
    for (int k = 0; k < nK; k++) {
    theta(i, j) += X(i, k) * B(j, k);
    }
    }
    }
    
    return(theta);
    
}"
  )
  vapply(
    floor(seq(1, n.samples, length.out = ns)),
    function(x){ inprod_mat(data$X, B[x, ,])},
    matrix(NA_real_, n, nsp)
  )
}


```


```{r heat, include=FALSE}
data<-sim_data$EnvEvenSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

Y_cor<-cor(data$Y)

to_prec<-function(m){
  n<-dim(m)[1]
  Tau_n<-matrix(nrow=n, ncol=n)
  for (j in 1:n) {
   for (k in 1:n){
    Tau_n[j, k] <-  -m[j, k]/sqrt((m[j,j]*m[k,k]))
   }
  }
  return(Tau_n)
}

#Tau_n<-matrix(nrow=dim(model$mean$Tau)[1], ncol=dim(model$mean$Tau)[1])
Tau_n<-to_prec(me5$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

par(mfrow=c(2,4),oma = c(3, 1, 2, 1))
cols = colorRampPalette(c("dark blue","white","red"))
col2 <- colorRampPalette(c("#4393C3", "#2166AC", "#053061",
                           "#FDDBC7", "#FFFFFF", "#D1E5F0", "#92C5DE",
                           "#67001F", "#B2182B", "#D6604D", "#F4A582"))


corrplot(Y_cor, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Correlation cor(Y)")
corrplot(me5$mean$EnvRho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("EnvRho")
corrplot(me5$mean$EnvRho*(!me5$overlap0$EnvRho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("EnvRho signif")
corrplot(me5$mean$Rho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Rho")
corrplot(me5$mean$Rho*(!me5$overlap0$Rho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Rho signif")
corrplot(Tau_n, diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Tau")
corrplot(Tau_n*(!me5$overlap0$Tau), diag = FALSE, order ="original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("Tau signif")

j_metric_e5<-metrics_jsdm(me5)
#cat("Success rate ")
#j_metric_e5$success_env
 cat(sprintf("Success rate: %s\n", metrics_jsdm(me5)$success_env))
 
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =as.matrix(me5$mean$Rho*(!me5$overlap0$Rho))) 
mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =as.matrix(me5$mean$Rho*(!me5$overlap0$Rho))) 



####Prediction
pred_j<-pnorm(predict_y_jsdm(me5))
pred_j_mean <- apply(pred_j, 1:2, mean)

pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)
pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)


```


### GJAM 

```{r gjam functions,include=FALSE}
############################################################Functions
makeSymm <- function(m) {
  m[upper.tri(m)] <- t(m)[upper.tri(m)]
  return(m)
}

expandSigma_rmd <- function(sigma, S){

  ss <- diag(S)
  ss[lower.tri(ss,diag=T)] <- sigma
  ss[upper.tri(ss)] <- t(ss)[upper.tri(ss)]
  ss
}

convert_to_m<-function(ar){
  d <-floor((sqrt(length(ar)*8+1)-1)/2)
  C <- matrix(0,d,d)
  i.lwr <- which(lower.tri(C, diag = TRUE), arr.ind=TRUE)
  C[i.lwr] <- ar
  C<-makeSymm(C)
  return(t(C))
}


metrics_gjam<-function(Rho, comp=NULL,fac=NULL,only_env=T){
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
       
      }
    }
    }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
  }
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
  list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
  }


fit_gjam<-function(data, it=2500,burn=500 , name="./gjam_models/temp.rda",interact=diag(ncol(data$Y))){
  #setup parameters
  data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )
  xdata<-as.data.frame(data$X[,-1])
  colnames(xdata)<- c("env","env2")
  ydata<-as.data.frame(data$Y)
  ###formula
  formula<-as.formula( ~env+ env2)
  ml   <- list(ng = it, burnin = burn, typeNames = 'PA')
  ####fit
  
  mod_gjam1  <- gjam(formula, xdata = xdata, ydata = ydata, modelList = ml)
  save(mod_gjam1, file = name)
  #summary(mod_gjam1)
  hist(effectiveSize(mod_gjam1$chains$sgibbs), main="ess(beta)",lwd=2,col=gray(.6))
  hist(effectiveSize(mod_gjam1$chains$bgibbs), main="ess(beta)",lwd=2,col=gray(.6))
  
  # postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
  # postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)
  postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
  postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)
  
  pH<-convert_to_m(postH)
  pL<-convert_to_m(postL)
  
  R_sign<-cov2cor(mod_gjam1$parameters$sigMu)*(!(pH>0 & pL<0))
  
  sgibbs<-mod_gjam1$chains$sgibbs
  tau<-array(NA,dim=c(data$J,data$J,1000))
  for(j in 1:1000){
    ss <- expandSigma_rmd(sgibbs[j,], S = data$J)
    si <- solve(ss)
    tau[,,j] <- -cov2cor(si)
  }
  #  sgibbs<-mod_gjam1$chains$sgibbs
  # tau<-array(NA,dim=c(data$J,data$J,it-burn))
  # for(j in (burn:it)){
  #   ss <- expandSigma_rmd(sgibbs[j,], S = 5)
  #   si <- solve(ss)
  #   tau[,,j-burn] <- -cov2cor(si)
  # }

  tau_mean<-apply(tau,c(1,2), mean)
  tau_HI<-apply(tau,c(1,2),quantile,0.95)
  tau_LO<-apply(tau,c(1,2),quantile,0.05)
  
  Tau_sign<-tau_mean*(!(tau_HI>0 & tau_LO<0))
  
  #newdata   <- list(xdata = xdata, nsim = 50 )

  x<- data$X
  #p1<-gjamPredict(mod_gjam1)
  mu<-array(NA,dim=c(data$n,data$J,it))
  for(k in 1:it){
      for(j in 1:data$J){
    
         mu[,j,k] <- pnorm(x%*%mod_gjam1$chains$bgibbs[k,(3*(j-1)+1):(3*j)])
          
    }
  }
  
  # par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  # corrplot(cor(ydata), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200),   type = "lower")
  # title("Correlation cor(Y)")
  # corrplot(mod_gjam1$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  # title("R")
  # corrplot(mod_gjam1$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  # title("E matrix")
  # corrplot(Tau_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  # title("Tau signif")
  # corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  # title("R signif")
  # corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  # title("True interactions")
  return(list(Rho_sign=R_sign,Tau_sign=Tau_sign,predict=mu))

  }


###this function only loads the model and return the R and T significant
load_gjam<-function(data,it=2500,burn=500,name="./gjam_models/temp.rda",interact=diag(ncol(data$Y))){
  #setup parameters
  data <- list(
    Y = subset(data, select = -env),
    X = cbind(1, scale(poly(data$env, 2))),
    covx = cov(cbind(1, scale(poly(data$env, 2)))),
    K = 3,
    J = ncol(data) - 1,
    n = nrow(data),
    I = diag(ncol(data) - 1),
    df = ncol(data)
  )

  xdata<-as.data.frame(data$X[,-1])

  gj_mod<-load_object(name)
  #summary(gj_mod)
  S<-ncol(data$Y)
  ind <-which(array(diag(S)[lower.tri(diag(S),diag=T)])==1)
  par(mfrow=c(1,3),oma = c(1, 1, 1, 1))
  hist(effectiveSize(gj_mod$chains$sgibbs[,-ind]), main="sigma non diagonal elements",lwd=2,col=gray(.6))
  hist(effectiveSize(gj_mod$chains$sgibbs[,ind]), main="sigma diagonal elements",lwd=2,col=gray(.6))
  hist(effectiveSize(gj_mod$chains$bgibbs), main="ess(beta)",lwd=2,col=gray(.6))
 
  
  postH<-apply(gj_mod$chains$sgibbs[burn:dim(gj_mod$chains$sgibbs)[1],], 2, quantile,0.95)
  postL<-apply(gj_mod$chains$sgibbs[burn:dim(gj_mod$chains$sgibbs)[1],], 2, quantile,0.05)
  pH<-convert_to_m(postH)
  pL<-convert_to_m(postL)
  R_sign<-cov2cor(gj_mod$parameters$sigMu)*(!(pH>0 & pL<0))
  
  
  sgibbs<-gj_mod$chains$sgibbs
  tau<-array(NA,dim=c(data$J,data$J,it-burn))
  for(j in (burn:it)){
    ss <- expandSigma_rmd(sgibbs[j,], S = data$J)
    si <- solve(ss)
    tau[,,j-burn] <- -cov2cor(si)
  }
    # sgibbs<-gj_mod$chains$sgibbs
    # tau<-array(NA,dim=c(data$J,data$J,1000))
    # for(j in (1:1000)){
    #   ss <- expandSigma_rmd(sgibbs[j,], S = 5)
    #   si <- solve(ss)
    #   tau[,,j] <- -cov2cor(si)
    # }
  #new<-list(data$X[floor(seq(1, data$n, length.out = 100)),2])

  #newdata   <- list(xdata = xdata, nsim = 50 )

  x<- data$X
  #p1<-gjamPredict(mod_gjam1)
  mu<-array(NA,dim=c(data$n,data$J,it))
  for(k in 1:it){
      for(j in 1:data$J){
    
         mu[,j,k] <- pnorm(x%*%gj_mod$chains$bgibbs[k,(3*(j-1)+1):(3*j)])
          
    }
  }
  
  
  tau_mean<-apply(tau,c(1,2), mean)
  tau_HI<-apply(tau,c(1,2),quantile,0.95)
  tau_LO<-apply(tau,c(1,2),quantile,0.05)
  
  Tau_sign<-tau_mean*(!(tau_HI>0 & tau_LO<0))
  
  

  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(data$Y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Correlation cor(Y)")
  corrplot(gj_mod$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R")
  corrplot(gj_mod$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("E matrix")
  corrplot(Tau_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Tau signif")
  corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
  
  return(list(Rho_sign=R_sign,Tau_sign=Tau_sign,predict=mu))
}

######################################################################
```




```{r gjam env5,include=FALSE}
##to setup chains parameters
data<-sim_data$EnvEvenSp5
mod_gjam<-fit_gjam(data,2500,500,name="./gjam_models/gjam5env.rda")
#mod_gjam<-load_gjam(data,2500,500,name="./gjam_models/gjam5env.rda")

g_metric_e5<-metrics_gjam(mod_gjam$Rho_sign)
g_metric_e5_p<-metrics_gjam(mod_gjam$Tau_sign)
cat(" ")
cat(sprintf("Success rate: %s\n", metrics_gjam(mod_gjam$Rho_sign)$success_env))

mod_list_Rho<-list.append(mod_list_Rho,gjam=mod_gjam$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,gjam=mod_gjam$Tau_sign)
#####Prediction
pred_gj_mean <-apply(mod_gjam$predict, 1:2,mean)
pred_gj_05 <- apply(mod_gjam$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(mod_gjam$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```

### HMSC

```{r hmsc, include=FALSE, results=FALSE,}
#setwd("~/Tesi/Code/Ecology-models-master/simcoms-master/ExampleFiles")
fit_hmsc<-function(data,label="Fit",nsamples = 1000,nchains=2,name="./HMmodels/hmtemp.rda" ){
  if (label=="Fit"){
    Y_data = subset(data, select = -env)
    ns<- ncol(Y_data)
    np <- nrow(Y_data)
    X<-scale(poly(data$env[1:np], 2))
    colnames(X)<-c("env","env2")
    studyDesign = data.frame(sample = as.factor(1:np))
    rL = HmscRandomLevel(units = studyDesign$sample)
    m = Hmsc(Y=as.matrix(Y_data), XData=as.data.frame(X), XFormula=~env+env2, distr="probit",
             studyDesign = studyDesign, ranLevels = list(sample = rL))
    m = sampleMcmc(m, nsamples, thin=10, adaptNf=c(200,200), transient=500,nChains=nchains ,verbose=F)
    save(m, file = name)
    return(m)
  }
  if (label=="Load"){
    return(load_object(name))
  }
}


data<-sim_data$EnvEvenSp5
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm5env.rda" )
hm_mod<-load_object("./HMmodels/hm5env.rda")

```


Convergence:

```{r hmsc convergence, include=FALSE}
hm_conv<-function(mod){
  codaList = convertToCodaObject(mod)
  #convergence histograms
  hist(effectiveSize(codaList$Beta), main="ess(beta)",lwd=2,col=gray(.6))
  hist(gelman.diag(codaList$Beta,multivariate=FALSE)$psrf,lwd=2,col=gray(.6), main="psrf(beta)")
  
  hist(effectiveSize(codaList$Omega[[1]]), main="ess(omega)",lwd=2,col=gray(.6))
  hist(gelman.diag(codaList$Omega[[1]], multivariate=FALSE)$psrf,lwd=2,col=gray(.6),      main="psrf(omega)")
}

hm_conv(hm_mod)
```



Study of interactions

```{r hmsc study of interactions, include=FALSE,results=F}
metrics_hmsc<-function(Rho, comp=NULL,fac=NULL,only_env=T){
  #{
    if(!is.null(comp) & !is.null(fac)){
    fac_comp <- fac-comp
    TP_comp <- FN_comp <-TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(fac_comp[i,j]>0 & Rho[i,j] >0)
          TP_fac=TP_fac+1
        if(fac_comp[i,j]>0 & Rho[i,j] == 0)
          FN_fac=FN_fac+1
        if(fac_comp[i,j]==0 & Rho[i,j] == 0)
           TN=TN+1
        if(fac_comp[i,j]==0 & Rho[i,j] != 0)
           FP=FP+1
        if(fac_comp[i,j]< 0 & Rho[i,j] < 0)
          TP_comp=TP_comp+1
        if(fac_comp[i,j]<0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if((fac_comp[i,j]<0 & Rho[i,j] > 0) | (fac_comp[i,j]>0 & Rho[i,j] < 0))
          wrong=wrong+1
      }
    }
    
  }else{
    if(!is.null(comp)){
    TP_comp <- FN_comp <- FP <- TN <- wrong <- 0
    TP_fac <- FN_fac<-NULL
    for(i in 1:(nrow(Rho)-1)){
      for(j in (i+1):ncol(Rho)){
        if(comp[i,j]>0 & Rho[i,j] <0)
          TP_comp=TP_comp+1
        if(comp[i,j]>0 & Rho[i,j] >0)
          wrong=wrong+1
        if(comp[i,j]>0 & Rho[i,j] == 0)
          FN_comp=FN_comp+1
        if(comp[i,j]==0 & Rho[i,j] == 0)
          TN=TN+1
        if(comp[i,j]==0 & Rho[i,j] != 0)
          FP=FP+1
      }
    }
  #  }
  #  }
  }
  if(!is.null(fac)){
    
            TP_fac <- FN_fac <- FP <- TN <- wrong <- 0
            TP_comp <- FN_comp<-NULL
            for(i in 1:(nrow(Rho)-1)){
              for(j in (i+1):ncol(Rho)){
                   if(fac[i,j]>0 & Rho[i,j] >0)
                      TP_fac=TP_fac+1
                   if(fac[i,j]>0 & Rho[i,j] <0)
                      wrong = wrong+1
                   if(fac[i,j]>0 & Rho[i,j] == 0)
                      FN_fac=FN_fac+1
                   if(fac[i,j]==0 & Rho[i,j] == 0)
                      TN=TN+1
                   if(fac[i,j]==0 & Rho[i,j] != 0)
                      FP=FP+1
              }
            }
  }
  }  
  
  if(only_env){
    
      FP <- TN <- 0
      TP_fac <- FN_fac<-TP_comp <- FN_comp<-wrong<-NULL
         for(i in 1:(nrow(Rho)-1)){
            for(j in (i+1):nrow(Rho)){
                if(Rho[i,j] != 0)
                      FP=FP+1
                if(Rho[i,j] == 0)
                      TN=TN+1
              }
            }
      
  }
  success_env<-TN/(TN+FP)
  
  if(!is.null(TP_comp)){success_comp <- TP_comp/(TP_comp+FN_comp)}else{ success_comp = NULL}
  
  if(!is.null(TP_fac)) {success_fac <- TP_fac/(TP_fac+FN_fac)}else{ success_fac = NULL}
  
  list("FP"=FP,"TN"=TN,"TP_comp"=TP_comp,"FN_comp"=FN_comp,"TP_fac"=TP_fac,"FN_fac"=FN_fac,
       "wrong"=wrong,"success_env"=success_env,"success_comp"=success_comp,"success_fac"=success_fac)
}


hm_inter<-function(mod, nchains=2,nsamples = 1000, interact=diag(ns)){
  getOmega = function(a,r=1)
  return(crossprod(a$Lambda[[r]]))
  ns<-mod$ns
  postOmega1 = array(unlist(lapply(mod$postList[[1]],getOmega)),c(ns,ns,mod$samples))
  postOmega2 = array(unlist(lapply(mod$postList[[2]],getOmega)),c(ns,ns,mod$samples))
  
  postOmega<-abind(postOmega1,postOmega2,along=3)
  postOmegaMean = apply(postOmega,c(1,2),mean)
  postOmegaUp=apply(postOmega,c(1,2),quantile,0.95)
  postOmegaLo=apply(postOmega,c(1,2),quantile,0.05)
  
  postR<-array(dim=c(ns,ns,nchains*nsamples))
  postT<-array(dim=c(ns,ns,nchains*nsamples))
  for(i in 1:dim(postOmega)[3]){
  postR[,,i]<-stats::cov2cor(postOmega[,,i])
  postT[,,i]<- -stats::cov2cor(solve(postOmega[,,i]+diag(ns)))
  }
  
  postRMean = apply(postR,c(1,2),mean)
  postRUp=apply(postR,c(1,2),quantile,0.95)
  postRLo=apply(postR,c(1,2),quantile,0.05)
  
  postTMean = apply(postT,c(1,2),mean)
  postTUp=apply(postT,c(1,2),quantile,0.95)
  postTLo=apply(postT,c(1,2),quantile,0.05)
  
  Toplot_R<-postRMean*(!(postRUp>0 & postRLo<0))
  Toplot_T<-postTMean*(!(postTUp>0 & postTLo<0))
  
  # Omegacor<- computeAssociations(m)
  # supportLevel<- 0.95
  # toPlot<- ((Omegacor[[1]]$support>supportLevel)+ (Omegacor[[1]]$support<(1-supportLevel))>0)*Omegacor[[1]]$mean
  # corrplot(toPlot, method="color", col=colorRampPalette(c("blue", "white", "red"))(200))
  
  par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
  corrplot(cor(hm_mod$Y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Correlation cor(Y)")
  corrplot(postRMean, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R")
  corrplot(Toplot_R, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Plot only non zero value")
  corrplot(Toplot_T, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Partial correlation matrix")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
  
  return(list(Rho_sign=Toplot_R,Tau_sign=Toplot_T)) 
}

hm_mod_R<-hm_inter(hm_mod,nchains=2,nsamples = 1000)

h_metric_e5<-metrics_hmsc(hm_mod_R$Rho_sign)
h_metric_e5_p<-metrics_hmsc(hm_mod_R$Tau_sign)


cat(" ")
cat(sprintf("Success rate: %s\n", metrics_hmsc(hm_mod_R$Rho_sign)$success_env))
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


# #prediction
# X<-scale(poly(data$env[1:500], 2))
# XData=as.data.frame(X)
# new<-XData[floor(seq(1, 500, length.out = 100)),]
# colnames(XData)<-c("env","env2")
# 
# pred_hm<-simplify2array(predict(hm_mod,expected=F))
# 
# pred_hm<-simplify2array(predict(hm_mod,XData=XData,expected=T))

#prediction
#pred_hm<-simplify2array(predict(hm_mod,expected=F))
x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hm_mean <- apply(pred_hm, c(1,2), mean)
pred_hm_05 <- apply(pred_hm, c(1,2), quantile,0.05)
pred_hm_95 <- apply(pred_hm, c(1,2), quantile,0.95)


pred_hmsc<- list(pred_hm_mean=pred_hm_mean,pred_hm_05=pred_hm_05,pred_hm_95=pred_hm_95)

```


## Plot species responses

```{r function response to environnment env5, include=TRUE,echo=FALSE}
create_plot_response<- function(data, nsp=5,pred_gjam, pred_jsdm,pred_hmsc ){
  np<-nrow(data)
  nspecies<-nsp
  niche_optima  = seq(2, 98, length.out=nspecies)
  niche_breadth = 20
 
  #dataframe for fundamental niches
table_fundamental<-data.frame()

for(i in 1:nspecies){
  tmp<-data.frame(xx=0:100,niche=dnorm(0:100,mean=niche_optima[i],sd=niche_breadth)/dnorm(niche_optima[i],mean=niche_optima[i],sd=niche_breadth),species=i)
  table_fundamental<-rbind(table_fundamental,tmp)
}

######## JSDM
xx<-data$env

table_jsdm<-data.frame()
pred_j_mean<-pred_jsdm$pred_j_mean
pred_j_05<-pred_jsdm$pred_j_05
pred_j_95<-pred_jsdm$pred_j_95

  
for(i in 1:nspecies) {
  tmp<-data.frame(xx=xx,mean=pred_j_mean[,i],q_95=pred_j_95[,i],q_05=pred_j_05[,i],type=rep("jsdm",np),species=rep(i,np))
  table_jsdm<-rbind(table_jsdm,tmp)
  
}
######## GJAM
table_gjam<-data.frame()

pred_gj_mean<-pred_gjam$pred_gj_mean
pred_gj_95<-pred_gjam$pred_gj_95
pred_gj_05<-pred_gjam$pred_gj_05

for(i in 1:nspecies) {
  tmp<-data.frame(xx=xx,mean=pred_gj_mean[,i],q_95=pred_gj_95[,i],q_05=pred_gj_05[,i],type=rep("gjam",np),species=rep(i,np))
  table_gjam<-rbind(table_gjam,tmp)
}

#HMSC
table_hmsc<-data.frame()
pred_hm_mean<-pred_hmsc$pred_hm_mean
pred_hm_95<-pred_hmsc$pred_hm_95
pred_hm_05<-pred_hmsc$pred_hm_05
  
for(i in 1:nspecies) {
  tmp<-data.frame(xx=xx,mean=pred_hm_mean[,i],q_95=pred_hm_95[,i],q_05=pred_hm_05[,i],type=rep("hmsc",np),species=rep(i,np))
  table_hmsc<-rbind(table_hmsc,tmp)
}
  
#table for predictions
table<-rbind(table_jsdm,table_gjam,table_hmsc)

#table for observations
Y_data = subset(data, select = -env)
table_obs<-data.frame()

for(i in 1:nspecies){
  tmp<-data.frame(xx=xx,obs=Y_data[,i],species=rep(i,np))
  table_obs<-rbind(table_obs,tmp)
}


######## FIRST TYPE OF PLOT
# 1 plot for each species, so one figure with 5 plots, in total 3 figures, one for each model
p_1<-list()
#jsdm 
for(i in 1:nsp)
local({
  i<-i
  tmp<-table_jsdm[which(table_jsdm$species==i),]
  tmp_obs<-table_obs[which(table_obs$species==i),]
  tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
  g<<-ggplot()+
    geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95),alpha=0.5)+
    geom_line(aes(x=tmp$xx,y=tmp$mean,color = "Predicted probability"),lwd=1.5)+
    geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
    geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
    labs(title=paste0("JSDM, Species ",i))+
    scale_color_manual(name = c("Legend"), values = c("Predicted probability" = "#FF6666","Fundamental niche"="#9999FF"))
    p_1<<-list.append(p_1,g)
    assign(paste0("p",i), g, pos =1)
})

if(nsp==5){
  grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
} else{ p_1}


#gjam
p_2<-list()
for(i in 1:nsp)
local({
  i<-i
  tmp<-table_gjam[which(table_gjam$species==i),]
  tmp_obs<-table_obs[which(table_obs$species==i),]
  tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
  g<<-ggplot()+
    geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95),alpha=0.5)+
    geom_line(aes(x=tmp$xx,y=tmp$mean,color = "Predicted probability"),lwd=1.5)+
    geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
    geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
    labs(title=paste0("GJAM, Species ",i))+
    scale_color_manual(name = c("Legend"), values = c("Predicted probability" = "#FF6666","Fundamental niche"="#9999FF"))

  p_2<<-list.append(p_2,g)
  assign(paste0("p",i), g, pos =1)
})

if (nsp==5){
  grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
}else{ 
  p_2
  }


#hmsc
p_3<-list()
for(i in 1:nsp)
local({
  i<-i
  tmp<-table[which(table_hmsc$species==i),]
  tmp_obs<-table_obs[which(table_obs$species==i),]
  tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
  g<<-ggplot()+
    geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95),alpha=0.5)+
    geom_line(aes(x=tmp$xx,y=tmp$mean,color = "Predicted probability"),lwd=1.5)+
    geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
    geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
    labs(title=paste0("HMSC, Species ",i))+
    scale_color_manual(name = c("Legend"), values = c("Predicted probability" = "#FF6666","Fundamental niche"="#9999FF"))
   p_3<<-list.append(p_3,g)
  assign(paste0("p",i), g, pos =1)
})

#x11()
if (nsp==5){
  grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
}else{ 
  p_3
  }




########SECOND TYPE OF PLOT
p_4<-list()
for(i in 1:nsp)
local({
  i<-i
  tmp<-table[which(table$species==i),]
  tmp_obs<-table_obs[which(table_obs$species==i),]
  tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
  g<<-ggplot()+
    geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95,col=as.factor(tmp$type)),alpha=0.5)+
    geom_line(aes(x=tmp$xx,y=tmp$mean,col=as.factor(tmp$type)),lwd=1.5)+
    geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
    geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
    labs(title=paste0("All models, Species ",i))+
    scale_color_manual(name = c("Legend"), values = c("jsdm" = "#FF6666","gjam" = "#FFFF66","hmsc" = "#FFB266","Fundamental niche"="#9999FF"))
  p_4<<-list.append(p_4,g)
  assign(paste0("p",i), g, pos =1)
})

if (nsp==5){
  grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
}else{ 
  p_4
  }
#x11()
#grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
  
}

create_plot_response(sim_data$EnvEvenSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )

```




```{r response to environnment env5, include=TRUE,echo=FALSE}
# # to be finished
# #fundamental niche
# 
# np<-500
# nspecies<-5
# niche_optima  = seq(2, 98, length.out=nspecies)
# niche_breadth = 20
# 
# #dataframe for fundamental niches
# table_fundamental<-data.frame()
# 
# for(i in 1:nspecies){
#   tmp<-data.frame(xx=0:100,niche=dnorm(0:100,mean=niche_optima[i],sd=niche_breadth)/dnorm(niche_optima[i],mean=niche_optima[i],sd=niche_breadth),species=i)
#   table_fundamental<-rbind(table_fundamental,tmp)
# }
# 
# xx<-data$env
# 
# table_jsdm<-data.frame()
#   
# for(i in 1:nspecies) {
#   tmp<-data.frame(xx=xx,mean=pred_j_mean[,i],q_95=pred_j_95[,i],q_05=pred_j_05[,i],type=rep("jsdm",np),species=rep(i,np))
#   table_jsdm<-rbind(table_jsdm,tmp)
# }
# 
# 
# table_gjam<-data.frame()
#   
# for(i in 1:nspecies) {
#   tmp<-data.frame(xx=xx,mean=pred_gj_mean[,i],q_95=pred_gj_95[,i],q_05=pred_gj_05[,i],type=rep("gjam",np),species=rep(i,np))
#   table_gjam<-rbind(table_gjam,tmp)
# }
# 
# 
# table_hmsc<-data.frame()
#   
# for(i in 1:nspecies) {
#   tmp<-data.frame(xx=xx,mean=pred_hm_mean[,i],q_95=pred_hm_95[,i],q_05=pred_hm_05[,i],type=rep("hmsc",np),species=rep(i,np))
#   table_hmsc<-rbind(table_hmsc,tmp)
# }
#   
# #table for predictions
# table<-rbind(table_jsdm,table_gjam,table_hmsc)
# 
# #table for observations
# Y_data = subset(data, select = -env)
# 
# table_obs<-data.frame()
# 
# for(i in 1:nspecies){
#   tmp<-data.frame(xx=xx,obs=Y_data[,i],species=rep(i,np))
#   table_obs<-rbind(table_obs,tmp)
# }
# 
# 
# ######## FIRST TYPE OF PLOT
# # 1 plot for each species, so one figure with 5 plots, in total 3 figures, one for each model
# 
# #jsdm 
# 
# for(i in 1:5)
# local({
#   i<-i
#   tmp<-table_jsdm[which(table_jsdm$species==i),]
#   tmp_obs<-table_obs[which(table_obs$species==i),]
#   tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
#   g<<-ggplot()+
#     geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95),alpha=0.5)+
#     geom_line(aes(x=tmp$xx,y=tmp$mean,color = "Predicted probability"),lwd=1.5)+
#     geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
#     geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
#     labs(title=paste0("JSDM, Species ",i))+
#     scale_color_manual(name = c("Legend"), values = c("Predicted probability" = "#FF6666","Fundamental niche"="#9999FF"))
# 
#     assign(paste0("p",i), g, pos =1)
# })
# 
# 
# grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
# 
# 
# 
# #gjam
# for(i in 1:5)
# local({
#   i<-i
#   tmp<-table_gjam[which(table_gjam$species==i),]
#   tmp_obs<-table_obs[which(table_obs$species==i),]
#   tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
#   g<<-ggplot()+
#     geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95),alpha=0.5)+
#     geom_line(aes(x=tmp$xx,y=tmp$mean,color = "Predicted probability"),lwd=1.5)+
#     geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
#     geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
#     labs(title=paste0("GJAM, Species ",i))+
#     scale_color_manual(name = c("Legend"), values = c("Predicted probability" = "#FF6666","Fundamental niche"="#9999FF"))
# 
#   
#   assign(paste0("p",i), g, pos =1)
# })
# 
# 
# grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
# 
# 
# #hmsc
# for(i in 1:5)
# local({
#   i<-i
#   tmp<-table[which(table_hmsc$species==i),]
#   tmp_obs<-table_obs[which(table_obs$species==i),]
#   tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
#   g<<-ggplot()+
#     geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95),alpha=0.5)+
#     geom_line(aes(x=tmp$xx,y=tmp$mean,color = "Predicted probability"),lwd=1.5)+
#     geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
#     geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
#     labs(title=paste0("HMSC, Species ",i))+
#     scale_color_manual(name = c("Legend"), values = c("Predicted probability" = "#FF6666","Fundamental niche"="#9999FF"))
# 
#   assign(paste0("p",i), g, pos =1)
# })
# 
# x11()
# grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
# 
# 
# 
# ########SECOND TYPE OF PLOT
# for(i in 1:5)
# local({
#   i<-i
#   tmp<-table[which(table$species==i),]
#   tmp_obs<-table_obs[which(table_obs$species==i),]
#   tmp_fund<-table_fundamental[which(table_fundamental$species==i),]
#   g<<-ggplot()+
#     geom_ribbon(aes(x=tmp$xx,ymin=tmp$q_05,ymax=tmp$q_95,col=as.factor(tmp$type)),alpha=0.5)+
#     geom_line(aes(x=tmp$xx,y=tmp$mean,col=as.factor(tmp$type)),lwd=1.5)+
#     geom_point(aes(x=tmp_obs$xx,y=tmp_obs$obs),col="#000066",size=0.5) +xlab("Environmental gradient")+ylab("Probability of presence")+
#     geom_line(data=tmp_fund,aes(x=tmp_fund$xx,y=tmp_fund$niche,color = "Fundamental niche"),lwd=1)+
#     labs(title=paste0("HMSC, Species ",i))+
#     scale_color_manual(name = c("Legend"), values = c("jsdm" = "#FF6666","gjam" = "#FFFF66","hmsc" = "#FFB266","Fundamental niche"="#9999FF"))
#   assign(paste0("p",i), g, pos =1)
# })
# 
# x11()
# grid.arrange(p1,p2,p3,p4,p5,nrow=ceiling(nspecies/2))
# 
# 


```


## Plot coefficients


```{r beta coefs env5, include=TRUE,echo=FALSE}

prepare_table<- function(datab,name,class){
  data_new<-as.data.frame(datab) 
  colnames(data_new) <- c("inter","env","env2")
  data_new$sp<-as.character(seq.int(nrow(data_new)))
  data_out<- melt(data_new, id=c("sp"), variable_name = "beta")
  colnames(data_out)[colnames(data_out)=="value"] <-name
  data_out$model<-class
  return(data_out)
}

########GJAM####################################################
prepare_beta_gjam<-function(datab,name,class){
  beta_out<-melt(datab)
  beta_out$rn<-rownames(beta_out)
  beta_out$sp<- as.character(as.numeric(substr(beta_out$rn,3,4)))
  beta_out$beta<- sapply(beta_out$rn,function(x) strsplit(x,"_")[[1]][2])
  colnames(beta_out)[colnames(beta_out)=="value"] <-name
  beta_out$model<- class
  beta_out$beta[which(beta_out$beta=="intercept")] <-"inter"
  return(beta_out[,c("beta","sp","model",name)])
}



####hmsc

prepare_beta_hmsc<-function(datab,name,class,vcol,vrow){
  colnames(datab)<- vcol
  rownames(datab)<-vrow
  beta_out<-melt(datab,value.name = "mean",varnames=c('beta', 'sp'))
  beta_out$sp<- as.character(as.numeric(substr(beta_out$sp,4,5)))
  colnames(beta_out)[colnames(beta_out)=="value"] <-name
  beta_out$model<- class
  beta_out$beta<-as.character(beta_out$beta)
  beta_out$beta[which(beta_out$beta=="(Intercept)")] <-"inter"
  colnames(beta_out)[colnames(beta_out)=="value"] <-name
  return(beta_out[,c("beta","sp","model",name)])
}



create_beta_plot<- function(gjmod, jsdmmod, hmmod){
  nsp<-hmmod$ns
  beta_mean<-prepare_table(jsdmmod$mean$B,name="mean",class="jsdm")
  beta_q25<-prepare_table(datab=jsdmmod$q2.5$B,name="low",class="jsdm")
  beta_q97<-prepare_table(jsdmmod$q97.5$B,name="high",class="jsdm")
  beta_jsdm<-merge(beta_mean,beta_q25, by=c("beta","sp","model"))
  beta_jsdm<-merge(beta_jsdm,beta_q97,by=c("beta","sp","model"))

########GJAM###################################################
  
  beta_mean_raw<- apply(gjmod$chains$bgibbsUn,2,mean)
  beta_q25_raw<- apply(gjmod$chains$bgibbsUn,2,quantile,0.025)
  beta_q97_raw<- apply(gjmod$chains$bgibbsUn,2,quantile,0.975)
  
  beta_mean<- prepare_beta_gjam(beta_mean_raw,"mean", "gjam")
  beta_q25<- prepare_beta_gjam(beta_q25_raw,"low", "gjam")
  beta_q97<- prepare_beta_gjam(beta_q97_raw,"high", "gjam")
  
  beta_gjam<-merge(beta_mean,beta_q25, by=c("beta","sp","model"))
  beta_gjam<-merge(beta_gjam,beta_q97,by=c("beta","sp","model"))

####hmsc
  
  beta_hm<-array(NA,dim=c(hmmod$nc,hmmod$ns,2*hmmod$samples)) #2 is nchains
  for(k in 1:(2*hmmod$samples)){
      if(k<=hmmod$samples){beta_hm[,,k] <- hmmod$postList[[1]][[k]]$Beta
      }else {beta_hm[,,k] <- hmmod$postList[[2]][[k-hmmod$samples]]$Beta}
  
  }
  beta_mean_raw<- apply(beta_hm,c(1,2),mean)
  beta_q25_raw<- apply(beta_hm,c(1,2),quantile,0.025)
  beta_q97_raw<- apply(beta_hm,c(1,2),quantile,0.975)

  
  beta_mean<- prepare_beta_hmsc(datab=beta_mean_raw,name="mean", class="hmsc",vcol=hmmod$spNames,vrow=hmmod$covNames)
  beta_q25<- prepare_beta_hmsc(beta_q25_raw,"low", "hmsc",vcol=hmmod$spNames,vrow=hmmod$covNames)
  beta_q97<- prepare_beta_hmsc(beta_q97_raw,"high", "hmsc",vcol=hmmod$spNames,vrow=hmmod$covNames)
  
  beta_hmsc<-merge(beta_mean,beta_q25, by=c("beta","sp","model"))
  beta_hmsc<-merge(beta_hmsc,beta_q97,by=c("beta","sp","model"))
  

  
  data_beta<-rbind(beta_gjam,beta_jsdm,beta_hmsc)
  data_beta$name<- "Specie"
  data_beta$name<- paste(data_beta$name,data_beta$sp)
  data_beta[, 'model'] <- as.factor(data_beta[, 'model'])
  
  
if(nsp==5){
p <- ggplot(data_beta, aes(mean, beta, colour = model))
q<- p + geom_point( size = 2) +xlab("Environmental gradient")+ylab("Coefficients")+scale_y_discrete(
        labels=c("inter" =expression(beta[0]),"env" = expression(beta[1]),"env2" = expression(beta[2])))+
  geom_errorbarh(aes(xmax = high, xmin = low, height = .3))+ facet_grid(name ~.,scales = "free")+
  geom_vline(aes(xintercept = 0),size = 0.2, colour = "red") + theme(strip.text.x = element_text(size = 10, colour = "black")) +
   ggtitle("Comparison of the estimated covariates coefficiens")
q
}else{
for(i in 1:nsp){
  tmp<-data_beta[which(data_beta$sp==i),]
  p <- ggplot(tmp, aes(mean, beta, colour = model))
  q<- p + geom_point( size = 2) +xlab("Environmental gradient")+ylab("Coefficients")+scale_y_discrete(
        labels=c("inter" =expression(beta[0]),"env" = expression(beta[1]),"env2" = expression(beta[2])))+
  geom_errorbarh(aes(xmax = high, xmin = low, height = .3))+
  geom_vline(aes(xintercept = 0),size = 0.2, colour = "red") + theme(strip.text.x = element_text(size = 10, colour = "black")) +
   ggtitle(paste("Comparison of the estimated covariates coefficiens for specie ",i))
print(q)
 }
}
}

#######
create_beta_plot(load_object("./gjam_models/gjam5env.rda"),me5,hmmod=load_object("./HMmodels/hm5env.rda"))

```




```{r all models env5, include=TRUE}

ALL3<-function(jsdm_mod,gjam_mod,hmsc_mod,interact=diag(5)){
 par(mfrow=c(2,2),oma = c(1, 1, 1, 1))
  corrplot(jsdm_mod, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R  JSDM ")
  corrplot(gjam_mod, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R GJAM")
  corrplot(hmsc_mod, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("R HMSC")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
}
ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,diag(5))

```



```{r all models tau env5, include=TRUE}

ALL4<-function(jsdm_mod,gjam_mod,hmsc_mod,interact=diag(5)){
 par(mfrow=c(2,2),oma = c(1, 1, 1, 1))
  #corrplot(jsdm_mod, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  #title("Partial correlation  JSDM ")
  corrplot(gjam_mod, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Partial correlation GJAM")
  corrplot(hmsc_mod, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Partial correlation HMSC")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,diag(5))

```

## Environmental filtering 10 species

### JSDM

```{r load_m en10,include=FALSE}
me10 <- load_object("model-2019-04-10-08-26-20.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me10)
jsdm_conv(me10)
me10$mcmc.info[1:7]

j_metric_e10<-metrics_jsdm(me10)
cat("Success rate ")
j_metric_e10$success_env

data<-sim_data$EnvEvenSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

plot_cor_jsdm<-function(mod,y,interact=diag(ncol(y))){
  par(mfrow=c(2,4),oma = c(3, 1, 2, 1))
  corrplot(cor(y), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Correlation cor(Y)")
  corrplot(mod$mean$EnvRho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("EnvRho")
  corrplot(mod$mean$EnvRho*(!mod$overlap0$EnvRho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("EnvRho signif")
  corrplot(mod$mean$Rho, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Rho")
  corrplot(mod$mean$Rho*(!mod$overlap0$Rho), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("Rho signif")
  corrplot(interact, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
  title("True interactions")
}

#plot_cor_jsdm(me10,data$Y)
###Correlation
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =me10$mean$Rho*(!me10$overlap0$Rho)) 
mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =me10$mean$Rho*(!me10$overlap0$Rho)) 
##Prediction
# pred_j<-pnorm(predict_y_jsdm(me10))
# pred_j_mean <- apply(pred_j, 1:2, mean)
# pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
# pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_j<-array(NA,dim=c(data$n,data$J,me10$mcmc.info$n.samples))
for(i in 1:me10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(me10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)
  

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
```

### Gjam

```{r gjam en10,include=FALSE}
data<-sim_data$EnvEvenSp10

#gjam_mod<-fit_gjam(data,3000,500,"./gjam_models/gjam10env.rda")
gjam_mod<-load_gjam(data,3000,500,name="./gjam_models/gjam10env.rda")
#gje10<-load_object("./gjam_models/gjam10env.rda")

g_metric_e10<-metrics_gjam(gjam_mod$Rho_sign)
g_metric_e10_p<-metrics_gjam(gjam_mod$Tau_sign)
cat("Success rate ")
g_metric_e10$success_env
###Correlation
mod_list_Rho<-list.append(mod_list_Rho,gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau,gjam=gjam_mod$Tau_sign) 
##Prediction
pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)
pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```

### HMSC
```{r hmsc en10,include=FALSE}
data<-sim_data$EnvEvenSp10
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm10env.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod)

h_metric_e10<-metrics_hmsc(hm_mod_R$Rho_sign)
h_metric_e10_p<-metrics_hmsc(hm_mod_R$Tau_sign)


cat(" ")
cat(sprintf("Success rate: %s\n", h_metric_e10$success_env))
cat(sprintf("Success rate: %s\n", h_metric_e10$success_fac))

mod_list_Rho<-list.append(mod_list_Rho, hmsc=hm_mod_R$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, hmsc=hm_mod_R$Tau_sign) 


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))


#plot(data$env,pred_hmsc$pred_hm_mean[,1])


```


```{r all models rho env10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam10env.rda"),me10,load_object("./HMmodels/hm10env.rda"))
#data, nsp=5,pred_gjam, pred_jsdm,pred_hmsc 
create_plot_response(data=sim_data$EnvEvenSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,diag(10))

```


```{r all models tau env10, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,diag(10))

```


## Environmental filtering 20 species

### JSDM

```{r load_m en20,include=FALSE}
me20 <- load_object("model-2019-04-11-19-06-02.rda")
#load("model-2019-04-09-19-02-16.rda")
summary(me20)

me20$mcmc.info[1:7]

jsdm_conv(me20)

j_metric_e20<-metrics_jsdm(me20)
cat("Success rate ")
j_metric_e20$success_env

data<-sim_data$EnvEvenSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################

plot_cor_jsdm(me20,data$Y)

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =me20$mean$Rho*(!me20$overlap0$Rho)) 
mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =me20$mean$Rho*(!me20$overlap0$Rho)) 
 
pred_j<-array(NA,dim=c(data$n,data$J,me20$mcmc.info$n.samples))
for(i in 1:me20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(me20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)
  


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)


```


### Gjam

```{r gjam en20,include=FALSE}

  data<-sim_data$EnvEvenSp20
  
  #gjam_mod<-fit_gjam(data,5000,500,"./gjam_models/gjam20env.rda")
  
  gjam_mod<-load_gjam(data,5000,500,name="./gjam_models/gjam20env.rda")
  #gje20<-load_object("./gjam_models/gjam20env.rda")
  
  g_metric_e20<-metrics_gjam(gjam_mod$Rho_sign)
  g_metric_e20_p<-metrics_gjam(gjam_mod$Tau_sign)
  
  cat(" ")
  cat(sprintf("Success rate env: %s\n", round(metrics_gjam(gjam_mod$Rho_sign)$success_env,3)))
  
  #to check posterior density of s in Sigma 
  #gje20<-load_object("./gjam_models/gjam20env.rda")
  #plot(density(gje20$chains$sgibbs[,4]))
  
  mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
  mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 
  
  pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
  pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
  pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)
  
  pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```




### Gjam dimension reduction

```{r gjam en20 dim red, include=FALSE}
# 
# data<-sim_data$EnvEvenSp20
# 
# #fit_gjam(data,5000,500,"./gjam_models/gjam20env.rda")
# 
# #load_gjam(data,name="./gjam_models/gjam20env.rda")
# #gje20<-load_object("./gjam_models/gjam20env.rda")
# 
# 
# #to check posterior density of s in Sigma 
# #gje20<-load_object("./gjam_models/gjam20env.rda")
# #plot(density(gje20$chains$sgibbs[,4]))
#  data <- list(
#     Y = subset(data, select = -env),
#     X = cbind(1, scale(poly(data$env, 2))),
#     covx = cov(cbind(1, scale(poly(data$env, 2)))),
#     K = 3,
#     J = ncol(data) - 1,
#     n = nrow(data),
#     I = diag(ncol(data) - 1),
#     df = ncol(data)
#   )
# xdata<-as.data.frame(data$X[,-1])
# colnames(xdata)<- c("env","env2")
# ydata<-as.data.frame(data$Y)
# ###formula
# rl   <- list(r = 8, N = 20)
# formula<-as.formula( ~env+ env2)
# ml  <- list(ng = 2500, burnin = 500, typeNames = 'PA', reductList = rl)
# ####fit
# 
# 
# mod_gjam1 <- gjam(formula, xdata = xdata, ydata = ydata, modelList = ml)
# save(mod_gjam1, file = "./gjam_models/gjam20env_dr.rda")
# summary(mod_gjam1)
# 
# Tau <- solve(mod_gjam1$parameters$sigMu)
# Tau_n = to_prec(Tau)
# 
# #postH<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.95)
# #postL<-apply(mod_gjam1$chains$sgibbs, 2, quantile,0.05)
# 
# 
# #pH<-convert_to_m(postH)
# #pL<-convert_to_m(postL)
# 
# #R_sign<-cov2cor(mod_gjam1$parameters$sigMu)*(!(pH>0 & pL<0))
# 
# g_metric_e20_dim_red<-metrics_gjam(Rho_sign)
# cat("Success rate ")
# g_metric_e20_dim_red$success_env
# 
# par(mfrow=c(2,3),oma = c(1, 1, 1, 1))
# corrplot(cor(ydata), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
# title("Correlation cor(Y)")
# corrplot(mod_gjam1$parameters$corMu, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
# title("R")
# corrplot(mod_gjam1$parameters$ematrix, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
# title("E matrix")
# # corrplot(Tau_n, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# # title("Tau")
# # corrplot(R_sign, diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", type = "lower")
# # title("R signif")
# corrplot(diag(20), diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
# title("True interactions")
# 


```

```{r hmsc en20,include=FALSE}

data<-sim_data$EnvEvenSp20
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm20env.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod)

h_metric_e20<-metrics_hmsc(hm_mod_R$Rho_sign)
h_metric_e20_p<-metrics_hmsc(hm_mod_R$Tau_sign)

cat("Success score ")
h_metric_e20$success_env
cat(" ")
cat(sprintf("Success rate non-interacting: %s\n", round(metrics_hmsc(hm_mod_R$Rho_sign)$success_env,3)))

mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

# pred_hm_mean <- apply(pred_hm, c(1,2), mean)
# pred_hm_05 <- apply(pred_hm, c(1,2), quantile,0.05)
# pred_hm_95 <- apply(pred_hm, c(1,2), quantile,0.95)
# 

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```




```{r all models env20, include=TRUE}

create_beta_plot(load_object("./gjam_models/gjam20env.rda"),me20,load_object("./HMmodels/hm20env.rda"))

create_plot_response(sim_data$EnvEvenSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,diag(20))

```




```{r all models tau env20, include=TRUE}

ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,diag(20))

```


## Environmental filtering + Facilitation dense 5 species

### JSDM

```{r load_m facd5,include=FALSE}
#mfd5 <- load_object("model-2019-04-11-19-35-11.rda")
mfd5 <- load_object("model-jsdm-2019-05-06-18-41-20.rda")
summary(mfd5)
#mfd5$Rhat
jsdm_conv(mfd5)
mfd5$mcmc.info[1:7]

j_metric_facDense5<-metrics_jsdm(mfd5,fac = fac_inter[[4]],only_env = F)
cat("Success rate ")
j_metric_facDense5$success_env
j_metric_facDense5$success_fac

data<-sim_data$FacDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

##########################################################################################
#Tau<-solve
#Tau_n<-to_prec(me10$mean$Tau)
#Tau_k<-Tau_n*(!(model$q97.5$Tau>0 & model$q2.5$Tau<0))

#plot_cor_jsdm(mfd5,data$Y,fac_inter[[4]])

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mfd5$mean$Rho*(!mfd5$overlap0$Rho)) 
 mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mfd5$mean$Rho*(!mfd5$overlap0$Rho)) 
 
pred_j<-array(NA,dim=c(data$n,data$J,mfd5$mcmc.info$n.samples))
for(i in 1:mfd5$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mfd5$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
  
```

### Gjam

```{r gjam fd5,include=FALSE}
data<-sim_data$FacDenseSp5
#gjam_mod<-fit_gjam(data,10000,2000,"./gjam_models/gjam5f.rda",interact=fac_inter[[4]])
gjam_mod<-load_gjam(data,10000,2000,name="./gjam_models/gjam5f.rda", interact=fac_inter[[4]])
#gjfd5<-load_object("./gjam_models/gjam5f.rda")

g_metric_facDense5<-metrics_gjam(gjam_mod$Rho_sign,fac=fac_inter[[4]], only_env = F)
g_metric_facDense5_p<-metrics_gjam(gjam_mod$Tau_sign,fac=fac_inter[[4]], only_env = F)

#cat("Success rate ")
#g_metric_facDense5$success_env
#g_metric_facDense5$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5f.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facDense5$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho,gjam=gjam_mod$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,gjam=gjam_mod$Tau_sign)


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```



### HMSC
```{r hmsc fd5,include=FALSE}
data<-sim_data$FacDenseSp5
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm5fd.rda" )
hm_conv(hm_mod)
hm_inter(hm_mod, interact = fac_inter[[4]])
hm_mod_R<-hm_inter(hm_mod)

h_metric_facDense5<-metrics_hmsc(hm_mod_R$Rho_sign,fac=fac_inter[[4]],only_env = F)
h_metric_facDense5_p<-metrics_hmsc(hm_mod_R$Tau_sign,fac=fac_inter[[4]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facDense5$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

# pred_hm_mean <- apply(pred_hm, c(1,2), mean)
# pred_hm_05 <- apply(pred_hm, c(1,2), quantile,0.05)
# pred_hm_95 <- apply(pred_hm, c(1,2), quantile,0.95)
# 

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))


```



```{r all models facd5, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam5f.rda"),mfd5,load_object("./HMmodels/hm5fd.rda" ))

create_plot_response(sim_data$FacDenseSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,fac_inter[[4]])

```

```{r all models tau facd5, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,diag(10))

```



## Environmental filtering + Facilitation dense 10 species

### JSDM

```{r model jsdm fd10, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfd10 <- load_object("model-2019-04-12-06-59-42.rda")

summary(mfd10)
jsdm_conv(mfd10)
mfd10$mcmc.info[1:7]

j_metric_facDense10<-metrics_jsdm(mfd10,fac = fac_inter[[5]],only_env = F)
cat("Success rate ")
j_metric_facDense10$success_env
j_metric_facDense10$success_fac

######################################################Prepare data
data<-sim_data$FacDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

######################################################Plot 

#plot_cor_jsdm(mfd10,data$Y,fac_inter[[5]])
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mfd10$mean$Rho*(!mfd10$overlap0$Rho))  

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mfd10$mean$Rho*(!mfd10$overlap0$Rho)) 

pred_j<-array(NA,dim=c(data$n,data$J,mfd10$mcmc.info$n.samples))
for(i in 1:mfd10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mfd10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


```{r gjam fd10,include=FALSE}

data<-sim_data$FacDenseSp10

#Rho_sign<-fit_gjam(data,5000,500,"./gjam_models/gjam10fd.rda",interact=fac_inter[[5]])
gjam_mod<- load_gjam(data,5000,500,name="./gjam_models/gjam10fd.rda", interact=fac_inter[[5]])
#gjfd5<-load_object("./gjam_models/gjam10fd.rda")

g_metric_facDense10<-metrics_gjam(gjam_mod$Rho_sign,fac=fac_inter[[5]], only_env = F)
g_metric_facDense10_p<-metrics_gjam(gjam_mod$Tau_sign,fac=fac_inter[[5]], only_env = F)

# cat("Success rate ")
# g_metric_facDense10$success_env
# g_metric_facDense10$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam10fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facDense10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facDense10$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho,gjam=gjam_mod$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,gjam=gjam_mod$Tau_sign)

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)



```


### HMSC

```{r model2 hmsc, echo=FALSE,include=FALSE}
data<-sim_data$FacDenseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples = 2000,nchains=2,name="./HMmodels/hm10fd.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples = 2000,nchains=2,interact = fac_inter[[5]])

h_metric_facDense10<-metrics_hmsc(hm_mod_R$Rho_sign,fac=fac_inter[[5]],only_env = F)
h_metric_facDense10_p<-metrics_hmsc(hm_mod_R$Tau_sign,fac=fac_inter[[5]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facDense10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facDense10$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

# pred_hm_mean <- apply(pred_hm, c(1,2), mean)
# pred_hm_05 <- apply(pred_hm, c(1,2), quantile,0.05)
# pred_hm_95 <- apply(pred_hm, c(1,2), quantile,0.95)
# 

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))


```


```{r all models facd10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam10fd.rda"),mfd10,load_object("./HMmodels/hm10fd.rda"))

create_plot_response(sim_data$FacDenseSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,fac_inter[[5]])

```


```{r all models tau facd10, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,fac_inter[[5]])

```


## Environmental filtering + Facilitation dense 20 species

### JSDM

```{r model jsdm fd20, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfd20 <- load_object("model-2019-04-13-17-22-12.rda")

summary(mfd20)
#mfd20$Rhat
jsdm_conv(mfd20)
mfd20$mcmc.info[1:7]

j_metric_facDense20<-metrics_jsdm(mfd20,fac = fac_inter[[6]],only_env = F)
cat("Success rate ")
j_metric_facDense20$success_env
j_metric_facDense20$success_fac

######################################################Prepare data
data<-sim_data$FacDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

#Tau_n<-to_prec(mfd20$mean$Tau)
#plot_cor_jsdm(mfd20,data$Y,fac_inter[[6]])

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mfd20$mean$Rho*(!mfd20$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mfd20$mean$Rho*(!mfd20$overlap0$Rho)) 

pred_j<-array(NA,dim=c(data$n,data$J,mfd20$mcmc.info$n.samples))
for(i in 1:mfd20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mfd20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


### Gjam


```{r gjam fd20,include=FALSE}

data<-sim_data$FacDenseSp20

#Rho_sign<-fit_gjam(data,10000,1500,"./gjam_models/gjam20fd.rda",interact=fac_inter[[6]])
gjam_mod<-load_gjam(data,10000,1500,name="./gjam_models/gjam20fd.rda", interact=fac_inter[[6]])
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")

g_metric_facDense20<-metrics_gjam(gjam_mod$Rho_sign,fac=fac_inter[[6]], only_env = F)
g_metric_facDense20_p<-metrics_gjam(gjam_mod$Tau_sign,fac=fac_inter[[6]], only_env = F)

# cat("Success rate ")
# g_metric_facDense20$success_env
# g_metric_facDense20$success_fac
# 
#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facDense20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facDense20$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)


```


### HMSC
```{r hmsc fd20,include=FALSE}
data<-sim_data$FacDenseSp20
hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm20fd.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, interact = fac_inter[[6]])

h_metric_facDense20<-metrics_hmsc(hm_mod_R$Rho_sign,fac=fac_inter[[6]],only_env = F)
h_metric_facDense20_p<-metrics_hmsc(hm_mod_R$Tau_sign,fac=fac_inter[[6]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facDense20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facDense20$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

# pred_hm_mean <- apply(pred_hm, c(1,2), mean)
# pred_hm_05 <- apply(pred_hm, c(1,2), quantile,0.05)
# pred_hm_95 <- apply(pred_hm, c(1,2), quantile,0.95)
# 

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))


```



```{r all models facd20, include=TRUE}

create_beta_plot(load_object("./gjam_models/gjam20fd.rda"),mfd20,load_object("./HMmodels/hm20fd.rda"))

create_plot_response(sim_data$FacDenseSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,fac_inter[[6]])

```


```{r all models tau facd20, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,fac_inter[[6]])

```



## Environmental filtering + Facilitation sparse 5 species

### JSDM


```{r model jsdm fs5, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs5 <- load_object("model-2019-04-13-17-51-16.rda")

summary(mfs5)
#mfs5$Rhat
jsdm_conv(mfs5)

mfs5$mcmc.info[1:7]

j_metric_facSparse5<-metrics_jsdm(mfs5,fac = fac_inter[[7]],only_env = F)
# cat("Success rate ")
# j_metric_facSparse5$success_env
# j_metric_facSparse5$success_fac
# cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_facSparse5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_facSparse5$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
#plot_cor_jsdm(mfs5,data$Y,fac_inter[[7]])

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mfs5$mean$Rho*(!mfs5$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mfs5$mean$Rho*(!mfs5$overlap0$Rho)) 

pred_j<-array(NA,dim=c(data$n,data$J,mfs5$mcmc.info$n.samples))
for(i in 1:mfs5$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mfs5$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


### Gjam

```{r gjam fs5,include=FALSE}

data<-sim_data$FacSparseSp5

#Rho_sign<-fit_gjam(data,2500,500,"./gjam_models/gjam5fs.rda",interact=fac_inter[[7]])
gjam_mod<-load_gjam(data,2500,500,name="./gjam_models/gjam5fs.rda", interact=fac_inter[[7]])
#gjfd5<-load_object("./gjam_models/gjam5fs.rda")

g_metric_facSparse5<-metrics_gjam(gjam_mod$Rho_sign,fac=fac_inter[[7]], only_env = F)
g_metric_facSparse5_p<-metrics_gjam(gjam_mod$Tau_sign,fac=fac_inter[[7]], only_env = F)

# cat("Success rate ")
# g_metric_facSparse5$success_env
# g_metric_facSparse5$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facSparse5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facSparse5$success_fac,3)))

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))

mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)



```

### HMSC
```{r hmsc fs5,include=FALSE}
data<-sim_data$FacSparseSp5

hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm5fs.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, interact = fac_inter[[7]])
h_metric_facSparse5<-metrics_hmsc(hm_mod_R$Rho_sign,fac=fac_inter[[8]],only_env = F)
h_metric_facSparse5_p<-metrics_hmsc(hm_mod_R$Tau_sign,fac=fac_inter[[8]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse5$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

# pred_hm_mean <- apply(pred_hm, c(1,2), mean)
# pred_hm_05 <- apply(pred_hm, c(1,2), quantile,0.05)
# pred_hm_95 <- apply(pred_hm, c(1,2), quantile,0.95)
# 

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))



```





```{r all models fs5, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam5fs.rda"),mfs5,load_object("./HMmodels/hm5fs.rda"))

create_plot_response(sim_data$FacSparseSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,fac_inter[[7]])

```


```{r all models tau fs5, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,fac_inter[[7]])

```

## Environmental filtering + Facilitation sparse 10 species

### JSDM

```{r model jsdm fs10, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs10 <- load_object("model-2019-04-14-05-17-58.rda")

summary(mfs10)
#mfs10$Rhat
jsdm_conv(mfs10)
mfs10$mcmc.info[1:7]

j_metric_facSparse10<-metrics_jsdm(mfd10,fac = fac_inter[[8]],only_env = F)
# cat("Success rate ")
# j_metric_facSparse10$success_env
# j_metric_facSparse10$success_fac
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_facSparse10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_facSparse10$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
#plot_cor_jsdm(mfs10,data$Y,fac_inter[[8]])


mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mfs10$mean$Rho*(!mfs10$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mfs10$mean$Rho*(!mfs10$overlap0$Rho)) 
 
pred_j<-array(NA,dim=c(data$n,data$J,mfs10$mcmc.info$n.samples))
for(i in 1:mfs10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mfs10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```

```{r gjam fs10,include=FALSE}

data<-sim_data$FacSparseSp10

#Rho_sign<-fit_gjam(data,2500,500,"./gjam_models/gjam10fs.rda",interact=fac_inter[[8]])
gjam_mod<-load_gjam(data,name="./gjam_models/gjam10fs.rda", interact=fac_inter[[8]])
#gjfd5<-load_object("./gjam_models/gjam10fs.rda")

g_metric_facSparse10<-metrics_gjam(gjam_mod$Rho_sign,fac=fac_inter[[8]], only_env = F)
g_metric_facSparse10_p<-metrics_gjam(gjam_mod$Tau_sign,fac=fac_inter[[8]], only_env = F)

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam10fs.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facSparse10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facSparse10$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)


```

### HMSC
```{r hmsc fs10,include=FALSE}
data<-sim_data$FacSparseSp10

hm_mod<-fit_hmsc(data,"Load",name="./HMmodels/hm10fs.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, interact = fac_inter[[8]])
h_metric_facSparse10<-metrics_hmsc(hm_mod_R$Rho_sign,fac=fac_inter[[8]],only_env = F)
h_metric_facSparse10_p<-metrics_hmsc(hm_mod_R$Tau_sign,fac=fac_inter[[8]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse10$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))
```


```{r all models fs10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam10fs.rda"),mfs10,load_object("./HMmodels/hm10fs.rda"))

create_plot_response(sim_data$FacSparseSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )
ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,fac_inter[[8]])
```



```{r all models tau fs10, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,fac_inter[[8]])
```


## Environmental filtering + Facilitation sparse 20 species

### JSDM


```{r model jsdm fs20, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mfs20 <- load_object("model-2019-04-15-15-34-20.rda")

summary(mfs20)
#mfs20$Rhat
jsdm_conv(mfs20)
mfs20$mcmc.info[1:7]

j_metric_facSparse20<-metrics_jsdm(mfs20,fac = fac_inter[[9]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_facSparse20$success_fac,3)))
######################################################Prepare data
data<-sim_data$FacSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mfs20$mean$Rho*(!mfs20$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mfs20$mean$Rho*(!mfs20$overlap0$Rho)) 
 
pred_j<-array(NA,dim=c(data$n,data$J,mfs20$mcmc.info$n.samples))
for(i in 1:mfs20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mfs20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


### Gjam

```{r gjam fs20,include=FALSE}

data<-sim_data$FacSparseSp20

#fit_gjam(data,10000,1500,"./gjam_models/gjam20fs.rda",interact=fac_inter[[9]])
gjam_mod <-load_gjam(data,10000,1500,name="./gjam_models/gjam20fs.rda", interact=fac_inter[[9]])
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")

g_metric_facSparse20<-metrics_gjam(gjam_mod$Rho_sign,fac=fac_inter[[9]], only_env = F)
g_metric_facSparse20_p<-metrics_gjam(gjam_mod$Tau_sign,fac=fac_inter[[9]], only_env = F)
# cat("Success rate ")
# g_metric_facSparse20$success_env
# g_metric_facSparse20$success_fac

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam20fd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_facSparse20$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)




```

### HMSC
```{r hmsc fs20,include=FALSE}
data<-sim_data$FacSparseSp20
hm_mod<-fit_hmsc(data,nsamples=3000, nchains=2,"Load",name="./HMmodels/hm20fs.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=3000, nchains=2,interact = fac_inter[[9]])
h_metric_facSparse20<-metrics_hmsc(hm_mod_R$Rho_sign,fac=fac_inter[[9]],only_env = F)
h_metric_facSparse20_p<-metrics_hmsc(hm_mod_R$Tau_sign,fac=fac_inter[[9]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse20$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))
```




```{r all models fs20, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam20fs.rda"),mfs20,load_object("./HMmodels/hm20fs.rda"))
create_plot_response(sim_data$FacSparseSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )
ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,fac_inter[[9]])

```


```{r all models tau fs20, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,fac_inter[[9]])
```


## Environmental filtering + Competition dense 5 species

### JSDM


```{r model jsdm cmpd5, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd5 <- load_object("model-2019-04-15-16-03-39.rda")

summary(mcmpd5)
#mcmpd5$Rhat
jsdm_conv(mcmpd5)

mcmpd5$mcmc.info[1:7]

j_metric_compDense5<-metrics_jsdm(mcmpd5,comp = comp_inter[[10]],only_env = F)
cat("Success rate ")
j_metric_compDense5$success_env
j_metric_compDense5$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_facSparse20$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_facSparse20$success_fac,3)))

######################################################Prepare data
data<-sim_data$CompDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
#plot_cor_jsdm(mcmpd5,data$Y,comp_inter[[10]])


mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mcmpd5$mean$Rho*(!mcmpd5$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mcmpd5$mean$Rho*(!mcmpd5$overlap0$Rho)) 
 
pred_j<-array(NA,dim=c(data$n,data$J,mcmpd5$mcmc.info$n.samples))
for(i in 1:mcmpd5$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mcmpd5$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```

### Gjam

```{r gjam cmpd5,include=FALSE}
data<-sim_data$CompDenseSp5

#Rho_sign<-fit_gjam(data,10000,1000,"./gjam_models/gjam5cmpd.rda",interact=comp_inter[[10]])

gjam_mod<-load_gjam(data,10000,1000,name="./gjam_models/gjam5cmpd.rda", interact=(-1)*comp_inter[[10]])
#gjfd5<-load_object("./gjam_models/gjam5cmpd.rda")

g_metric_compDense5<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[10]], only_env = F)
g_metric_compDense5_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[10]], only_env = F)

# cat("Success rate ")
# g_metric_compDense5$success_env
# g_metric_compDense5$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_compDense5$success_comp,3)))

#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5cmpd.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 
#Prediction
pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)
pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```


```{r hmsc cmpd5,include=FALSE}
data<-sim_data$CompDenseSp5

hm_mod<-fit_hmsc(data,"Load",nsamples=3000, nchains=2,name="./HMmodels/hm5cmpd.rda" )
#hm_mod<-fit_hmsc(data,"Fit",nsamples=3000, nchains=2 )

hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=3000, nchains=2,interact = (-1)*comp_inter[[10]])

h_metric_compDense5<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[10]],only_env = F)
h_metric_compDense5_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[10]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compDense5$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_compDense5$success_comp,3)))
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```





```{r all models cmpd5, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam5cmpd.rda"),mcmpd5,load_object("./HMmodels/hm5cmpd.rda"))
create_plot_response(sim_data$CompDenseSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )
ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,(-1)*comp_inter[[10]])

```



```{r all models tau fcmpd5, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,(-1)*comp_inter[[10]])
```

## Environmental filtering + Competition dense 10 species

```{r model jsdm cmpd10, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd10 <- load_object("model-2019-04-16-03-39-17.rda")

summary(mcmpd10)
#mcmpd10$Rhat

jsdm_conv(mcmpd10)
mcmpd10$mcmc.info[1:7]

j_metric_compDense10<-metrics_jsdm(mcmpd10,comp = comp_inter[[11]],only_env = F)
# cat("Success rate ")
# j_metric_compDense10$success_env
# j_metric_compDense10$success_comp
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compDense10$success_env,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_compDense10$success_comp,3)))

######################################################Prepare data
data<-sim_data$CompDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
##Correlation
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mcmpd10$mean$Rho*(!mcmpd10$overlap0$Rho))  

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mcmpd10$mean$Rho*(!mcmpd10$overlap0$Rho))  
 ##Prediction
pred_j<-array(NA,dim=c(data$n,data$J,mcmpd10$mcmc.info$n.samples))
for(i in 1:mcmpd10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mcmpd10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```



### Gjam

```{r gjam cmpd10,include=FALSE}
data<-sim_data$CompDenseSp10
#Rho_sign<-fit_gjam(data,5000,500,"./gjam_models/gjam10cmpd.rda",interact=comp_inter[[11]])

gjam_mod<-load_gjam(data,5000,500,name="./gjam_models/gjam10cmpd.rda", interact= (-1)*comp_inter[[11]])
#gjfd5<-load_object("./gjam_models/gjam10cmpd.rda")

g_metric_compDense10<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[11]], only_env = F)
g_metric_compDense10_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[11]], only_env = F)

# cat("Success rate ")
# g_metric_compDense10$success_env
# g_metric_compDense10$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compDense10$success_comp,3)))
###Correlation
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 
#Prediction
pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```


### HMSC

```{r hmsc cmpd10,include=FALSE}
data<-sim_data$CompDenseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples=5000, nchains=2,name="./HMmodels/hm10cmpd.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod,nsamples=5000, nchains=2, interact =  (-1)*comp_inter[[11]])

h_metric_compDense10<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[11]],only_env = F)
h_metric_compDense10_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[11]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compDense10$success_comp,3)))
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```



```{r all models cmpd10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam10cmpd.rda"),mcmpd10,load_object("./HMmodels/hm10cmpd.rda"))

create_plot_response(sim_data$CompDenseSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,(-1)*comp_inter[[11]])

```


```{r all models tau cmpd10, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,(-1)*comp_inter[[11]])

```


## Environmental filtering + Competition dense 20 species

```{r model jsdm cmpd20, echo=FALSE,include=FALSE}
#load("model-2019-04-10-15-13-15.rda")
mcmpd20 <- load_object("model-2019-04-17-14-00-45.rda")

summary(mcmpd20)
#mcmpd10$Rhat

jsdm_conv(mcmpd20)
mcmpd20$mcmc.info[1:7]

j_metric_compDense20<-metrics_jsdm(mcmpd20,comp = comp_inter[[12]],only_env = F)
# cat("Success rate ")
# j_metric_compDense20$success_env
# j_metric_compDense20$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compDense20$success_comp,3)))

######################################################Prepare data
data<-sim_data$CompDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#Tau_n<-to_prec(mfd10$mean$Tau)
#plot_cor_jsdm(mcmpd20,data$Y, (-1)*comp_inter[[12]])



mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =mcmpd20$mean$Rho*(!mcmpd20$overlap0$Rho))  

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =mcmpd20$mean$Rho*(!mcmpd20$overlap0$Rho)) 
 
pred_j<-array(NA,dim=c(data$n,data$J,mcmpd20$mcmc.info$n.samples))
for(i in 1:mcmpd20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(mcmpd20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)


```



### Gjam

```{r gjam cmpd20,include=FALSE}
data<-sim_data$CompDenseSp20

#Rho_sign<-fit_gjam(data,10000,1000,"./gjam_models/gjam20cmpd.rda",interact= (-1)*comp_inter[[12]])

gjam_mod<-load_gjam(data,10000,1000,name="./gjam_models/gjam20cmpd.rda", interact= (-1)*comp_inter[[12]])
#gjfd5<-load_object("./gjam_models/gjam20cmpd.rda")

g_metric_compDense20<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[12]], only_env = F)
g_metric_compDense20_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[12]], only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compDense20$success_comp,3)))


mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```


### HMSC

```{r hmsc cmpd20,include=FALSE}
data<-sim_data$CompDenseSp20

hm_mod<-fit_hmsc(data,"Load",nsamples=5000, nchains=2,name="./HMmodels/hm20cmpd.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=5000, nchains=2,interact =  (-1)*comp_inter[[12]])

h_metric_compDense20<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[12]],only_env = F)
h_metric_compDense20_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[12]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compDense20$success_comp,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))
```


```{r all models cmpd20, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam20cmpd.rda"),mcmpd20,load_object("./HMmodels/hm20cmpd.rda" ))

create_plot_response(sim_data$CompDenseSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,(-1)*comp_inter[[12]])

```






```{r all models tau cmpd20, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,(-1)*comp_inter[[12]])
```



## Environmental filtering + Competition sparse 5 species

```{r model jsdm cmps5, echo=FALSE,include=FALSE}
#load("model-2019-04-17-14-30-01.rda")
cmps5 <- load_object("model-2019-04-17-14-30-01.rda")

summary(cmps5)
jsdm_conv(cmps5)
cmps5$mcmc.info[1:7]

j_metric_compSparse5<-metrics_jsdm(cmps5,comp = comp_inter[[13]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compSparse5$success_comp,3)))



######################################################Prepare data
data<-sim_data$CompSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmps5$mean$Rho*(!cmps5$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmps5$mean$Rho*(!cmps5$overlap0$Rho)) 
####Prediction  
pred_j<-array(NA,dim=c(data$n,data$J,cmps5$mcmc.info$n.samples))
for(i in 1:cmps5$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmps5$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```




### Gjam

```{r gjam cmps5,include=FALSE}
data<-sim_data$CompSparseSp5


#Rho_sign<-fit_gjam(data,5000,2000,"./gjam_models/gjam5cmps.rda",interact= (-1)*comp_inter[[13]])
gjam_mod<-load_gjam(data,5000,2000,name="./gjam_models/gjam5cmps.rda", interact= (-1)*comp_inter[[13]])
#gjfd5<-load_object("./gjam_models/gjam5cmps.rda")

g_metric_compSparse5<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[13]], only_env = F)
g_metric_compSparse5_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[13]], only_env = F)


cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compSparse5$success_comp,3)))


#to check posterior density of s in Sigma 
#gjfd5<-load_object("./gjam_models/gjam5cmps.rda")
#plot(density(gjfd5$chains$sgibbs[,4]))

mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 
###Prediction
pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```


### HMSC

```{r hmsc cmps5,include=FALSE}
data<-sim_data$CompSparseSp5

hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hm5cmps.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[13]])

h_metric_compSparse5<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[13]],only_env = F)
h_metric_compSparse5_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[13]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compSparse5$success_comp,3)))

#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```



```{r all models cmps5, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam5cmps.rda"),cmps5,load_object("./HMmodels/hm5cmps.rda"))

create_plot_response(sim_data$CompSparseSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )
ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,(-1)*comp_inter[[13]])

```


```{r all models tau cmps5, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,(-1)*comp_inter[[13]])

```


## Environmental filtering + Competition sparse 10 species


### JSDM

```{r model jsdm cmps10, echo=FALSE,include=FALSE}
#load("model-2019-04-17-14-30-01.rda")
cmps10 <- load_object("model-2019-04-18-01-55-45.rda")

summary(cmps10)
jsdm_conv(cmps10)
cmps10$mcmc.info[1:7]

j_metric_compSparse10<-metrics_jsdm(cmps10,comp = comp_inter[[14]],only_env = F)
cat("Success rate ")
j_metric_compSparse10$success_env
j_metric_compSparse10$success_comp

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compSparse10$success_comp,3)))


######################################################Prepare data
data<-sim_data$CompSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmps10$mean$Rho*(!cmps10$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmps10$mean$Rho*(!cmps10$overlap0$Rho)) 
###Prediction  
pred_j<-array(NA,dim=c(data$n,data$J,cmps10$mcmc.info$n.samples))
for(i in 1:cmps10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmps10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


### Gjam

```{r gjam cmps10,include=FALSE}
data<-sim_data$CompSparseSp10
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjam10cmps.rda",interact= (-1)*comp_inter[[14]])
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjam10cmps.rda", interact= (-1)*comp_inter[[14]])

g_metric_compSparse10<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[14]], only_env = F)
g_metric_compSparse10_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[14]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compSparse10$success_comp,3)))
###Coorrelation
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 
###Prediction

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```


```{r hmsc cmps10, results=F, include=FALSE}
data<-sim_data$CompSparseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hm10cmps.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[14]])

h_metric_compSparse10<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[14]],only_env = F)
h_metric_compSparse10_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[14]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compSparse10$success_comp,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)

mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))


```




```{r all models cmps10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam10cmps.rda"),cmps10,load_object("./HMmodels/hm10cmps.rda"))

create_plot_response(sim_data$CompSparseSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )
ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,(-1)*comp_inter[[14]])

```



```{r all models tau cmps10, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,(-1)*comp_inter[[14]])

```


## Environmental filtering + Competition sparse 20 species

### JSDM 

```{r model jsdm cmps20, echo=FALSE,include=FALSE}
#load("model-2019-04-17-14-30-01.rda")
cmps20 <- load_object("model-2019-04-19-12-40-30.rda")

summary(cmps20)
jsdm_conv(cmps20)
cmps20$mcmc.info[1:7]

j_metric_compSparse20<-metrics_jsdm(cmps20,comp = comp_inter[[15]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_compSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_compSparse20$success_comp,3)))


######################################################Prepare data
data<-sim_data$CompSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmps20$mean$Rho*(!cmps20$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmps20$mean$Rho*(!cmps20$overlap0$Rho))  
  
pred_j<-array(NA,dim=c(data$n,data$J,cmps20$mcmc.info$n.samples))
for(i in 1:cmps20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmps20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
```

### Gjam

```{r gjam cmps20,include=FALSE}
data<-sim_data$CompSparseSp20
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjam20cmps.rda",interact= (-1)*comp_inter[[15]])
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjam20cmps.rda", interact= (-1)*comp_inter[[15]])

g_metric_compSparse20<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[15]], only_env = F)
g_metric_compSparse20_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[15]], only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_compSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_compSparse20$success_comp,3)))

mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 
###Prediction
pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```


### HMSC

```{r hmsc cmps20,include=FALSE}
data<-sim_data$CompSparseSp20

hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hm20cmps.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[15]])

h_metric_compSparse20<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[15]],only_env = F)
h_metric_compSparse20_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[15]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_compSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_compSparse20$success_comp,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)

mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```


```{r all models cmps20, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam20cmps.rda"),cmps20,load_object("./HMmodels/hm20cmps.rda"))

create_plot_response(sim_data$CompSparseSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc,(-1)*comp_inter[[15]])

```


```{r all models tau cmps20, include=TRUE}

ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc,(-1)*comp_inter[[15]])

```




## Environmental filtering + Competition +Facilitation 5 dense species

### JSDM 

```{r model jsdm cmp_facd5, echo=FALSE,include=FALSE}
cmp_fd5 <- load_object("model-2019-04-19-13-08-47.rda")
summary(cmp_fd5)
jsdm_conv(cmp_fd5)
cmp_fd5$mcmc.info[1:7]
j_metric_FacCompDense5<-metrics_jsdm(cmp_fd5,comp = comp_inter[[16]],fac = fac_inter[[16]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompDense5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompDense5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompDense5$success_fac,3)))

######################################################Prepare data
data<-sim_data$FacCompDenseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
##Cor
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmp_fd5$mean$Rho*(!cmp_fd5$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmp_fd5$mean$Rho*(!cmp_fd5$overlap0$Rho)) 
  
###Prediction
pred_j<-array(NA,dim=c(data$n,data$J,cmp_fd5$mcmc.info$n.samples))
for(i in 1:cmp_fd5$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmp_fd5$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


### Gjam

```{r gjam cmp_facd5,include=FALSE}
data<-sim_data$FacCompDenseSp5
gjam_mod<-load_gjam(data,20000,5000,"./gjam_models/gjam5cmp_facd2.rda",interact= (-1)*comp_inter[[16]]+fac_inter[[16]])

g_metric_FacCompDense5<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[16]], fac=fac_inter[[16]], only_env = F)
g_metric_FacCompDense5_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[16]], fac=fac_inter[[16]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompDense5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompDense5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompDense5$success_fac,3)))

mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```



### HMSC

```{r hmsc cmp_facd5,include=FALSE}
data<-sim_data$FacCompDenseSp5
hm_mod<-fit_hmsc(data,"Load",nsamples=3000, nchains=2,name="./HMmodels/hmcmp_facd5.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=3000, nchains=2,interact =  (-1)*comp_inter[[16]]+ fac_inter[[16]])

h_metric_FacCompDense5<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[16]],fac= fac_inter[[16]],only_env = F)
h_metric_FacCompDense5_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[16]],fac= fac_inter[[16]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompDense5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompDense5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompDense5$success_fac,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```


```{r all models cmp_facd5, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjam5cmp_facd2.rda"),cmp_fd5,load_object("./HMmodels/hmcmp_facd5.rda"))

create_plot_response(sim_data$FacCompDenseSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc, (-1)*comp_inter[[16]]+ fac_inter[[16]])

```


```{r all models tau cmp_facd5, include=TRUE}

ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc, (-1)*comp_inter[[16]]+ fac_inter[[16]])

```



## Environmental filtering + Competition +Facilitation 10 dense species

### JSDM 

```{r model jsdm cmp_facd10, echo=FALSE,include=FALSE}
cmp_fd10 <- load_object("model-2019-04-20-00-37-25.rda")
# 
summary(cmp_fd10)
jsdm_conv(cmp_fd10)
cmp_fd10$mcmc.info[1:7]
# 
j_metric_FacCompDense10<-metrics_jsdm(cmp_fd10,comp = comp_inter[[17]],fac=fac_inter[[17]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompDense10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompDense10$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompDenseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

#plot_cor_jsdm(cmp_fd10,data$Y,(-1)*comp_inter[[17]] +fac_inter[[17]] )

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmp_fd10$mean$Rho*(!cmp_fd10$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmp_fd10$mean$Rho*(!cmp_fd10$overlap0$Rho)) 
  

pred_j<-array(NA,dim=c(data$n,data$J,cmp_fd10$mcmc.info$n.samples))
for(i in 1:cmp_fd10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmp_fd10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
  
```

### Gjam

```{r gjam cmp_facd10,include=FALSE}
data<-sim_data$FacCompDenseSp10
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facd10.rda",interact=  (-1)*comp_inter[[17]]+fac_inter[[17]])
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjamcmp_facd10.rda", interact= (-1)*comp_inter[[17]]+fac_inter[[17]])

g_metric_FacCompDense10<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[17]], fac=fac_inter[[17]], only_env = F)
g_metric_FacCompDense10_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[17]], fac=fac_inter[[17]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompDense10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompDense10$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```


### HMSC

```{r hmsc cmp_facd10,include=FALSE}
  
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facd10.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[17]] + fac_inter[[17]])

h_metric_FacCompDense10<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[17]],fac=fac_inter[[17]], only_env = F)
h_metric_FacCompDense10_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[17]],fac=fac_inter[[17]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompDense10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompDense10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompDense10$success_fac,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)

x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))


```

```{r all models cmp_facd10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjamcmp_facd10.rda"),cmp_fd10,load_object("./HMmodels/hmcmp_facd10.rda"))

create_plot_response(sim_data$FacCompDenseSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc, (-1)*comp_inter[[17]]+ fac_inter[[17]])

```


```{r all models tau cmp_facd10, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc, (-1)*comp_inter[[17]]+ fac_inter[[17]])

```



## Environmental filtering + Competition +Facilitation 20 dense species

### JSDM 

```{r model jsdm cmp_facd20, echo=FALSE,include=FALSE}

cmp_fd20 <- load_object("model-2019-04-21-11-10-34.rda")

summary(cmp_fd20)
jsdm_conv(cmp_fd20)
cmp_fd20$mcmc.info[1:7]
# 
j_metric_FacCompDense20<-metrics_jsdm(cmp_fd20,comp = comp_inter[[18]],fac=fac_inter[[18]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompDense20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompDense20$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompDenseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmp_fd20$mean$Rho*(!cmp_fd20$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmp_fd20$mean$Rho*(!cmp_fd20$overlap0$Rho)) 

pred_j<-array(NA,dim=c(data$n,data$J,cmp_fd20$mcmc.info$n.samples))
for(i in 1:cmp_fd20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmp_fd20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
   
```


### Gjam

```{r gjam cmp_facd20,include=FALSE}
data<-sim_data$FacCompDenseSp20
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facd20.rda",interact=  (-1)*comp_inter[[18]]+fac_inter[[18]])
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjamcmp_facd20.rda", interact= (-1)*comp_inter[[18]]+fac_inter[[18]])

g_metric_FacCompDense20<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[18]], fac=fac_inter[[18]], only_env = F)
g_metric_FacCompDense20_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[18]], fac=fac_inter[[18]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompDense20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompDense20$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)

```


### HMSC

```{r hmsc cmp_facd20,include=FALSE}
data<-sim_data$FacCompDenseSp20
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facd20.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[18]] + fac_inter[[18]])
h_metric_FacCompDense20<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[18]],fac=fac_inter[[18]],only_env = F)
h_metric_FacCompDense20_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[18]],fac=fac_inter[[18]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompDense20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompDense20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompDense20$success_fac,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))



```

```{r all models cmp_facd20, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjamcmp_facd20.rda"),cmp_fd20,load_object("./HMmodels/hmcmp_facd20.rda"))

create_plot_response(sim_data$FacCompDenseSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc, (-1)*comp_inter[[18]]+ fac_inter[[18]])

```

```{r all models tau cmp_facd20, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc, (-1)*comp_inter[[18]]+ fac_inter[[18]])

```



## Environmental filtering + Competition +Facilitation 5 sparse species

### JSDM 

```{r model jsdm cmp_facs5, echo=FALSE,include=FALSE}
cmp_fds5 <- load_object("model-2019-04-21-11-39-52.rda")
# 
summary(cmp_fds5)
jsdm_conv(cmp_fds5)
cmp_fds5$mcmc.info[1:7]
# 
j_metric_FacCompSparse5<-metrics_jsdm(cmp_fds5,comp = comp_inter[[19]],fac=fac_inter[[19]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompSparse5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompSparse5$success_comp,3)))
# ######################################################Prepare data
data<-sim_data$FacCompSparseSp5
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
#####Correlation
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmp_fds5$mean$Rho*(!cmp_fds5$overlap0$Rho)) 
mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmp_fds5$mean$Rho*(!cmp_fds5$overlap0$Rho))  
##Prediction
pred_j<-array(NA,dim=c(data$n,data$J,cmp_fds5$mcmc.info$n.samples))
for(i in 1:cmp_fds5$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmp_fds5$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
    
```

### Gjam

```{r gjam cmp_facs5,include=FALSE}
data<-sim_data$FacCompSparseSp5
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facs5.rda",interact= (-1)*comp_inter[[19]]+ fac_inter[[19]] )
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjamcmp_facs5.rda", interact=  (-1)*comp_inter[[19]]+ fac_inter[[19]])
g_metric_FacCompSparse5<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[15]], only_env = F)
g_metric_FacCompSparse5_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[15]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse5$success_comp,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse5$success_comp,3)))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```


### HMSC

```{r hmsc cmp_facs5,include=FALSE}
data<-sim_data$FacCompSparseSp5
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facs5.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[19]]+ fac_inter[[19]])
 
h_metric_FacCompSparse5<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[19]],fac= fac_inter[[19]] ,only_env = F)
h_metric_FacCompSparse5_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[19]],fac= fac_inter[[19]] ,only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompSparse5$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompSparse5$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompSparse5$success_fac,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)


x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}
pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))



```


```{r all models cmp_facs5, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjamcmp_facs5.rda"),cmp_fds5,load_object("./HMmodels/hmcmp_facs5.rda" ))

create_plot_response(sim_data$FacCompSparseSp5, nsp=5,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc, (-1)*comp_inter[[19]]+ fac_inter[[19]])

```


```{r all models tau cmp_facs5, include=TRUE}
ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc, (-1)*comp_inter[[19]]+ fac_inter[[19]])

```



## Environmental filtering + Competition +Facilitation 10 sparse species

### JSDM 

```{r model jsdm cmp_facs10, echo=FALSE,include=FALSE}
cmp_fds10 <- load_object("model-2019-04-21-22-58-58.rda")
#
summary(cmp_fds10)
jsdm_conv(cmp_fds10)
cmp_fds10$mcmc.info[1:7]
# 
j_metric_FacCompSparse10<-metrics_jsdm(cmp_fds10,comp = comp_inter[[20]],fac=fac_inter[[20]],only_env = F)
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompSparse10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompSparse10$success_comp,3)))
# ######################################################Prepare data
data<-sim_data$FacCompSparseSp10
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)
########Correlation
mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmp_fds10$mean$Rho*(!cmp_fds10$overlap0$Rho)) 

mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmp_fds10$mean$Rho*(!cmp_fds10$overlap0$Rho)) 
########Prediction
pred_j<-array(NA,dim=c(data$n,data$J,cmp_fds10$mcmc.info$n.samples))
for(i in 1:cmp_fds10$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmp_fds10$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)


pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)

```


### Gjam

```{r gjam cmp_facs10,include=FALSE}
data<-sim_data$FacCompSparseSp10
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facs10.rda",interact= (-1)*comp_inter[[20]] +fac_inter[[20]])
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjamcmp_facs10.rda", interact=  (-1)*comp_inter[[20]] +fac_inter[[20]])

g_metric_FacCompSparse10<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[20]],fac=fac_inter[[20]], only_env = F)
g_metric_FacCompSparse10_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[20]],fac=fac_inter[[20]], only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompSparse10$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 

pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```


### HMSC

```{r hmsc cmp_facs10,include=FALSE}
data<-sim_data$FacCompSparseSp10
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facs10.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[20]] +fac_inter[[20]])

h_metric_FacCompSparse10<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[20]],fac=fac_inter[[20]],only_env = F)
h_metric_FacCompSparse10_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[20]],fac=fac_inter[[20]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompSparse10$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompSparse10$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompSparse10$success_fac,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)
#Prediction
x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}

pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```


```{r all models cmp_facs10, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjamcmp_facs10.rda"),cmp_fds10,load_object("./HMmodels/hmcmp_facs10.rda"))

create_plot_response(sim_data$FacCompSparseSp10, nsp=10,pred_gjam, pred_jsdm,pred_hmsc )

ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc, (-1)*comp_inter[[20]]+ fac_inter[[20]])

```


```{r all models tau cmp_facs10, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc, (-1)*comp_inter[[20]]+ fac_inter[[20]])

```



## Environmental filtering + Competition +Facilitation 20 sparse species

### JSDM 

```{r model jsdm cmp_facs20, echo=FALSE,include=FALSE}
cmp_fds20 <- load_object("model-2019-04-23-09-42-18.rda")

summary(cmp_fds20)
jsdm_conv(cmp_fds20)
cmp_fds20$mcmc.info[1:7]
# 
j_metric_FacCompSparse20<-metrics_jsdm(cmp_fds20,comp = comp_inter[[21]],fac=fac_inter[[21]],only_env = F)
# # cat("Success rate ")
# # j_metric_compSparse10$success_env
# # j_metric_compSparse10$success_comp
# # 
cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(j_metric_FacCompSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(j_metric_FacCompSparse20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(j_metric_FacCompSparse20$success_comp,3)))
# 
# 
# ######################################################Prepare data
data<-sim_data$FacCompSparseSp20
data <- list(
  Y = subset(data, select = -env),
  X = cbind(1, scale(poly(data$env, 2))),
  covx = cov(cbind(1, scale(poly(data$env, 2)))),
  K = 3,
  J = ncol(data) - 1,
  n = nrow(data),
  I = diag(ncol(data) - 1),
  df = ncol(data)
)

#plot_cor_jsdm(cmp_fds20,data$Y,(-1)*comp_inter[[21]] +fac_inter[[21]] )

mod_list_Rho<-list()
mod_list_Rho<-list(jsdm =cmp_fds20$mean$Rho*(!cmp_fds20$overlap0$Rho)) 
 
mod_list_Tau<-list()
mod_list_Tau<-list(jsdm =cmp_fds20$mean$Rho*(!cmp_fds20$overlap0$Rho)) 

pred_j<-array(NA,dim=c(data$n,data$J,cmp_fds20$mcmc.info$n.samples))
for(i in 1:cmp_fds20$mcmc.info$n.samples){
  
  pred_j[,,i]<-pnorm(data$X%*%t(cmp_fds20$sims.list$B[i,,]))
  
}

pred_j_mean <- apply(pred_j, 1:2, mean)
pred_j_05 <- apply(pred_j, 1:2, quantile,0.05)
pred_j_95 <- apply(pred_j, 1:2, quantile,0.95)

pred_jsdm<-list(pred_j_mean=pred_j_mean,pred_j_05=pred_j_05,pred_j_95=pred_j_95)
```

### Gjam

```{r gjam cmp_facs20,results=FALSE, include=FALSE}
data<-sim_data$FacCompSparseSp20
#Rho_sign<-fit_gjam(data,2000,500,"./gjam_models/gjamcmp_facs20.rda",interact= (-1)*comp_inter[[21]]+fac_inter[[21]])
gjam_mod<-load_gjam(data,2000,500,name="./gjam_models/gjamcmp_facs20.rda", interact= (-1)*comp_inter[[21]]+fac_inter[[21]])
g_metric_FacCompSparse20<-metrics_gjam(gjam_mod$Rho_sign,comp=comp_inter[[21]], fac=fac_inter[[21]],only_env = F)
g_metric_FacCompSparse20_p<-metrics_gjam(gjam_mod$Tau_sign,comp=comp_inter[[21]], fac=fac_inter[[21]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(g_metric_FacCompSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(g_metric_FacCompSparse20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(g_metric_FacCompSparse20$success_fac,3)))
mod_list_Rho<-list.append(mod_list_Rho, gjam=gjam_mod$Rho_sign) 
mod_list_Tau<-list.append(mod_list_Tau, gjam=gjam_mod$Tau_sign) 


pred_gj_mean <-apply(gjam_mod$predict, 1:2,mean)
pred_gj_05 <- apply(gjam_mod$predict, 1:2,quantile,0.05)
pred_gj_95 <- apply(gjam_mod$predict, 1:2,quantile,0.95)

pred_gjam<- list(pred_gj_mean=pred_gj_mean,pred_gj_05=pred_gj_05,pred_gj_95=pred_gj_95)
```

### HMSC

```{r hmsc cmp_facs20,results=FALSE, include=FALSE}
data<-sim_data$FacCompSparseSp20
hm_mod<-fit_hmsc(data,"Load",nsamples=2000, nchains=2,name="./HMmodels/hmcmp_facs20.rda" )
hm_conv(hm_mod)
hm_mod_R<-hm_inter(hm_mod, nsamples=2000, nchains=2,interact =  (-1)*comp_inter[[21]] +fac_inter[[21]])
h_metric_FacCompSparse20<-metrics_hmsc(hm_mod_R$Rho_sign,comp=comp_inter[[21]],fac=fac_inter[[21]],only_env = F)
h_metric_FacCompSparse20_p<-metrics_hmsc(hm_mod_R$Tau_sign,comp=comp_inter[[21]],fac=fac_inter[[21]],only_env = F)

cat("\n")
cat(sprintf("Success rate for non-interacting: %s\n", round(h_metric_FacCompSparse20$success_env,3)))
cat(sprintf("Success rate for competition: %s\n", round(h_metric_FacCompSparse20$success_comp,3)))
cat(sprintf("Success rate for facilitation: %s\n", round(h_metric_FacCompSparse20$success_fac,3)))
#mod_list<-list.append(mod_list,hmsc=Rho_sign)
mod_list_Rho<-list.append(mod_list_Rho,hmsc=hm_mod_R$Rho_sign)
mod_list_Tau<-list.append(mod_list_Tau,hmsc=hm_mod_R$Tau_sign)
####Prediction
x = cbind(1, scale(poly(data$env, 2)))
pred_hm<-array(NA,dim=c(hm_mod$ny,hm_mod$ns,2*hm_mod$samples)) #2 is nchains
for(k in 1:(2*hm_mod$samples)){
    if(k<=hm_mod$samples){pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[1]][[k]]$Beta)
    }else {pred_hm[,,k] <- pnorm(x%*%hm_mod$postList[[2]][[k-hm_mod$samples]]$Beta)}

}
pred_hmsc<- list(pred_hm_mean=apply(pred_hm, c(1,2), mean),
                 pred_hm_05=apply(pred_hm, c(1,2), quantile,0.05),
                 pred_hm_95=apply(pred_hm, c(1,2), quantile,0.95))

```

```{r all models cmp_facs20, include=TRUE}
create_beta_plot(load_object("./gjam_models/gjamcmp_facs20.rda"),cmp_fds20,load_object("./HMmodels/hmcmp_facs20.rda"))

create_plot_response(sim_data$FacCompSparseSp20, nsp=20,pred_gjam, pred_jsdm,pred_hmsc )


ALL3(mod_list_Rho$jsdm,mod_list_Rho$gjam,mod_list_Rho$hmsc, (-1)*comp_inter[[21]]+ fac_inter[[21]])

```



```{r all models tau cmp_facs20, include=TRUE}


ALL4(mod_list_Tau$jsdm,mod_list_Tau$gjam,mod_list_Tau$hmsc, (-1)*comp_inter[[21]]+ fac_inter[[21]])

```


## Graph from paper

```{r combined models, echo=FALSE, warning=FALSE,include=TRUE}

 models<-list(EnvEvenSp5=me5,EnvEvenSp10=me10, EnvEvenSp20=me20,FacDenseSp5 =mfd5, FacDenseSp10=mfd10, FacDenseSp20=mfd20,
              FacSparseSp5 =mfs5, FacSparseSp10=mfs10, FacSparseSp20=mfs20, CompDenseSp5=mcmpd5,CompDenseSp10=mcmpd10,CompDenseSp20=mcmpd20,
              CompSparseSp5=cmps5,      CompSparseSp10 =cmps10,   CompSparseSp20 =cmps20,   FacCompDenseSp5=cmp_fd5,FacCompDenseSp10=cmp_fd10,       
              FacCompDenseSp20 =cmp_fd20,FacCompSparseSp5=cmp_fds5,  FacCompSparseSp10=cmp_fds10, FacCompSparseSp20=cmp_fds20)



 mean_cor<-function(mod){
   mean_correlations <- do.call(
   rbind,
   lapply(
     seq_along(mod),
     function(i) {
       x <- models[[i]]
       nm <- strsplit(
         names(models)[[i]], "(?<=[a-z])(?=[A-Z])", perl = TRUE
       )[[1]]
       nsp <- ncol(x$mean$Rho)
       ut <- upper.tri(x$mean$Rho)
       sp <- arrayInd(which(ut), c(nsp, nsp))
       ans <- data.frame(
         model = i,
         sp1 = sp[, 1],
         sp2 = sp[, 2],
         rho = c(prob_cooccur_es(x$model$cluster1$data()$Y)[ut], x$mean$Rho[ut]),
         rho_type = rep(c("Effect-Size", "Residual"), each = sum(ut)),
         sgn = sign(x$mean$Rho)[ut],
         significant = x$overlap$Rho[ut],
         #cint = simulation_parameters$comp_inter[[i]][ut],
         #fint = simulation_parameters$fac_inter[[i]][ut],
         cint = comp_inter[[i]][ut],
         fint = fac_inter[[i]][ut],
         density = tail(nm, 2)[1],
         type = paste0(head(nm, -2), collapse = ""),
         nsp = nsp,
         stringsAsFactors = FALSE
       )
       ans$cint[is.na(ans$cint)] <- 0
       ans$fint[is.na(ans$fint)] <- 0
       ans$density[ans$density == "Even"] <- "None"
       ans$density <- factor(ans$density, c("None", "Sparse", "Dense"))
       ans$type[ans$type == "Env"] <- "Environmental\nFiltering Only"
       ans$type[ans$type == "Fac"] <- "Facilitation"
       ans$type[ans$type == "Comp"] <- "Competition"
       ans$type[ans$type == "FacComp"] <- "Facililation +\nCompetition"
       ans$type <- factor(
         ans$type,
         c(
           "Environmental\nFiltering Only", "Facilitation", "Competition",
           "Facililation +\nCompetition"
         )
       )
       ans$interaction <- "None"
       ans$interaction <- ifelse(ans$cint, "Competition", ans$interaction)
       ans$interaction <- ifelse(ans$fint, "Facilitation", ans$interaction)
       ans$status <- ifelse(
         ans$significant,
         ifelse(ans$sgn * -ans$cint == 1 | ans$sgn * ans$fint == 1, "TP", "FP"),
         ifelse(ans$cint == 0 & ans$fint == 0, "TN", "FN")
       )
       ans$interaction <- factor(
         ans$interaction, c("None", "Facilitation", "Competition")
       )
       ans
     }
   )
 )
  return(mean_correlations)
 }

 mean_correlations <- mean_cor(models)
 x <- subset(mean_correlations, type != "Environmental\nFiltering Only")
 acc <- by(x, x$model, function(x) sum(x$status == "TP" | x$status == "TN") / nrow(x))

 #' Plot correlation parameter means
 #+ plot-correlations
 ggplot(mean_correlations) +
   aes(factor(nsp), rho, fill = interaction) +
   geom_hline(yintercept = 0) +
   geom_boxplot(
     outlier.size = .2, size = .1, position = position_dodge(preserve = "single")
   ) +
   scale_fill_manual(values = c("grey", "blue", "red")) +
   facet_grid(type ~ rho_type + density, switch = "y") +
   xlab("Number of species") +
   ylab("Correlation") +
   theme_bw() +
   theme(legend.position = "top")


 mean_correlations <- mean_cor(models)
 x <- subset(mean_correlations, type != "Environmental\nFiltering Only")
 acc <- by(x, x$model, function(x) sum(x$status == "TP" | x$status == "TN") / nrow(x))

 mean_correlations2<- subset(mean_correlations, interaction != "None")
 #' Plot correlation parameter means
 #+ plot-correlations
 ggplot(mean_correlations2) +
   aes(factor(nsp), rho, fill = interaction) +
   geom_hline(yintercept = 0) +
   geom_boxplot(
     outlier.size = .2, size = .1, position = position_dodge(preserve = "single")
   ) +
   scale_fill_manual(values = c( "blue", "red")) +
   facet_grid(type ~ rho_type + density, switch = "y") +
   xlab("Number of species") +
   ylab("Correlation") +
   theme_bw() +
   theme(legend.position = "top")

 
 
all<-list("j_metric_e5"=j_metric_e5,"g_metric_e5"=g_metric_e5,"h_metric_e5"=h_metric_e5,
          "j_metric_e10"=j_metric_e10,"g_metric_e10"=g_metric_e10,"h_metric_e10"=h_metric_e10,
          "j_metric_e20"=j_metric_e20,"g_metric_e20"=g_metric_e20,"h_metric_e20"=h_metric_e20,
          "h_metric_facDense5"=h_metric_facDense5,"g_metric_facDense5"=g_metric_facDense5,"j_metric_facDense5"=j_metric_facDense5,
          "h_metric_facDense10"=h_metric_facDense10,"g_metric_facDense10"=g_metric_facDense10,"j_metric_facDense10"=j_metric_facDense10,
          "h_metric_facDense20"=h_metric_facDense20,"g_metric_facDense20"=g_metric_facDense20,"j_metric_facDense20"=j_metric_facDense20,
          "h_metric_facSparse5"=h_metric_facSparse5,"g_metric_facSparse5"=g_metric_facSparse5,"j_metric_facSparse5"=j_metric_facSparse5,
          "h_metric_facSparse10"=h_metric_facSparse10,"g_metric_facSparse10"=g_metric_facSparse10,"j_metric_facSparse10"=j_metric_facSparse10,
          "h_metric_facSparse20"=h_metric_facSparse20,"g_metric_facSparse20"=g_metric_facSparse20,"j_metric_facSparse10"=j_metric_facSparse20,
          "h_metric_compDense5"=h_metric_compDense5,"g_metric_compDense5"=g_metric_compDense5,"j_metric_compDense5"=j_metric_compDense5,
          "h_metric_compDense10"=h_metric_compDense10,"g_metric_compDense10"=g_metric_compDense10,"j_metric_compDense10"=j_metric_compDense10,
          "h_metric_compDense20"=h_metric_compDense20,"g_metric_compDense20"=g_metric_compDense20,"j_metric_compDense20"=j_metric_compDense20,
          "h_metric_compSparse5"=h_metric_compSparse5,"g_metric_compSparse5"=g_metric_compSparse5,"j_metric_compSparse5"=j_metric_compSparse5,
          "h_metric_compSparse10"=h_metric_compSparse10,"g_metric_compSparse10"=g_metric_compSparse10,"j_metric_compSparse10"=j_metric_compSparse10,
          "h_metric_compSparse20"=h_metric_compSparse20,"g_metric_compSparse20"=g_metric_compSparse20,"j_metric_compSparse20"=j_metric_compSparse20,
          "g_metric_faccompSparseSp5"= g_metric_FacCompSparse5,"h_metric_faccompSparseSp5"=h_metric_FacCompSparse5, "j_metric_faccompSparseSp5"=j_metric_FacCompSparse5,
          "g_metric_faccompSparseSp10"= g_metric_FacCompSparse10,"h_metric_faccompSparseSp10"=h_metric_FacCompSparse10, "j_metric_faccompSparseSp10"=j_metric_FacCompSparse10,
          "g_metric_faccompSparseSp20"= g_metric_FacCompSparse20,"h_metric_faccompSparseSp20"=h_metric_FacCompSparse20, "j_metric_faccompSparseSp20"=j_metric_FacCompSparse20,
          "g_metric_faccompDenseSp5"= g_metric_FacCompDense5,"h_metric_faccompDenseSp5"=h_metric_FacCompDense5, "j_metric_faccompDenseSp5"=j_metric_FacCompDense5,
          "g_metric_faccompDenseSp10"= g_metric_FacCompDense10,"h_metric_faccompDenseSp10"=h_metric_FacCompDense10, "j_metric_faccompDenseSp10"=j_metric_FacCompDense10,
          "g_metric_faccompDenseSp20"= g_metric_FacCompDense20,"h_metric_faccompDenseSp20"=h_metric_FacCompDense20, "j_metric_faccompDenseSp20"=j_metric_FacCompDense20
        )
          
table<-as.data.frame(matrix(NA,nrow=63, ncol=8,dimnames=list(NULL,c("success_env","success_comp","success_fac","n_sp","Facilitation","Competition","sparsity","model"))))
                                                  
for(i in 1:length(names(all))){
  if(!is.null(all[[i]]$success_env)) table[i,"success_env"]<-all[[i]]$success_env
  if(!is.null(all[[i]]$success_comp)) table[i,"success_comp"]<-all[[i]]$success_comp
  if(!is.null(all[[i]]$success_fac)) table[i,"success_fac"]<-all[[i]]$success_fac
  
  if(length(grep("5",names(all)[i]))>0) table[i,"n_sp"]<-5
  if(length(grep("10",names(all)[i]))>0) table[i,"n_sp"]<-10
  if(length(grep("20",names(all)[i]))>0) table[i,"n_sp"]<-20
  
  if(length(grep("fac",names(all)[i]))>0){ table[i,"Facilitation"]<-"facilitation"}#else{table[i,"facilition"]<-NULL}
  if(length(grep("comp",names(all)[i]))>0){ table[i,"Competition"]<-"competition"}#else{table[i,"competition"]<-NULL}
  #if(!(length(grep("comp",names(all)[i]))>0) | length(grep("fac",names(all)[i]))>0) {table[i,"Comp_fac"]<-"comp_fac"}else{table[i,"Comp_fac"]<-NULL}
  
  
  if(length(grep("Dense",names(all)[i]))>0){ table[i,"sparsity"]<-"dense"}else{table[i,"sparsity"]<-"sparse"}
  
  if(length(grep("j_",names(all)[i]))>0) table[i,"model"]<-"Jsdm"
  if(length(grep("g_",names(all)[i]))>0) table[i,"model"]<-"Gjam"
  if(length(grep("h_",names(all)[i]))>0) table[i,"model"]<-"Hmsc"
  
}

table_comp<-table[which(!is.na(table$success_comp)),]
table_fac<-table[which(!is.na(table$success_fac)),]

tc<-cbind(table_comp$success_comp,table_comp$model,rep("All",nrow(table_comp)),rep("Int",nrow(table_comp)))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==5),"success_comp"],table_comp[which(table_comp$n_sp==5),"model"],rep("5",sum(table_comp$n_sp==5)),rep("Int",sum(table_comp$n_sp==5))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==10),"success_comp"],table_comp[which(table_comp$n_sp==10),"model"],rep("10",sum(table_comp$n_sp==10)),rep("Int",sum(table_comp$n_sp==10))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==20),"success_comp"],table_comp[which(table_comp$n_sp==20),"model"],rep("20",sum(table_comp$n_sp==20)),rep("Int",sum(table_comp$n_sp==20))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$sparsity=="dense"),"success_comp"],table_comp[which(table_comp$sparsity=="dense"),"model"],rep("dense",sum(table_comp$sparsity=="dense")),rep("Int",sum(table_comp$sparsity=="dense"))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$sparsity=="sparse"),"success_comp"],table_comp[which(table_comp$sparsity=="sparse"),"model"],rep("sparse",sum(table_comp$sparsity=="sparse")),rep("Int",sum(table_comp$sparsity=="sparse"))))
tc<-rbind(tc,cbind(table_comp$success_env,table_comp$model,rep("All_env",nrow(table_comp)),rep("Env",nrow(table_comp))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==5),"success_env"],table_comp[which(table_comp$n_sp==5),"model"],rep("5_env",sum(table_comp$n_sp==5)),rep("Env",sum(table_comp$n_sp==5))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==10),"success_env"],table_comp[which(table_comp$n_sp==10),"model"],rep("10_env",sum(table_comp$n_sp==10)),rep("Env",sum(table_comp$n_sp==10))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==20),"success_env"],table_comp[which(table_comp$n_sp==20),"model"],rep("20_env",sum(table_comp$n_sp==20)),rep("Env",sum(table_comp$n_sp==20))))

tc<-data.frame("success"=as.numeric(tc[,1]),"model"=tc[,2],"fac"=tc[,3],"int"=rep("Competition",nrow(tc)),"col"=tc[,4])



tf<-cbind(table_fac$success_fac,table_fac$model,rep("All",nrow(table_fac)),rep("Int",nrow(table_fac)))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==5),"success_fac"],table_fac[which(table_fac$n_sp==5),"model"],rep("5",sum(table_fac$n_sp==5)),rep("Int",sum(table_fac$n_sp==5))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==10),"success_fac"],table_fac[which(table_fac$n_sp==10),"model"],rep("10",sum(table_fac$n_sp==10)),rep("Int",sum(table_fac$n_sp==10))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==20),"success_fac"],table_fac[which(table_fac$n_sp==20),"model"],rep("20",sum(table_fac$n_sp==20)),rep("Int",sum(table_fac$n_sp==20))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$sparsity=="dense"),"success_fac"],table_fac[which(table_fac$sparsity=="dense"),"model"],rep("dense",sum(table_fac$sparsity=="dense")),rep("Int",sum(table_fac$sparsity=="dense"))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$sparsity=="sparse"),"success_fac"],table_fac[which(table_fac$sparsity=="sparse"),"model"],rep("sparse",sum(table_fac$sparsity=="sparse")),rep("Int",sum(table_fac$sparsity=="sparse"))))
tf<-rbind(tf,cbind(table_fac$success_env,table_fac$model,rep("All_env",nrow(table_fac)),rep("Env",nrow(table_fac))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==5),"success_env"],table_fac[which(table_fac$n_sp==5),"model"],rep("5_env",sum(table_fac$n_sp==5)),rep("Env",sum(table_fac$n_sp==5))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==10),"success_env"],table_fac[which(table_fac$n_sp==10),"model"],rep("10_env",sum(table_fac$n_sp==10)),rep("Env",sum(table_fac$n_sp==10))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==20),"success_env"],table_fac[which(table_fac$n_sp==20),"model"],rep("20_env",sum(table_fac$n_sp==20)),rep("Env",sum(table_fac$n_sp==20))))

tf<-data.frame("success"=as.numeric(tf[,1]),"model"=tf[,2],"fac"=tf[,3],"int"=rep("Facilitation",nrow(tf)),"col"=tf[,4])

table<-rbind(tf,tc)

p<-ggplot(data=table)+geom_boxplot(aes(y=as.numeric(success),x=as.factor(fac),fill=as.factor(col)))+
  scale_x_discrete(name="Parameters", breaks=c("All","5","10","20","dense","sparse","All_env","5_env","10_env","20_env"),
                   labels=c("All","5","10","20","dense","sparse","All","5","10","20"),limits=c("All","5","10","20","dense","sparse","All_env","5_env","10_env","20_env"))+
  scale_y_continuous(name="% success")+
  scale_fill_discrete(name = "Success in retrieving_", labels = c("Sensibility (non int.)","Sensitivity (int."))+theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position="top")+
  facet_wrap( ~ int+model, scales="free")+ggtitle("Pairs indentification by correlation")
p


```

```{r inter_partial correlations, echo=FALSE}

all_part<-list("g_metric_e5"=g_metric_e5_p,"h_metric_e5"=h_metric_e5_p,
          "g_metric_e10"=g_metric_e10_p,"h_metric_e10"=h_metric_e10_p,
          "g_metric_e20"=g_metric_e20_p,"h_metric_e20"=h_metric_e20_p,
          "h_metric_facDense5"=h_metric_facDense5_p,"g_metric_facDense5"=g_metric_facDense5_p,
          "h_metric_facDense10"=h_metric_facDense10_p,"g_metric_facDense10"=g_metric_facDense10_p,
          "h_metric_facDense20"=h_metric_facDense20_p,"g_metric_facDense20"=g_metric_facDense20_p,
          "h_metric_facSparse5"=h_metric_facSparse5_p,"g_metric_facSparse5"=g_metric_facSparse5_p,
          "h_metric_facSparse10"=h_metric_facSparse10_p,"g_metric_facSparse10"=g_metric_facSparse10_p,
          "h_metric_facSparse20"=h_metric_facSparse20_p,"g_metric_facSparse20"=g_metric_facSparse20_p,
          "h_metric_compDense5"=h_metric_compDense5_p,"g_metric_compDense5"=g_metric_compDense5_p,
          "h_metric_compDense10"=h_metric_compDense10_p,"g_metric_compDense10"=g_metric_compDense10_p,
          "h_metric_compDense20"=h_metric_compDense20_p,"g_metric_compDense20"=g_metric_compDense20_p,
          "h_metric_compSparse5"=h_metric_compSparse5_p,"g_metric_compSparse5"=g_metric_compSparse5_p,
          "h_metric_compSparse10"=h_metric_compSparse10_p,"g_metric_compSparse10"=g_metric_compSparse10_p,
          "h_metric_compSparse20"=h_metric_compSparse20_p,"g_metric_compSparse20"=g_metric_compSparse20_p,
          "g_metric_faccompSparseSp5"= g_metric_FacCompSparse5_p,"h_metric_faccompSparseSp5"=h_metric_FacCompSparse5_p, 
          "g_metric_faccompSparseSp10"= g_metric_FacCompSparse10_p,"h_metric_faccompSparseSp10"=h_metric_FacCompSparse10_p,
          "g_metric_faccompSparseSp20"= g_metric_FacCompSparse20_p,"h_metric_faccompSparseSp20"=h_metric_FacCompSparse20_p,
          "g_metric_faccompDenseSp5"= g_metric_FacCompDense5_p,"h_metric_faccompDenseSp5"=h_metric_FacCompDense5_p, 
          "g_metric_faccompDenseSp10"= g_metric_FacCompDense10_p,"h_metric_faccompDenseSp10"=h_metric_FacCompDense10_p,
          "g_metric_faccompDenseSp20"= g_metric_FacCompDense20_p,"h_metric_faccompDenseSp20"=h_metric_FacCompDense20_p
        )
          
table<-as.data.frame(matrix(NA,nrow=63, ncol=8,dimnames=list(NULL,c("success_env","success_comp","success_fac","n_sp","Facilitation","Competition","sparsity","model"))))
                                                  
for(i in 1:length(names(all_part))){
  if(!is.null(all_part[[i]]$success_env)) table[i,"success_env"]<-all_part[[i]]$success_env
  if(!is.null(all_part[[i]]$success_comp)) table[i,"success_comp"]<-all_part[[i]]$success_comp
  if(!is.null(all_part[[i]]$success_fac)) table[i,"success_fac"]<-all_part[[i]]$success_fac
  
  if(length(grep("5",names(all_part)[i]))>0) table[i,"n_sp"]<-5
  if(length(grep("10",names(all_part)[i]))>0) table[i,"n_sp"]<-10
  if(length(grep("20",names(all_part)[i]))>0) table[i,"n_sp"]<-20
  
  if(length(grep("fac",names(all_part)[i]))>0){ table[i,"Facilitation"]<-"facilitation"}#else{table[i,"facilition"]<-NULL}
  if(length(grep("comp",names(all_part)[i]))>0){ table[i,"Competition"]<-"competition"}#else{table[i,"competition"]<-NULL}
  #if(!(length(grep("comp",names(all_part)[i]))>0) | length(grep("fac",names(all_part)[i]))>0) {table[i,"Comp_fac"]<-"comp_fac"}else{table[i,"Comp_fac"]<-NULL}
  
  
  if(length(grep("Dense",names(all_part)[i]))>0){ table[i,"sparsity"]<-"dense"}else{table[i,"sparsity"]<-"sparse"}
  
  if(length(grep("j_",names(all_part)[i]))>0) table[i,"model"]<-"Jsdm"
  if(length(grep("g_",names(all_part)[i]))>0) table[i,"model"]<-"Gjam"
  if(length(grep("h_",names(all_part)[i]))>0) table[i,"model"]<-"Hmsc"
  
}

table_comp<-table[which(!is.na(table$success_comp)),]
table_fac<-table[which(!is.na(table$success_fac)),]

tc<-cbind(table_comp$success_comp,table_comp$model,rep("All",nrow(table_comp)),rep("Int",nrow(table_comp)))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==5),"success_comp"],table_comp[which(table_comp$n_sp==5),"model"],rep("5",sum(table_comp$n_sp==5)),rep("Int",sum(table_comp$n_sp==5))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==10),"success_comp"],table_comp[which(table_comp$n_sp==10),"model"],rep("10",sum(table_comp$n_sp==10)),rep("Int",sum(table_comp$n_sp==10))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==20),"success_comp"],table_comp[which(table_comp$n_sp==20),"model"],rep("20",sum(table_comp$n_sp==20)),rep("Int",sum(table_comp$n_sp==20))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$sparsity=="dense"),"success_comp"],table_comp[which(table_comp$sparsity=="dense"),"model"],rep("dense",sum(table_comp$sparsity=="dense")),rep("Int",sum(table_comp$sparsity=="dense"))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$sparsity=="sparse"),"success_comp"],table_comp[which(table_comp$sparsity=="sparse"),"model"],rep("sparse",sum(table_comp$sparsity=="sparse")),rep("Int",sum(table_comp$sparsity=="sparse"))))
tc<-rbind(tc,cbind(table_comp$success_env,table_comp$model,rep("All_env",nrow(table_comp)),rep("Env",nrow(table_comp))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==5),"success_env"],table_comp[which(table_comp$n_sp==5),"model"],rep("5_env",sum(table_comp$n_sp==5)),rep("Env",sum(table_comp$n_sp==5))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==10),"success_env"],table_comp[which(table_comp$n_sp==10),"model"],rep("10_env",sum(table_comp$n_sp==10)),rep("Env",sum(table_comp$n_sp==10))))
tc<-rbind(tc,cbind(table_comp[which(table_comp$n_sp==20),"success_env"],table_comp[which(table_comp$n_sp==20),"model"],rep("20_env",sum(table_comp$n_sp==20)),rep("Env",sum(table_comp$n_sp==20))))

tc<-data.frame("success"=as.numeric(tc[,1]),"model"=tc[,2],"fac"=tc[,3],"int"=rep("Competition",nrow(tc)),"col"=tc[,4])



tf<-cbind(table_fac$success_fac,table_fac$model,rep("All",nrow(table_fac)),rep("Int",nrow(table_fac)))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==5),"success_fac"],table_fac[which(table_fac$n_sp==5),"model"],rep("5",sum(table_fac$n_sp==5)),rep("Int",sum(table_fac$n_sp==5))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==10),"success_fac"],table_fac[which(table_fac$n_sp==10),"model"],rep("10",sum(table_fac$n_sp==10)),rep("Int",sum(table_fac$n_sp==10))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==20),"success_fac"],table_fac[which(table_fac$n_sp==20),"model"],rep("20",sum(table_fac$n_sp==20)),rep("Int",sum(table_fac$n_sp==20))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$sparsity=="dense"),"success_fac"],table_fac[which(table_fac$sparsity=="dense"),"model"],rep("dense",sum(table_fac$sparsity=="dense")),rep("Int",sum(table_fac$sparsity=="dense"))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$sparsity=="sparse"),"success_fac"],table_fac[which(table_fac$sparsity=="sparse"),"model"],rep("sparse",sum(table_fac$sparsity=="sparse")),rep("Int",sum(table_fac$sparsity=="sparse"))))
tf<-rbind(tf,cbind(table_fac$success_env,table_fac$model,rep("All_env",nrow(table_fac)),rep("Env",nrow(table_fac))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==5),"success_env"],table_fac[which(table_fac$n_sp==5),"model"],rep("5_env",sum(table_fac$n_sp==5)),rep("Env",sum(table_fac$n_sp==5))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==10),"success_env"],table_fac[which(table_fac$n_sp==10),"model"],rep("10_env",sum(table_fac$n_sp==10)),rep("Env",sum(table_fac$n_sp==10))))
tf<-rbind(tf,cbind(table_fac[which(table_fac$n_sp==20),"success_env"],table_fac[which(table_fac$n_sp==20),"model"],rep("20_env",sum(table_fac$n_sp==20)),rep("Env",sum(table_fac$n_sp==20))))

tf<-data.frame("success"=as.numeric(tf[,1]),"model"=tf[,2],"fac"=tf[,3],"int"=rep("Facilitation",nrow(tf)),"col"=tf[,4])

table<-rbind(tf,tc)

p<-ggplot(data=table)+geom_boxplot(aes(y=as.numeric(success),x=as.factor(fac),fill=as.factor(col)))+
  scale_x_discrete(name="Parameters", breaks=c("All","5","10","20","dense","sparse","All_env","5_env","10_env","20_env"),
                   labels=c("All","5","10","20","dense","sparse","All","5","10","20"),limits=c("All","5","10","20","dense","sparse","All_env","5_env","10_env","20_env"))+
  scale_y_continuous(name="% success")+
  scale_fill_discrete(name = "Success in retrieving_", labels = c("Sensibility (non int.)","Sensitivity (int."))+theme(axis.text.x = element_text(angle = 45, hjust = 1),legend.position="top")+
  facet_wrap( ~ int+model, scales="free") +ggtitle("Pairs indentification by partial correlation")
p

```

## Visualization for true interactions

### Facilitation

```{r inter_patter_fac, echo=FALSE}
par(mfrow=c(1,3))
corrplot(fac_inter[[4]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200),type = "lower")
title("FacDenseSp5")
corrplot(fac_inter[[5]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("FacDenseSp10")
corrplot(fac_inter[[6]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp20")
mtext("Facilitation Dense", outer = TRUE, cex = 1.5,side=1,line=-1)

par(mfrow=c(1,3))
corrplot(fac_inter[[7]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp5")
corrplot(fac_inter[[8]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp10")
corrplot(fac_inter[[9]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp20")
mtext("Facilitation Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)
```

### Competition Dense

```{r inter_pattern_comp dense, echo=FALSE}
par(mfrow=c(1,3))
corrplot((-1)*comp_inter[[10]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp5")
corrplot((-1)*comp_inter[[11]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("CompDenseSp10")
corrplot((-1)*comp_inter[[12]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp20")
#mtext("Competition Dense", outer = TRUE, cex = 1.5,side=1,line=-1)

```

### Competition Dense

```{r inter_pattern_comp sparse, echo=FALSE}

par(mfrow=c(1,3))
corrplot((-1)*comp_inter[[13]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompSparseSp5")
corrplot((-1)*comp_inter[[14]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompSparseSp10")
corrplot((-1)*comp_inter[[15]], diag = FALSE, order = "FPC",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("CompSparseSp20")
#mtext("Competition Sparse", outer = TRUE, cex = 1.5,side=1,line=-1)


```


### Competition + Facilitation Dense

```{r inter_pattern_both dense, echo=FALSE}
par(mfrow=c(2,3))
corrplot(fac_inter[[16]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp5")
corrplot(fac_inter[[17]], diag = FALSE,order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp10")
corrplot(fac_inter[[18]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacDenseSp20")
#mtext("Both types Dense - Facilitation + Competition", outer = TRUE, cex = 1.5,side=1,line=-1)
corrplot((-1)*comp_inter[[16]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp5")
corrplot((-1)*comp_inter[[17]], diag = FALSE,order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp10")
corrplot((-1)*comp_inter[[18]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompDenseSp20")
#mtext("Both types Dense", outer = TRUE, cex = 1.5,side=3,line=-1)

```

### Competition + Facilitation Sparse

```{r inter_pattern_both sparse, echo=FALSE}
par(mfrow=c(2,3))
corrplot(fac_inter[[19]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("FacSparseSp5")
corrplot(fac_inter[[20]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("FacSparseSp10")
corrplot(fac_inter[[21]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color" ,col=cols(200), type = "lower")
title("FacSparseSp20")
#mtext("Both types Sparse", outer = TRUE, cex = 1.5,side=1,line=-0.5)
corrplot((-1)*comp_inter[[19]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color",col=cols(200), type = "lower")
title("CompSparseSp5")
corrplot((-1)*comp_inter[[20]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color", col=cols(200),type = "lower")
title("CompSparseSp10")
corrplot((-1)*comp_inter[[21]], diag = FALSE, order = "original",tl.pos = "ld", tl.cex = 0.5, method = "color" ,col=cols(200), type = "lower")
title("CompSparseSp20")
```




```{r prediction, echo=FALSE}

predict_y_jsdm <- function(x, ns = 1000) {
  data   <- if(x$parallel) x$model[[1]]$data() else x$model$data()
  n      <- data$n
  nsp    <- data$J
  n.samples  <- x$mcmc.info$n.samples
  B <- x$sims.list$B
  X <- data$X
  Y <- data$Y
  inprod_mat <- cppFunction(
    "NumericMatrix inprod_mat(NumericMatrix X, NumericMatrix B) {
    
    int nX = X.nrow();
    int nB = B.nrow();
    int nK = X.ncol();
    
    NumericMatrix theta(nX, nB);
    
    for (int i = 0; i < nX; i++) {
    for (int j = 0; j < nB; j++) {
    theta(i, j) = 0;
    for (int k = 0; k < nK; k++) {
    theta(i, j) += X(i, k) * B(j, k);
    }
    }
    }
    
    return(theta);
    
}"
  )
  vapply(
    floor(seq(1, n.samples, length.out = ns)),
    function(x) inprod_mat(X, B[x, ,]),
    matrix(NA_real_, n, nsp)
  )
  }


#me5_pred<-predict_y_jsdm(me5)

predictions <- sapply(models, predict_y_jsdm)

prediction_means <- sapply(predictions, apply, 1:2, mean)

prediction_q05 <- sapply(predictions, apply, 1:2, quantile,0.05)
prediction_q95 <- sapply(predictions, apply, 1:2, quantile,0.05)

prediction_sds <- sapply(predictions, apply, 1:2, sd)




```


